### 2012-02-29 proposal/proposal.tex
added proposal document (empty)

\documentclass{ubicomp2011}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Your Title}, pdfauthor={Your Authors}, pdfkeywords={your
keywords}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
citecolor=black, filecolor=black, linkcolor=black, urlcolor=black,
breaklinks=true, }
\newcommand{\comment}[1]{}
\definecolor{Orange}{rgb}{1,0.5,0}
\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[[#1]]}}}}

\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy

\begin{document}
% to make various LaTeX processors do the right thing with page size
\special{papersize=8.5in,11in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

% use this command to override the default ACM copyright statement
% (e.g. for preprints). Remove for camera ready copy.

%\toappear{Paper submitted for evaluation in the Pervasive Computing Course, Spring 2012. The IT University of Copenhagen. Copyright remains with the authors.}

\toappear{Project proposal for the Pervasive Computing Course, Spring 2012. The IT University of Copenhagen. Copyright remains with the authors.}

\title{UbiComp 2011 Conference Proceedings Format}
\numberofauthors{2}
\author{
  \alignauthor Egil Hansen\\
    \affaddr{IT University of Copenhagen}\\
%    \affaddr{Address  (Blank for Blind Review)}\\
    \email{ekri@itu.dk}
 \alignauthor David Thomas\\
    \affaddr{IT University of Copenhagen}\\
%    \affaddr{Address  (Blank for Blind Review)}\\
    \email{dtho@itu.dk}  }
\maketitle

%\begin{abstract}
%  In this paper we describe the formatting requirements for the UbiComp 2011
%  Conference Proceedings, and offer recommendations on writing for the
%  worldwide Ubiquitous Computing readership.  Please review this document even if
%  you have submitted to Ubiquitous Computing conferences before, for some format
%  details have changed relative to previous years. These include the
%  formatting of table captions, the formatting of references, a
%  requirement to include ACM DL indexing information, and guidelines for how to handle relevant references to your own work while preparing your submission for blind review.
%\end{abstract}

%\keywords{Guides, instructions, authors' kit, conference publications.}

%\category{H.5.2}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}.

%\generalterms{This section is limited to the following 16 terms and
%MUST be included on the first page of all submissions after the ACM
%Categories section, then as well chosen properly on the Proceedings
%or Publication's submission page: Algorithms, Design,
%Documentation, Economics, Experimentation, Human Factors, Languages,
%Legal Aspects, Management, Measurement, Performance, Reliability,
%Security, Standardization, Theory, Verification.}

\section{Background}
hep

\section{Idea}
hep

\section{Scenario}
hep

\section{Plan}
hep

\subsection{Equipment}
hep

% Referencer:
% ~\cite{ref}

% til sidst
%\nocite{example-journal,example-abstracts,example-conference2}

\bibliographystyle{abbrv}
\bibliography{proposal}

\end{document}

### 2012-02-29 proposal/proposal.tex
project proposal filled in

@@
 
-\title{UbiComp 2011 Conference Proceedings Format}
+\title{Smart Homes for Dummies}
 \numberofauthors{2}
@@
 \section{Background}
-hep
+Many existing systems and protocols enable the control of devices in smart homes, including OSGi, X10, and ZigBee.
+However, all of these systems rely on a central control unit in addition to the devices being controlled.
+Installation and configuration of devices in smart homes, especially UI-less devices,  is also hard for most non-technical users, often requiring a technician to assist in the installation.
+Both of these facts make smart home technology less accessible to many people, by increasing the initial cost in hardware and man-hours.
 
 \section{Idea}
-hep
+We want to define a general purpose architecture and protocol for UI-less smart homes devices, that leverages the existing, modern, infrastructure which exists in most homes, i.e.
+Wifi networks and Android devices.
+We believe that is possible to design such a system that will allow non-technical users to easily install, configure, and operate most common smart home devices with only their Android device.
+
+To provide a UI for UI-less devices, we must also define or re-purpose a protocol that enables the functionality that the device supports.
+Our idea is to let each smart home device define UI controls without defining their visual appearance, that way we decouple look and feel from functionality, and make it possible to achieve an consistent look and feel of the control among many different smart home devices.
+
+The minimum requirement to a smart home device is a Wifi radio, and a way to put put the device into installation mode.
+When a device is in installation mode, an Android device is able to configure it, in essence, assigning a name to it and telling it which Wifi hotspot to connect to.
+Once the device is on Wifi, an Android device will be able to control and configure it while connected to the homes Wifi.
+
+A similar approach is described in LockIT~\cite{lockit}, though it has the disadvantages of requiring an NFC-enabled phone  and of disconnecting the phone from the ordinary Wifi  connection during use.
 
 \section{Scenario}
-hep
+\subsection{Installation}
+\begin{enumerate}
+\item A user buys our device in a hardware store. In this example, the device is a smart switch controlling the power for a lamp.
+\item The user gets home and plugs in the device between a power plug and a lamp.
+\item The user is guided through the process of installing the Android app and connecting the smart switch to the Wifi access point.
+\end{enumerate}
+
+\subsection{Daily use}
+\begin{enumerate}
+\item The user is lying on the couch watching a movie, and realizes that the room lighting  is too bright.
+\item Not wanting to get up, the user opts to turn down the light using a smart light switch that was previously installed.
+\item The user starts the app on his Android phone, which shows a list of available devices.
+\item The user selects the light switch, and the app shows the UI for the switch.
+\item The user turns down the light through the UI and enjoys the rest of the movie.
+\end{enumerate}
 
 \section{Plan}
-hep
+In our project, we need to:
+\begin{itemize}
+\item Select communication protocols, service protocols, etc., for UI-less devices.
+\item Select or define  a syntax for specifying the UIs to be shown in the Android app.
+\item Define an easy-to-follow process for associating a UI-less device with a Wifi access point.
+\item Develop Android app for installation, configuration, and control of UI-less devices.
+\end{itemize}
 
-\subsection{Equipment}
-hep
+We will evaluate our implementation through user testing by users who own a smart phone but are otherwise non-technical.
+
+\section{Equipment}
+\begin{itemize}
+\item Android phone (both group members have Android phones available)
+\item Arduino with Wifi shield, for prototyping a UI-less device
+\end{itemize}
+
+\section{Supervisors}
+Jakob Bardram?
 

### 2012-04-22 JUIDLParser.java/src/dk/itu/spcl/dex/juidl/UIGenerator.java
report, etc

@@ -2,7 +2,10 @@ package dk.itu.spcl.dex.juidl;
 
 import java.util.ArrayList;
 import java.util.Arrays;
+import java.util.Collections;
+import java.util.Comparator;
 import java.util.HashSet;
+import java.util.LinkedList;
 import java.util.List;
 
 import org.json.JSONArray;
@@ -10,7 +13,8 @@ import org.json.JSONObject;
 
 public abstract class UIGenerator {
 	public static final double[] SUPPORTED_SCHEMA_VERSIONS = { 1.0 };
-	private HashSet<String> idCol;
+	private static Comparator<JSONObject> priorityComparator = new JSONWidgetPriorityComparator();
+	private HashSet<String> idCol; 
 
 	/**
 	 * Use this method to generate the UI based on the schema.
@@ -98,17 +102,43 @@ public abstract class UIGenerator {
 		}
 	}
 	
-	private void generateWidgets(JSONArray widgets, String parentId) {		
+	private void generateWidgets(JSONArray widgets, String parentId) {			
+		JSONObject[] sortedWidgets = new JSONObject[widgets.length()]; 
 		int index = 0;
 		JSONObject widget;	
-		while (null != (widget = widgets.optJSONObject(index))) {
-			generateWidget(widget, parentId);
+		while (null != (widget = widgets.optJSONObject(index))) {			
+			sortedWidgets[index] = widget;
 			index++;
-		}	
+		}
+		
+		// sort array of widgets according to priority
+		Arrays.sort(sortedWidgets, priorityComparator);
+		
+		// generate each widget
+		for(index = 0; index < sortedWidgets.length; index++) {
+			generateWidget(sortedWidgets[index], parentId);
+		}
 	}
 	
 	private void generateWidget(JSONObject widget, String parentId) {
-		
+		// create new widget	
+		//Widget w = Widget.createFromJSONObject(widget);
+//		String ct = widget.optString("content-type");
+//		if (ct.equalsIgnoreCase("integer")) {
+//			Widget<Integer> w = Widget.genericFillFromJSONObject(Integer.class, widget, parentId);
+//			
+//		} else if (ct.equalsIgnoreCase("boolean")) {
+//			Widget<Boolean> w = new Widget<Boolean>();
+//		} else if (ct.equalsIgnoreCase("integer[]")) {
+//			Widget<List<Integer>> w = new Widget<List<Integer>>();
[…]

### 2012-04-22 JUIDLParser.java/src/dk/itu/spcl/dex/juidl/Widget.java

@@ -1,0 +1,83 @@
+package dk.itu.spcl.dex.juidl;
+
+import java.util.List;
+
+import org.json.JSONObject;
+
+public class Widget<T> {
+	private String _id;
+	private String _parentId;
+	private String _title;
+	private String _description;
+	private WidgetType _type;
+	private T _content;
+	private List<Widget> _widgets;
+
+	public String getId() {
+		return _id;
+	}
+
+	public void setId(String _id) {
+		this._id = _id;
+	}
+
+	public String getParentId() {
+		return _parentId;
+	}
+
+	public void setParentId(String _parentId) {
+		this._parentId = _parentId;
+	}
+
+	public String getTitle() {
+		return _title;
+	}
+
+	public void setTitle(String _title) {
+		this._title = _title;
+	}
+
+	public String getDescription() {
+		return _description;
+	}
+
+	public void setDescription(String _description) {
+		this._description = _description;
+	}
+
+	public WidgetType getType() {
+		return _type;
+	}
+
+	public void setType(WidgetType _type) {
+		this._type = _type;
+	}
+
+	public T getContent() {
+		return _content;
+	}
+
+	public void setContent(T _content) {
+		this._content = _content;
+	}
+
+	public List<Widget> getWidgets() {
+		return _widgets;
+	}
+
+	public void setWidgets(List<Widget> _widgets) {
+		this._widgets = _widgets;
+	}
+
+	public static <T> Widget<T> genericFillFromJSONObject(JSONObject json, String parentId) {
+		Widget<T> w = new Widget<T>();
+		w.setId(json.optString("id"));
+		w.setDescription(json.optString("description"));
+		w.setTitle(json.optString("title"));
+		w.setType(Enum.valueOf(WidgetType.class, json.optString("type", "read-only").replace('-', '_').toUpperCase()));
+		w.setParentId(parentId);
+		
+		
+		return w;
+	}
+}

### 2012-04-22 JUIDLParser.java/src/dk/itu/spcl/dex/juidl/WidgetType.java

@@ -1,0 +1,10 @@
+package dk.itu.spcl.dex.juidl;
+
+public enum WidgetType {
+	READ_ONLY,
+	EDITABLE,
+	SELECT,
+	MULTI_SELECT,
+	TRIGGER,
+	GROUP
+}

### 2012-04-22 JUIDLParser.java/tests/dk/itu/spcl/dex/juidl/tests/MockUIGenerator.java

@@ -10,68 +10,16 @@ import org.json.JSONObject;
 import dk.itu.spcl.dex.juidl.UIGenerator;
 
 public class MockUIGenerator extends UIGenerator {
+	public String canvasTitle;
+	public String canvasDesription;
+	public double canvasVersion;
+	public ArrayList<JSONObject> canvasItems = new ArrayList<JSONObject>();
 
 	@Override
 	protected void generateCanvas(String title, String description,
 			double version) {
-		// TODO Auto-generated method stub
-		
+		canvasTitle = title;
+		canvasDesription = description;
+		canvasVersion = version;
 	}
-
-	@Override
-	protected void generateStringWidget(String id, String parentId,
-			String title, String description, String type, String content) {
-		// TODO Auto-generated method stub
-		
-	}
-
-	@Override
-	protected void generateIntWidget(String id, String parentId, String title,
-			String description, String type, int content) {
-		// TODO Auto-generated method stub
-		
-	}
-
-	@Override
-	protected void generateDoubleWidget(String id, String parentId,
-			String title, String description, String type, double content) {
-		// TODO Auto-generated method stub
-		
-	}
-
-	@Override
-	protected void generateBooleanWidget(String id, String parentId,
-			String title, String description, String type, boolean content) {
-		// TODO Auto-generated method stub
-		
-	}
-
-	@Override
-	protected void generateStringListWidget(String id, String parentId,
-			String title, String description, String type, List<String> content) {
-		// TODO Auto-generated method stub
-		
-	}
-
-	@Override
-	protected void generateIntListWidget(String id, String parentId,
-			String title, String description, String type, List<Integer> content) {
-		// TODO Auto-generated method stub
-		
-	}
-
-	@Override
-	protected void generateDoubleListWidget(String id, String parentId,
-			String title, String description, String type, List<Double> content) {
-		// TODO Auto-generated method stub
-		
-	}
-
-	@Override
-	protected void generateBooleanListWidget(String id, String parentId,
-			String title, String description, String type, List<Boolean> content) {
-		// TODO Auto-generated method stub
-		
-	}
-
 }

### 2012-04-22 JUIDLParser.java/tests/dk/itu/spcl/dex/juidl/tests/UIGeneratorTest.java

@@ -1,14 +1,44 @@
 package dk.itu.spcl.dex.juidl.tests;
 
 import static org.junit.Assert.*;
+import junit.framework.Assert;
 
+import org.json.JSONException;
+import org.json.JSONObject;
+import org.junit.Before;
 import org.junit.Test;
+
+import dk.itu.spcl.dex.juidl.JUIDLException;
+import dk.itu.spcl.dex.juidl.UIGenerator;
 
 public class UIGeneratorTest {
 
-	@Test
-	public void test() {
-		
+	private MockUIGenerator p;
+
+	@Before
+	public void Setup() {
+		p = new MockUIGenerator();
 	}
 
+	@Test
+	public void canvasGenTest() throws JSONException, JUIDLException {
+		String test_schema = "{'title':'The Title', " +
+							  "'description':'The Description', " +
+							  "'version':1.0, 'widgets':[]}";
+		JSONObject schema_json = new JSONObject(test_schema);
+		p.generate(schema_json);
+		assertEquals("The Title", p.canvasTitle);		
+		assertEquals("The Description", p.canvasDesription);
+		assertEquals(1.0, p.canvasVersion, 0);
+	}
+	
+	// @Test
+	// public void sortingTest() {
+	// String test_schema = "{'title':'The Title', 'version':1.0, " +
+	// "'widgets':[{'id':'2'}," +
+	// "{'id':'3'}," +
+	// "]}";
+	// JSONObject schema_json = new JSONObject(test_schema);
+	// p.validate(schema_json);
+	// }
 }

### 2012-04-22 JUIDLParser.java/tests/dk/itu/spcl/dex/juidl/tests/WidgetTest.java

@@ -1,0 +1,41 @@
+package dk.itu.spcl.dex.juidl.tests;
+
+import static org.junit.Assert.*;
+
+import java.util.List;
+
+import org.json.JSONException;
+import org.json.JSONObject;
+import org.junit.Test;
+
+import dk.itu.spcl.dex.juidl.Widget;
+import dk.itu.spcl.dex.juidl.WidgetType;
+
+public class WidgetTest {
+
+	@Test
+	public void testGenericFillFromJSONObject() throws JSONException {
+		JSONObject json = new JSONObject();
+		String expId = "1234";
+		json.put("id", expId);
+		String expTitle = "The Title";
+		json.put("title", expTitle);
+		String expDesc = "The Description";
+		json.put("description", expDesc);
+		WidgetType expType = WidgetType.EDITABLE;
+		json.put("type", "editable");
+		int[] expectedContent = new int[]{3,4,5};
+		json.put("content", expectedContent);
+		String expParentId = "42";
+		
+		Widget<int[]> widget = Widget.genericFillFromJSONObject(json, expParentId);
+
+		assertEquals(expId, widget.getId());
+		assertEquals(expTitle, widget.getTitle());
+		assertEquals(expDesc, widget.getDescription());
+		assertEquals(expType, widget.getType());
+		assertEquals(expectedContent, widget.getContent());
+		assertEquals(expParentId, widget.getParentId());
+	}
+
+}

### 2012-04-22 prototype/gen/dk/itu/spcl/dex/R.java
prototype, got rid of serialization

@@ -15,17 +15,23 @@ public final class R {
         public static final int ic_tab_default=0x7f020001;
     }
     public static final class id {
-        public static final int newThingyMenu=0x7f060000;
+        public static final int newPresetMenu=0x7f060001;
+        public static final int newThingyMenu=0x7f060002;
+        public static final int presetThingyList=0x7f060000;
     }
     public static final class layout {
-        public static final int home=0x7f030000;
-        public static final int thingylist_item=0x7f030001;
+        public static final int default_list_item=0x7f030000;
+        public static final int home=0x7f030001;
+        public static final int preset=0x7f030002;
     }
     public static final class menu {
-        public static final int thingylistmenu=0x7f050000;
+        public static final int presetlistmenu=0x7f050000;
+        public static final int thingylistmenu=0x7f050001;
     }
     public static final class string {
         public static final int app_name=0x7f040000;
+        public static final int newPresetMenu=0x7f040003;
         public static final int newThingyMenu=0x7f040001;
+        public static final int presetActivate=0x7f040002;
     }
 }

### 2012-04-22 prototype/src/dk/itu/spcl/dex/EditPresetActivity.java

@@ -1,0 +1,7 @@
+package dk.itu.spcl.dex;
+
+import android.app.Activity;
+
+public class EditPresetActivity extends Activity {
+
+}

### 2012-04-22 prototype/src/dk/itu/spcl/dex/PresetActivity.java

@@ -1,0 +1,36 @@
+package dk.itu.spcl.dex;
+
+import android.app.Activity;
+import android.os.Bundle;
+import android.widget.ArrayAdapter;
+import android.widget.ListView;
+import dk.itu.spcl.dex.model.Preset;
+import dk.itu.spcl.dex.model.Repository;
+import dk.itu.spcl.dex.model.Thingy;
+
+public class PresetActivity extends Activity {
+  
+  private Preset _preset;
+  
+  @Override
+  protected void onCreate(Bundle savedInstanceState) {
+    super.onCreate(savedInstanceState);
+    setContentView(R.layout.preset);
+    
+    _preset = Repository.getInstance().getPreset(getIntent().getStringExtra("preset"));
+    setTitle("Preset: " + _preset.getName());
+    populateThingyList();
+  }
+  
+  private void populateThingyList() {
+    ArrayAdapter<Thingy> listAdapter = new ArrayAdapter<Thingy>(this, R.layout.default_list_item,
+        _preset.getThingies());
+    ListView listView = (ListView)findViewById(R.id.presetThingyList);
+    listView.setAdapter(listAdapter);
+  }
+  
+}
+
+
+
+

### 2012-04-22 prototype/src/dk/itu/spcl/dex/PresetListActivity.java

@@ -1,18 +1,101 @@
 package dk.itu.spcl.dex;
 
-import android.app.Activity;
+import android.app.ListActivity;
+import android.content.Intent;
 import android.os.Bundle;
-import android.widget.TextView;
+import android.view.Menu;
+import android.view.MenuInflater;
+import android.view.MenuItem;
+import android.view.View;
+import android.widget.AdapterView;
+import android.widget.AdapterView.OnItemClickListener;
+import android.widget.ArrayAdapter;
+import android.widget.ListView;
+import dk.itu.spcl.dex.model.Preset;
+import dk.itu.spcl.dex.model.Repository;
+import dk.itu.spcl.dex.model.Repository.UpdateListener;
 
-public class PresetListActivity extends Activity {
-  
+public class PresetListActivity extends ListActivity {
+
+  private Repository _repository;
+  private ArrayAdapter<Preset> _listAdapter;
+  private Repository.UpdateListener _updateListener;
+
   @Override
   protected void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
-    
-    TextView textview = new TextView(this);
-    textview.setText("Preset list goes here");
-    setContentView(textview);
+    _repository = Repository.getInstance();
+    populatePresetList();
+    addRepositoryListener();
+    addListSelectionListener();
+  }
+
+  @Override
+  protected void onDestroy() {
+    super.onDestroy();
+    removeUpdateListener();
+  }
+
+  private void addRepositoryListener() {
+    _updateListener = new UpdateListener() {
+      @Override
+      public void repositoryUpdated() {
+        _listAdapter.clear();
+        for (Preset p : _repository.getPresets())
+          _listAdapter.add(p);
+        _listAdapter.notifyDataSetChanged();
+      }
+    };
+    _repository.addUpdateListener(_updateListener);
+  }
+
+  private void removeUpdateListener() {
+    _repository.removeUpdateListener(_updateListener);
+  }
+
+  private void addListSelectionListener() {
+    ListView listView = getListView();
+    listView.setOnItemClickListener(new OnItemClickListener() {
+      public void onItemClick(AdapterView<?> parent, View view, int position,
+          long id) {
+        Preset preset = (Preset) parent.getItemAtPosition(position);
+        startPresetActivity(preset);
+      }
+    });
+  }
+
+  private void startPresetActivity(Preset preset) {
[…]

### 2012-04-22 prototype/src/dk/itu/spcl/dex/ScanActivity.java

@@ -1,18 +1,45 @@
 package dk.itu.spcl.dex;
 
 import android.app.Activity;
+import android.content.Intent;
 import android.os.Bundle;
 import android.widget.TextView;
+import dk.itu.spcl.dex.model.Thingy;
 
 public class ScanActivity extends Activity {
-  
+
   @Override
   protected void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
-    
+
     TextView textview = new TextView(this);
     textview.setText("Scanning goes here");
-    setContentView(textview); 
+    setContentView(textview);
+
+    performDummyScan();
+  }
+
+  private void performDummyScan() {
+    Thread scanThread = new Thread(new Runnable() {
+
+      @Override
+      public void run() {
+        try {
+          Thread.sleep(1500);
+        } catch (InterruptedException e) {
+        }
+        
+        Thingy thingy = new Thingy().setName("scanned thingy whoo!");
+        returnScannedThingy(thingy);
+      }
+
+      private void returnScannedThingy(Thingy thingy) { 
+        Intent data = new Intent(ScanActivity.this, ScanActivity.class).putExtra("thingy", thingy.getName());
+        setResult(RESULT_OK, data);
+        finish();
+      }
+    });
+    scanThread.start();
   }
 
 }

### 2012-04-22 prototype/src/dk/itu/spcl/dex/ThingyActivity.java

@@ -1,23 +1,25 @@
 package dk.itu.spcl.dex;
 
-import dk.itu.spcl.dex.model.Thingy;
 import android.app.Activity;
 import android.os.Bundle;
 import android.widget.TextView;
+import dk.itu.spcl.dex.model.Repository;
+import dk.itu.spcl.dex.model.Thingy;
 
 public class ThingyActivity extends Activity {
 
-  private Thingy _thingy;  
-  
+  private Thingy _thingy;
+
   @Override
   protected void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
-    
-    _thingy = getIntent().getParcelableExtra("thingy");
-    
+
+    _thingy = Repository.getInstance().getThingy(
+        getIntent().getStringExtra("thingy"));
+
     TextView textview = new TextView(this);
     textview.setText("UI for " + _thingy.getName() + " goes here!");
     setContentView(textview);
   }
-  
+
 }

### 2012-04-22 prototype/src/dk/itu/spcl/dex/ThingyListActivity.java

@@ -12,22 +12,49 @@ import android.widget.AdapterView.OnItemClickListener;
 import android.widget.ArrayAdapter;
 import android.widget.ListView;
 import dk.itu.spcl.dex.model.Repository;
+import dk.itu.spcl.dex.model.Repository.UpdateListener;
 import dk.itu.spcl.dex.model.Thingy;
 
 public class ThingyListActivity extends ListActivity {
 
   private Repository _repository;
   private final int SCAN_FOR_THINGY_REQUEST_CODE = 1;
+  private ArrayAdapter<Thingy> _listAdapter;
+  private Repository.UpdateListener _updateListener;
 
   @Override
   protected void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
     _repository = Repository.getInstance();
     populateThingyList();
-    addThingyListListener();
+    addRepositoryListener();
+    addListSelectionListener();
   }
 
-  private void addThingyListListener() {
+  @Override
+  protected void onDestroy() {
+    super.onDestroy();
+    removeUpdateListener();
+  }
+
+  private void addRepositoryListener() {
+    _updateListener = new UpdateListener() {
+      @Override
+      public void repositoryUpdated() {
+        _listAdapter.clear();
+        for (Thingy t : _repository.getThingies())
+          _listAdapter.add(t);
+        _listAdapter.notifyDataSetChanged();
+      }
+    };
+    _repository.addUpdateListener(_updateListener);
+  }
+
+  private void removeUpdateListener() {
+    _repository.removeUpdateListener(_updateListener);
+  }
+
+  private void addListSelectionListener() {
     ListView listView = getListView();
     listView.setOnItemClickListener(new OnItemClickListener() {
       public void onItemClick(AdapterView<?> parent, View view, int position,
@@ -37,16 +64,17 @@ public class ThingyListActivity extends ListActivity {
       }
     });
   }
-  
+
   private void startThingyActivity(Thingy thingy) {
-    Intent intent = new Intent(this, ThingyActivity.class).putExtra("thingy", thingy);
+    Intent intent = new Intent(this, ThingyActivity.class).putExtra("thingy",
+        thingy.getName());
     startActivity(intent);
   }
 
   private void populateThingyList() {
-    ArrayAdapter<Thingy> listAdapter = new ArrayAdapter<Thingy>(this,
[…]

### 2012-04-22 prototype/src/dk/itu/spcl/dex/model/Preset.java

@@ -1,5 +1,35 @@
 package dk.itu.spcl.dex.model;
 
-public class Preset {
+import java.util.ArrayList;
 
+public class Preset {
+  
+  private ArrayList<Thingy> _thingies;
+  private String _name;
+  
+  public Preset() {
+    _thingies = new ArrayList<Thingy>(); 
+  }
+ 
+  public Preset setName(String name) {
+    _name = name;
+    return this;
+  }
+  
+  public String getName() {
+    return _name;
+  }
+  
+  public void addThingy(Thingy t) {
+    _thingies.add(t);
+  }
+  
+  public ArrayList<Thingy> getThingies() {
+    return _thingies;
+  }
+  
+  @Override
+  public String toString() {
+    return getName();
+  }
 }

### 2012-04-22 prototype/src/dk/itu/spcl/dex/model/Repository.java

@@ -1,30 +1,76 @@
 package dk.itu.spcl.dex.model;
 
-import java.util.*;
+import java.util.ArrayList;
+import java.util.HashMap;
 
 public class Repository {
-  
-  private ArrayList<Thingy> _thingies = new ArrayList<Thingy>();
+
+  public interface UpdateListener {
+    public void repositoryUpdated();
+  }
+
+  HashMap<String, Thingy> _thingies = new HashMap<String, Thingy>();
+  HashMap<String, Preset> _presets = new HashMap<String, Preset>();
+
   private static Repository _instance;
-  
+  private ArrayList<UpdateListener> _updateListeners = new ArrayList<Repository.UpdateListener>();
+
   private Repository() {
     // test data
-    _thingies.add(new Thingy().setName("test thingy"));
-    _thingies.add(new Thingy().setName("other thingy"));
+    addThingy(new Thingy().setName("test thingy"));
+    addThingy(new Thingy().setName("other thingy"));
+    addThingy(new Thingy().setName("third thingy"));
+
+    Preset samplePreset = new Preset().setName("sample preset");
+    samplePreset.addThingy(getThingies().get(0));
+    samplePreset.addThingy(getThingies().get(1));
+    addPreset(samplePreset);
   }
-  
+
+  public void addUpdateListener(UpdateListener listener) {
+    _updateListeners.add(listener);
+  }
+
+  public void removeUpdateListener(UpdateListener listener) {
+    _updateListeners.remove(listener);
+  }
+
   public static Repository getInstance() {
     if (_instance == null)
       _instance = new Repository();
     return _instance;
-  }  
-
-  public ArrayList<Thingy> getThingies() {
-    return _thingies;
   }
 
   public void addThingy(Thingy t) {
-    _thingies.add(t);
+    _thingies.put(t.getName(), t);
+    onUpdate();
+  }
+
+  public void addPreset(Preset p) {
+    _presets.put(p.getName(), p);
+    onUpdate();
+  }
+
+  private void onUpdate() {
+    for (UpdateListener listener : _updateListeners) {
+      listener.repositoryUpdated();
+    }
+  }
+
+  public ArrayList<Preset> getPresets() {
+    return new ArrayList<Preset>(_presets.values());
+  }
+  
+  public ArrayList<Thingy> getThingies() {
+    return new ArrayList<Thingy>(_thingies.values());
+  }
+  
+  public Thingy getThingy(String name) {
[…]

### 2012-04-22 prototype/src/dk/itu/spcl/dex/model/Thingy.java

@@ -1,17 +1,10 @@
 package dk.itu.spcl.dex.model;
 
-import android.os.Parcel;
-import android.os.Parcelable;
-
-public class Thingy implements Parcelable {
+public class Thingy {
 
   private String _name;
 
   public Thingy() {
-  }
-
-  private Thingy(Parcel in) {
-    _name = in.readString();
   }
 
   public String getName() {
@@ -27,25 +20,4 @@ public class Thingy implements Parcelable {
   public String toString() {
     return getName();
   }
-
-  @Override
-  public int describeContents() {
-    return 0;
-  }
-
-  @Override
-  public void writeToParcel(Parcel out, int flags) {
-    out.writeString(_name);
-  }
-
-  public static final Parcelable.Creator<Thingy> CREATOR = new Parcelable.Creator<Thingy>() {
-    public Thingy createFromParcel(Parcel in) {
-      return new Thingy(in);
-    }
-
-    public Thingy[] newArray(int size) {
-      return new Thingy[size];
-    }
-  };
-
 }

### 2012-04-22 prototype/gen/dk/itu/spcl/dex/R.java
adding thingies to presets

@@ -15,8 +15,9 @@ public final class R {
         public static final int ic_tab_default=0x7f020001;
     }
     public static final class id {
+        public static final int addThingyMenu=0x7f060002;
         public static final int newPresetMenu=0x7f060001;
-        public static final int newThingyMenu=0x7f060002;
+        public static final int newThingyMenu=0x7f060003;
         public static final int presetThingyList=0x7f060000;
     }
     public static final class layout {
@@ -26,12 +27,15 @@ public final class R {
     }
     public static final class menu {
         public static final int presetlistmenu=0x7f050000;
-        public static final int thingylistmenu=0x7f050001;
+        public static final int presetmenu=0x7f050001;
+        public static final int thingylistmenu=0x7f050002;
     }
     public static final class string {
+        public static final int addThingyMenu=0x7f040004;
         public static final int app_name=0x7f040000;
         public static final int newPresetMenu=0x7f040003;
         public static final int newThingyMenu=0x7f040001;
         public static final int presetActivate=0x7f040002;
+        public static final int renamePresetMenu=0x7f040005;
     }
 }

### 2012-04-22 prototype/src/dk/itu/spcl/dex/EditPresetActivity.java

@@ -1,7 +1,0 @@
-package dk.itu.spcl.dex;
-
-import android.app.Activity;
-
-public class EditPresetActivity extends Activity {
-
-}

### 2012-04-22 prototype/src/dk/itu/spcl/dex/PresetActivity.java

@@ -1,7 +1,11 @@
 package dk.itu.spcl.dex;
 
 import android.app.Activity;
+import android.content.Intent;
 import android.os.Bundle;
+import android.view.Menu;
+import android.view.MenuInflater;
+import android.view.MenuItem;
 import android.widget.ArrayAdapter;
 import android.widget.ListView;
 import dk.itu.spcl.dex.model.Preset;
@@ -10,12 +14,17 @@ import dk.itu.spcl.dex.model.Thingy;
 
 public class PresetActivity extends Activity {
   
+  private static final int PICK_THINGY_REQUEST_CODE = 1;
   private Preset _preset;
+  private Repository _repository;
+  private ArrayAdapter<Thingy> _listAdapter;
   
   @Override
   protected void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
     setContentView(R.layout.preset);
+    
+    _repository = Repository.getInstance();
     
     _preset = Repository.getInstance().getPreset(getIntent().getStringExtra("preset"));
     setTitle("Preset: " + _preset.getName());
@@ -23,11 +32,49 @@ public class PresetActivity extends Activity {
   }
   
   private void populateThingyList() {
-    ArrayAdapter<Thingy> listAdapter = new ArrayAdapter<Thingy>(this, R.layout.default_list_item,
+    _listAdapter = new ArrayAdapter<Thingy>(this, R.layout.default_list_item,
         _preset.getThingies());
     ListView listView = (ListView)findViewById(R.id.presetThingyList);
-    listView.setAdapter(listAdapter);
+    listView.setAdapter(_listAdapter);
   }
+
+  @Override
+  public boolean onCreateOptionsMenu(Menu menu) {
+    MenuInflater inflater = getMenuInflater();
+    inflater.inflate(R.menu.presetmenu, menu);
+    return true;
+  }
+  
+  @Override
+  public boolean onOptionsItemSelected(MenuItem item) {
+    switch (item.getItemId()) {
+    case R.id.addThingyMenu:
+      addThingy();
+      return true;
+//    case R.id.renamePresetMenu:
+//      renamePreset();
+//      return true;
+    default:
+      return super.onOptionsItemSelected(item);
+    }
+  }
+
+  private void addThingy() {
+    startActivityForResult(new Intent(this, ThingyListActivity.class).putExtra("selectionMode", true),
+        PICK_THINGY_REQUEST_CODE);
+  }
+  
[…]

### 2012-04-22 prototype/src/dk/itu/spcl/dex/ScanActivity.java

@@ -4,13 +4,18 @@ import android.app.Activity;
 import android.content.Intent;
 import android.os.Bundle;
 import android.widget.TextView;
+import dk.itu.spcl.dex.model.Repository;
 import dk.itu.spcl.dex.model.Thingy;
 
 public class ScanActivity extends Activity {
+  
+  private Repository _repository;
 
   @Override
   protected void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
+    
+    _repository = Repository.getInstance();
 
     TextView textview = new TextView(this);
     textview.setText("Scanning goes here");
@@ -30,11 +35,13 @@ public class ScanActivity extends Activity {
         }
         
         Thingy thingy = new Thingy().setName("scanned thingy whoo!");
+        _repository.addThingy(thingy);
+        
         returnScannedThingy(thingy);
       }
 
-      private void returnScannedThingy(Thingy thingy) { 
-        Intent data = new Intent(ScanActivity.this, ScanActivity.class).putExtra("thingy", thingy.getName());
+      private void returnScannedThingy(Thingy thingy) {
+        Intent data = new Intent(ScanActivity.this, getClass()).putExtra("thingy", thingy.getName());
         setResult(RESULT_OK, data);
         finish();
       }

### 2012-04-22 prototype/src/dk/itu/spcl/dex/ThingyActivity.java

@@ -16,6 +16,8 @@ public class ThingyActivity extends Activity {
 
     _thingy = Repository.getInstance().getThingy(
         getIntent().getStringExtra("thingy"));
+    
+    setTitle("Thingy: " +_thingy.getName());
 
     TextView textview = new TextView(this);
     textview.setText("UI for " + _thingy.getName() + " goes here!");

### 2012-04-22 prototype/src/dk/itu/spcl/dex/ThingyListActivity.java

@@ -21,11 +21,15 @@ public class ThingyListActivity extends ListActivity {
   private final int SCAN_FOR_THINGY_REQUEST_CODE = 1;
   private ArrayAdapter<Thingy> _listAdapter;
   private Repository.UpdateListener _updateListener;
+  private boolean _selectionMode;
 
   @Override
   protected void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
     _repository = Repository.getInstance();
+
+    _selectionMode = getIntent().getBooleanExtra("selectionMode", false);
+
     populateThingyList();
     addRepositoryListener();
     addListSelectionListener();
@@ -60,9 +64,23 @@ public class ThingyListActivity extends ListActivity {
       public void onItemClick(AdapterView<?> parent, View view, int position,
           long id) {
         Thingy thingy = (Thingy) parent.getItemAtPosition(position);
-        startThingyActivity(thingy);
+        onThingySelected(thingy);
       }
     });
+  }
+
+  private void onThingySelected(Thingy thingy) {
+    if (_selectionMode) {
+      returnThingy(thingy);
+    } else {
+      startThingyActivity(thingy);
+    }
+  }
+
+  private void returnThingy(Thingy thingy) {
+    Intent data = new Intent(this, getClass()).putExtra("thingy", thingy.getName());
+    setResult(RESULT_OK, data);
+    finish();
   }
 
   private void startThingyActivity(Thingy thingy) {
@@ -104,8 +122,7 @@ public class ThingyListActivity extends ListActivity {
   protected void onActivityResult(int requestCode, int resultCode, Intent data) {
     // super.onActivityResult(requestCode, resultCode, data);
     if (resultCode != RESULT_CANCELED) {
-      Thingy newThingy = (Thingy) data.getExtras().get("thingy");
-      _repository.addThingy(newThingy);
+      // thingy added to repo already, nothing to do!
     }
   }
 

### 2012-04-22 prototype/src/dk/itu/spcl/dex/PresetActivity.java
preset creation

@@ -1,83 +1,87 @@
 package dk.itu.spcl.dex;
 
+import java.util.ArrayList;
+
 import android.app.Activity;
 import android.content.Intent;
 import android.os.Bundle;
-import android.view.Menu;
-import android.view.MenuInflater;
-import android.view.MenuItem;
+import android.view.View;
+import android.widget.AdapterView;
 import android.widget.ArrayAdapter;
 import android.widget.ListView;
+import android.widget.AdapterView.OnItemClickListener;
 import dk.itu.spcl.dex.model.Preset;
 import dk.itu.spcl.dex.model.Repository;
 import dk.itu.spcl.dex.model.Thingy;
 
 public class PresetActivity extends Activity {
-  
+
   private static final int PICK_THINGY_REQUEST_CODE = 1;
   private Preset _preset;
   private Repository _repository;
   private ArrayAdapter<Thingy> _listAdapter;
-  
+
   @Override
   protected void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
     setContentView(R.layout.preset);
-    
+
     _repository = Repository.getInstance();
-    
-    _preset = Repository.getInstance().getPreset(getIntent().getStringExtra("preset"));
+
+    _preset = Repository.getInstance().getPreset(
+        getIntent().getStringExtra("preset"));
     setTitle("Preset: " + _preset.getName());
-    populateThingyList();
-  }
-  
-  private void populateThingyList() {
-    _listAdapter = new ArrayAdapter<Thingy>(this, R.layout.default_list_item,
-        _preset.getThingies());
-    ListView listView = (ListView)findViewById(R.id.presetThingyList);
-    listView.setAdapter(_listAdapter);
+    initializeThingyList();
+    addListSelectionListener();
   }
 
-  @Override
-  public boolean onCreateOptionsMenu(Menu menu) {
-    MenuInflater inflater = getMenuInflater();
-    inflater.inflate(R.menu.presetmenu, menu);
-    return true;
+  private void addListSelectionListener() {
+    ListView listView = (ListView) findViewById(R.id.presetThingyList);
+    listView.setOnItemClickListener(new OnItemClickListener() {
+      public void onItemClick(AdapterView<?> parent, View view, int position,
+          long id) {
+        Thingy thingy = (Thingy) parent.getItemAtPosition(position);
+        onThingySelected(thingy);
+      }
+    });
   }
-  
-  @Override
[…]

### 2012-04-22 prototype/src/dk/itu/spcl/dex/PresetListActivity.java

@@ -1,15 +1,17 @@
 package dk.itu.spcl.dex;
 
+import java.util.ArrayList;
+
+import android.app.AlertDialog;
 import android.app.ListActivity;
+import android.content.DialogInterface;
 import android.content.Intent;
 import android.os.Bundle;
-import android.view.Menu;
-import android.view.MenuInflater;
-import android.view.MenuItem;
 import android.view.View;
 import android.widget.AdapterView;
 import android.widget.AdapterView.OnItemClickListener;
 import android.widget.ArrayAdapter;
+import android.widget.EditText;
 import android.widget.ListView;
 import dk.itu.spcl.dex.model.Preset;
 import dk.itu.spcl.dex.model.Repository;
@@ -25,7 +27,7 @@ public class PresetListActivity extends ListActivity {
   protected void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
     _repository = Repository.getInstance();
-    populatePresetList();
+    initializePresetList();
     addRepositoryListener();
     addListSelectionListener();
   }
@@ -40,10 +42,12 @@ public class PresetListActivity extends ListActivity {
     _updateListener = new UpdateListener() {
       @Override
       public void repositoryUpdated() {
-        _listAdapter.clear();
-        for (Preset p : _repository.getPresets())
-          _listAdapter.add(p);
-        _listAdapter.notifyDataSetChanged();
+        runOnUiThread(new Runnable() {
+          @Override
+          public void run() {
+            populatePresetList();
+          }
+        });
       }
     };
     _repository.addUpdateListener(_updateListener);
@@ -59,9 +63,16 @@ public class PresetListActivity extends ListActivity {
       public void onItemClick(AdapterView<?> parent, View view, int position,
           long id) {
         Preset preset = (Preset) parent.getItemAtPosition(position);
-        startPresetActivity(preset);
+        onPresetSelected(preset);
       }
     });
+  }
+
+  private void onPresetSelected(Preset preset) {
+    if (preset != _repository.getDummyPreset())
+      startPresetActivity(preset);
+    else
+      newPreset();
   }
 
   private void startPresetActivity(Preset preset) {
@@ -70,32 +81,49 @@ public class PresetListActivity extends ListActivity {
     startActivity(intent);
   }
 
-  private void populatePresetList() {
+  private void initializePresetList() {
[…]

### 2012-04-22 prototype/src/dk/itu/spcl/dex/ScanActivity.java

@@ -48,5 +48,4 @@ public class ScanActivity extends Activity {
     });
     scanThread.start();
   }
-
 }

### 2012-04-22 prototype/src/dk/itu/spcl/dex/ThingyListActivity.java

@@ -1,11 +1,10 @@
 package dk.itu.spcl.dex;
 
+import java.util.ArrayList;
+
 import android.app.ListActivity;
 import android.content.Intent;
 import android.os.Bundle;
-import android.view.Menu;
-import android.view.MenuInflater;
-import android.view.MenuItem;
 import android.view.View;
 import android.widget.AdapterView;
 import android.widget.AdapterView.OnItemClickListener;
@@ -29,8 +28,10 @@ public class ThingyListActivity extends ListActivity {
     _repository = Repository.getInstance();
 
     _selectionMode = getIntent().getBooleanExtra("selectionMode", false);
+    if (_selectionMode)
+      setTitle("Select a thingy");
 
-    populateThingyList();
+    initializeThingyList();
     addRepositoryListener();
     addListSelectionListener();
   }
@@ -45,10 +46,12 @@ public class ThingyListActivity extends ListActivity {
     _updateListener = new UpdateListener() {
       @Override
       public void repositoryUpdated() {
-        _listAdapter.clear();
-        for (Thingy t : _repository.getThingies())
-          _listAdapter.add(t);
-        _listAdapter.notifyDataSetChanged();
+        runOnUiThread(new Runnable() {
+          @Override
+          public void run() {
+            populateThingyList();
+          }
+        });
       }
     };
     _repository.addUpdateListener(_updateListener);
@@ -72,13 +75,16 @@ public class ThingyListActivity extends ListActivity {
   private void onThingySelected(Thingy thingy) {
     if (_selectionMode) {
       returnThingy(thingy);
+    } else if (thingy == _repository.getDummyThingy()) {
+      newThingy();
     } else {
       startThingyActivity(thingy);
     }
   }
 
   private void returnThingy(Thingy thingy) {
-    Intent data = new Intent(this, getClass()).putExtra("thingy", thingy.getName());
+    Intent data = new Intent(this, getClass()).putExtra("thingy",
+        thingy.getName());
     setResult(RESULT_OK, data);
     finish();
   }
@@ -89,28 +95,21 @@ public class ThingyListActivity extends ListActivity {
     startActivity(intent);
   }
 
-  private void populateThingyList() {
+  private void initializeThingyList() {
     _listAdapter = new ArrayAdapter<Thingy>(this, R.layout.default_list_item,
-        _repository.getThingies());
+        new ArrayList<Thingy>());
[…]

### 2012-04-22 prototype/src/dk/itu/spcl/dex/model/Preset.java

@@ -2,34 +2,39 @@ package dk.itu.spcl.dex.model;
 
 import java.util.ArrayList;
 
-public class Preset {
-  
+public class Preset implements Comparable<Preset> {
+
   private ArrayList<Thingy> _thingies;
   private String _name;
-  
+
   public Preset() {
-    _thingies = new ArrayList<Thingy>(); 
+    _thingies = new ArrayList<Thingy>();
   }
- 
+
   public Preset setName(String name) {
     _name = name;
     return this;
   }
-  
+
   public String getName() {
     return _name;
   }
-  
+
   public void addThingy(Thingy t) {
     _thingies.add(t);
   }
-  
+
   public ArrayList<Thingy> getThingies() {
     return _thingies;
   }
-  
+
   @Override
   public String toString() {
     return getName();
+  }
+
+  @Override
+  public int compareTo(Preset another) {
+    return getName().compareTo(another.getName());
   }
 }

### 2012-04-22 prototype/src/dk/itu/spcl/dex/model/Repository.java

@@ -1,6 +1,8 @@
 package dk.itu.spcl.dex.model;
 
 import java.util.ArrayList;
+import java.util.Collections;
+import java.util.Comparator;
 import java.util.HashMap;
 
 public class Repository {
@@ -58,11 +60,15 @@ public class Repository {
   }
 
   public ArrayList<Preset> getPresets() {
-    return new ArrayList<Preset>(_presets.values());
+    ArrayList<Preset> list = new ArrayList<Preset>(_presets.values());
+    Collections.sort(list);
+    return list;
   }
   
   public ArrayList<Thingy> getThingies() {
-    return new ArrayList<Thingy>(_thingies.values());
+    ArrayList<Thingy> list = new ArrayList<Thingy>(_thingies.values());
+    Collections.sort(list);
+    return list;
   }
   
   public Thingy getThingy(String name) {
@@ -71,6 +77,26 @@ public class Repository {
   
   public Preset getPreset(String name) {
     return _presets.get(name);
+  }
+  
+  private Preset _dummyPreset;
+  
+  private Thingy _dummyThingy;
+  
+  
+  public Preset getDummyPreset() {
+    if (_dummyPreset == null) {
+      _dummyPreset = new Preset().setName("New preset...");
+    }
+    
+    return _dummyPreset;
+  }
+  
+  public Thingy getDummyThingy() {
+    if (_dummyThingy == null) {
+      _dummyThingy = new Thingy().setName("Add thingy...");
+    }
+    return _dummyThingy;
   }
 
 }

### 2012-04-22 prototype/src/dk/itu/spcl/dex/model/Thingy.java

@@ -1,6 +1,6 @@
 package dk.itu.spcl.dex.model;
 
-public class Thingy {
+public class Thingy implements Comparable<Thingy> {
 
   private String _name;
 
@@ -19,5 +19,10 @@ public class Thingy {
   @Override
   public String toString() {
     return getName();
+  }
+
+  @Override
+  public int compareTo(Thingy another) {
+    return getName().compareTo(another.getName());
   }
 }

### 2012-04-22 prototype/gen/dk/itu/spcl/dex/R.java
list icons

@@ -15,10 +15,11 @@ public final class R {
         public static final int ic_tab_default=0x7f020001;
     }
     public static final class id {
-        public static final int addThingyMenu=0x7f060002;
-        public static final int newPresetMenu=0x7f060001;
-        public static final int newThingyMenu=0x7f060003;
-        public static final int presetThingyList=0x7f060000;
+        public static final int addThingyMenu=0x7f060003;
+        public static final int listTextView=0x7f060000;
+        public static final int newPresetMenu=0x7f060002;
+        public static final int newThingyMenu=0x7f060004;
+        public static final int presetThingyList=0x7f060001;
     }
     public static final class layout {
         public static final int default_list_item=0x7f030000;

### 2012-04-22 prototype/src/dk/itu/spcl/dex/PresetActivity.java

@@ -7,9 +7,9 @@ import android.content.Intent;
 import android.os.Bundle;
 import android.view.View;
 import android.widget.AdapterView;
+import android.widget.AdapterView.OnItemClickListener;
 import android.widget.ArrayAdapter;
 import android.widget.ListView;
-import android.widget.AdapterView.OnItemClickListener;
 import dk.itu.spcl.dex.model.Preset;
 import dk.itu.spcl.dex.model.Repository;
 import dk.itu.spcl.dex.model.Thingy;
@@ -19,7 +19,7 @@ public class PresetActivity extends Activity {
   private static final int PICK_THINGY_REQUEST_CODE = 1;
   private Preset _preset;
   private Repository _repository;
-  private ArrayAdapter<Thingy> _listAdapter;
+  private CustomArrayAdapter<Thingy> _listAdapter;
 
   @Override
   protected void onCreate(Bundle savedInstanceState) {
@@ -52,8 +52,8 @@ public class PresetActivity extends Activity {
   }
 
   private void initializeThingyList() {
-    _listAdapter = new ArrayAdapter<Thingy>(this, R.layout.default_list_item,
-        new ArrayList<Thingy>());
+    _listAdapter = new CustomArrayAdapter<Thingy>(this,
+        R.layout.default_list_item, R.id.listTextView, new ArrayList<Thingy>());
     ListView listView = (ListView) findViewById(R.id.presetThingyList);
     listView.setAdapter(_listAdapter);
 
@@ -78,7 +78,8 @@ public class PresetActivity extends Activity {
   protected void onActivityResult(int requestCode, int resultCode, Intent data) {
     // super.onActivityResult(requestCode, resultCode, data);
     if (resultCode != RESULT_CANCELED) {
-      Thingy selected = _repository.getThingy(data.getExtras().getString("thingy"));
+      Thingy selected = _repository.getThingy(data.getExtras().getString(
+          "thingy"));
       _preset.addThingy(selected);
       populateThingyList();
     }

### 2012-04-22 prototype/src/dk/itu/spcl/dex/PresetListActivity.java

@@ -10,7 +10,6 @@ import android.os.Bundle;
 import android.view.View;
 import android.widget.AdapterView;
 import android.widget.AdapterView.OnItemClickListener;
-import android.widget.ArrayAdapter;
 import android.widget.EditText;
 import android.widget.ListView;
 import dk.itu.spcl.dex.model.Preset;
@@ -20,7 +19,7 @@ import dk.itu.spcl.dex.model.Repository.UpdateListener;
 public class PresetListActivity extends ListActivity {
 
   private Repository _repository;
-  private ArrayAdapter<Preset> _listAdapter;
+  private CustomArrayAdapter<Preset> _listAdapter;
   private Repository.UpdateListener _updateListener;
 
   @Override
@@ -82,8 +81,8 @@ public class PresetListActivity extends ListActivity {
   }
 
   private void initializePresetList() {
-    _listAdapter = new ArrayAdapter<Preset>(this, R.layout.default_list_item,
-        new ArrayList<Preset>());
+    _listAdapter = new CustomArrayAdapter<Preset>(this,
+        R.layout.default_list_item, R.id.listTextView, new ArrayList<Preset>());
     setListAdapter(_listAdapter);
 
     populatePresetList();

### 2012-04-22 prototype/src/dk/itu/spcl/dex/ThingyListActivity.java

@@ -8,7 +8,6 @@ import android.os.Bundle;
 import android.view.View;
 import android.widget.AdapterView;
 import android.widget.AdapterView.OnItemClickListener;
-import android.widget.ArrayAdapter;
 import android.widget.ListView;
 import dk.itu.spcl.dex.model.Repository;
 import dk.itu.spcl.dex.model.Repository.UpdateListener;
@@ -18,7 +17,7 @@ public class ThingyListActivity extends ListActivity {
 
   private Repository _repository;
   private final int SCAN_FOR_THINGY_REQUEST_CODE = 1;
-  private ArrayAdapter<Thingy> _listAdapter;
+  private CustomArrayAdapter<Thingy> _listAdapter;
   private Repository.UpdateListener _updateListener;
   private boolean _selectionMode;
 
@@ -96,8 +95,8 @@ public class ThingyListActivity extends ListActivity {
   }
 
   private void initializeThingyList() {
-    _listAdapter = new ArrayAdapter<Thingy>(this, R.layout.default_list_item,
-        new ArrayList<Thingy>());
+    _listAdapter = new CustomArrayAdapter<Thingy>(this,
+        R.layout.default_list_item, R.id.listTextView, new ArrayList<Thingy>());
     setListAdapter(_listAdapter);
 
     populateThingyList();

### 2012-04-22 prototype/src/dk/itu/spcl/dex/model/Repository.java

@@ -2,7 +2,6 @@ package dk.itu.spcl.dex.model;
 
 import java.util.ArrayList;
 import java.util.Collections;
-import java.util.Comparator;
 import java.util.HashMap;
 
 public class Repository {

### 2012-04-22 DEX-wizard/DEX-wizard/AsynchronousSocketListener.cs
simple wizard server

@@ -1,0 +1,151 @@
+﻿using System;
+using System.Collections.Generic;
+using System.Linq;
+using System.Text;
+
+namespace DEX_wizard
+{
+    public class AsynchronousSocketListener
+    {
+        // Thread signal.
+        public static ManualResetEvent allDone = new ManualResetEvent(false);
+
+        public AsynchronousSocketListener()
+        {
+        }
+
+        public static void StartListening()
+        {
+            // Data buffer for incoming data.
+            byte[] bytes = new Byte[1024];
+
+            // Establish the local endpoint for the socket.
+            // The DNS name of the computer
+            // running the listener is "host.contoso.com".
+            IPHostEntry ipHostInfo = Dns.Resolve(Dns.GetHostName());
+            IPAddress ipAddress = ipHostInfo.AddressList[0];
+            IPEndPoint localEndPoint = new IPEndPoint(ipAddress, 11000);
+
+            // Create a TCP/IP socket.
+            Socket listener = new Socket(AddressFamily.InterNetwork,
+                SocketType.Stream, ProtocolType.Tcp);
+
+            // Bind the socket to the local endpoint and listen for incoming connections.
+            try
+            {
+                listener.Bind(localEndPoint);
+                listener.Listen(100);
+
+                while (true)
+                {
+                    // Set the event to nonsignaled state.
+                    allDone.Reset();
+
+                    // Start an asynchronous socket to listen for connections.
+                    Console.WriteLine("Waiting for a connection...");
+                    listener.BeginAccept(
+                        new AsyncCallback(AcceptCallback),
+                        listener);
+
+                    // Wait until a connection is made before continuing.
+                    allDone.WaitOne();
+                }
+
+            }
+            catch (Exception e)
+            {
+                Console.WriteLine(e.ToString());
+            }
+
+            Console.WriteLine("\nPress ENTER to continue...");
+            Console.Read();
+
+        }
+
+        public static void AcceptCallback(IAsyncResult ar)
+        {
+            // Signal the main thread to continue.
+            allDone.Set();
+
+            // Get the socket that handles the client request.
+            Socket listener = (Socket)ar.AsyncState;
+            Socket handler = listener.EndAccept(ar);
+
+            // Create the state object.
+            StateObject state = new StateObject();
+            state.workSocket = handler;
+            handler.BeginReceive(state.buffer, 0, StateObject.BufferSize, 0,
+                new AsyncCallback(ReadCallback), state);
+        }
+
+        public static void ReadCallback(IAsyncResult ar)
+        {
[…]

### 2012-04-22 DEX-wizard/DEX-wizard/Program.cs

@@ -1,0 +1,46 @@
+﻿using System;
+using System.Net;
+using System.Net.Sockets;
+using System.Text;
+using System.Threading;
+
+namespace DEX_wizard
+{
+    class Program
+    {
+        static void Main(string[] args)
+        {
+            bool running = true;
+
+            // IPAddress ipAddress = Dns.Resolve(Dns.GetHostName()).AddressList[0];
+            IPAddress ipAddress = IPAddress.Parse(args[0]);
+            IPEndPoint ipLocalEndPoint = new IPEndPoint(ipAddress, int.Parse(args[1]));
+            TcpListener server = new TcpListener(ipLocalEndPoint);
+            server.Start();
+
+            // listen for client
+            Console.WriteLine("Listening for cilent . . .");
+            TcpClient client = server.AcceptTcpClient();
+            NetworkStream stream = client.GetStream();
+            Console.WriteLine("Client connected. {0}", client.ToString());
+
+            while (running)
+            {
+                string data = Console.ReadLine();
+                if (data.StartsWith("quit"))
+                {
+                    running = false;
+                    break;
+                }
+                Console.WriteLine("Sending: {0}", data);
+                data += "\n\r";
+                Byte[] buffer = Encoding.ASCII.GetBytes(data);
+                stream.Write(buffer, 0, buffer.Length);
+            }
+
+            Console.WriteLine("exiting...");
+            client.Close();
+            server.Stop();
+        }
+    }
+}

### 2012-04-22 DEX-wizard/DEX-wizard/Properties/AssemblyInfo.cs

@@ -1,0 +1,36 @@
+﻿using System.Reflection;
+using System.Runtime.CompilerServices;
+using System.Runtime.InteropServices;
+
+// General Information about an assembly is controlled through the following 
+// set of attributes. Change these attribute values to modify the information
+// associated with an assembly.
+[assembly: AssemblyTitle("DEX-wizard")]
+[assembly: AssemblyDescription("")]
+[assembly: AssemblyConfiguration("")]
+[assembly: AssemblyCompany("Microsoft")]
+[assembly: AssemblyProduct("DEX-wizard")]
+[assembly: AssemblyCopyright("Copyright © Microsoft 2012")]
+[assembly: AssemblyTrademark("")]
+[assembly: AssemblyCulture("")]
+
+// Setting ComVisible to false makes the types in this assembly not visible 
+// to COM components.  If you need to access a type in this assembly from 
+// COM, set the ComVisible attribute to true on that type.
+[assembly: ComVisible(false)]
+
+// The following GUID is for the ID of the typelib if this project is exposed to COM
+[assembly: Guid("a02875be-bc3a-4649-9c33-59db1bec3d53")]
+
+// Version information for an assembly consists of the following four values:
+//
+//      Major Version
+//      Minor Version 
+//      Build Number
+//      Revision
+//
+// You can specify all the values or you can default the Build and Revision Numbers 
+// by using the '*' as shown below:
+// [assembly: AssemblyVersion("1.0.*")]
+[assembly: AssemblyVersion("1.0.0.0")]
+[assembly: AssemblyFileVersion("1.0.0.0")]

### 2012-04-22 prototype/src/dk/itu/spcl/dex/CustomArrayAdapter.java
list icons

@@ -1,0 +1,53 @@
+package dk.itu.spcl.dex;
+
+import java.util.List;
+
+import android.content.Context;
+import android.graphics.Rect;
+import android.graphics.drawable.Drawable;
+import android.view.View;
+import android.view.ViewGroup;
+import android.widget.ArrayAdapter;
+import android.widget.TextView;
+import dk.itu.spcl.dex.model.Preset;
+import dk.itu.spcl.dex.model.Repository;
+import dk.itu.spcl.dex.model.Thingy;
+
+public class CustomArrayAdapter<T> extends ArrayAdapter<T> {
+
+  private Repository _repository;
+  private int _textViewResourceId;
+
+  public CustomArrayAdapter(Context context, int resource,
+      int textViewResourceId, List<T> objects) {
+    super(context, resource, textViewResourceId, objects);
+    _textViewResourceId = textViewResourceId;
+    _repository = Repository.getInstance();
+  }
+
+  @Override
+  public View getView(int position, View convertView, ViewGroup parent) {
+    View itemView = super.getView(position, convertView, parent);
+    TextView textView = (TextView) itemView.findViewById(_textViewResourceId);
+    Drawable icon = getDrawableForListItem(getItem(position));
+    if (icon != null)
+      icon.setBounds(new Rect(0, 0, 20, 24));
+    textView.setCompoundDrawables(icon, null, null, null);
+    return itemView;
+  }
+
+  private Drawable getDrawableForListItem(T listItem) {
+    if (listItem == _repository.getDummyPreset()
+        || listItem == _repository.getDummyThingy())
+      return getContext().getResources().getDrawable(
+          android.R.drawable.ic_input_add);
+    else if (listItem instanceof Preset)
+      return null;
+    else if (listItem instanceof Thingy)
+      return null;
+    else
+      return null;
+
+  }
+
+}

### 2012-04-22 prototype/src/dk/itu/spcl/dex/PresetActivity.java

@@ -8,7 +8,6 @@ import android.os.Bundle;
 import android.view.View;
 import android.widget.AdapterView;
 import android.widget.AdapterView.OnItemClickListener;
-import android.widget.ArrayAdapter;
 import android.widget.ListView;
 import dk.itu.spcl.dex.model.Preset;
 import dk.itu.spcl.dex.model.Repository;

### 2012-04-22 prototype/src/dk/itu/spcl/dex/model/Repository.java

@@ -17,7 +17,11 @@ public class Repository {
   private ArrayList<UpdateListener> _updateListeners = new ArrayList<Repository.UpdateListener>();
 
   private Repository() {
-    // test data
+    //addTestData();
+  }
+
+  @SuppressWarnings("unused")
+  private void addTestData() {
     addThingy(new Thingy().setName("test thingy"));
     addThingy(new Thingy().setName("other thingy"));
     addThingy(new Thingy().setName("third thingy"));

### 2012-04-23 prototype/src/dk/itu/spcl/dex/PresetActivity.java
adding url & status to thingies for wizardry

@@ -19,6 +19,7 @@ public class PresetActivity extends Activity {
   private Preset _preset;
   private Repository _repository;
   private CustomArrayAdapter<Thingy> _listAdapter;
+  private Repository.Listener _repositoryListener;  
 
   @Override
   protected void onCreate(Bundle savedInstanceState) {
@@ -32,7 +33,39 @@ public class PresetActivity extends Activity {
     setTitle("Preset: " + _preset.getName());
     initializeThingyList();
     addListSelectionListener();
+    addRepositoryListener();
   }
+  
+  @Override
+  protected void onDestroy() {
+    removeRepositoryListener();
+    super.onDestroy();
+  }
+  
+  private void addRepositoryListener() {
+    _repositoryListener = new Repository.Listener() {
+      @Override
+      public void structureChanged() {
+        // don't care
+      }
+
+      @Override
+      public void statusChanged() {
+        runOnUiThread(new Runnable() {
+          @Override
+          public void run() {
+            _listAdapter.notifyDataSetChanged();
+          }
+        });
+      }
+    };
+    _repository.addUpdateListener(_repositoryListener);
+  }
+
+  private void removeRepositoryListener() {
+    _repository.removeUpdateListener(_repositoryListener);
+  }
+
 
   private void addListSelectionListener() {
     ListView listView = (ListView) findViewById(R.id.presetThingyList);

### 2012-04-23 prototype/src/dk/itu/spcl/dex/PresetListActivity.java

@@ -14,13 +14,13 @@ import android.widget.EditText;
 import android.widget.ListView;
 import dk.itu.spcl.dex.model.Preset;
 import dk.itu.spcl.dex.model.Repository;
-import dk.itu.spcl.dex.model.Repository.UpdateListener;
+import dk.itu.spcl.dex.model.Repository.Listener;
 
 public class PresetListActivity extends ListActivity {
 
   private Repository _repository;
   private CustomArrayAdapter<Preset> _listAdapter;
-  private Repository.UpdateListener _updateListener;
+  private Repository.Listener _updateListener;
 
   @Override
   protected void onCreate(Bundle savedInstanceState) {
@@ -38,15 +38,20 @@ public class PresetListActivity extends ListActivity {
   }
 
   private void addRepositoryListener() {
-    _updateListener = new UpdateListener() {
+    _updateListener = new Listener() {
       @Override
-      public void repositoryUpdated() {
+      public void structureChanged() {
         runOnUiThread(new Runnable() {
           @Override
           public void run() {
             populatePresetList();
           }
         });
+      }
+
+      @Override
+      public void statusChanged() {
+        // don't care
       }
     };
     _repository.addUpdateListener(_updateListener);

### 2012-04-23 prototype/src/dk/itu/spcl/dex/ThingyListActivity.java

@@ -10,7 +10,7 @@ import android.widget.AdapterView;
 import android.widget.AdapterView.OnItemClickListener;
 import android.widget.ListView;
 import dk.itu.spcl.dex.model.Repository;
-import dk.itu.spcl.dex.model.Repository.UpdateListener;
+import dk.itu.spcl.dex.model.Repository.Listener;
 import dk.itu.spcl.dex.model.Thingy;
 
 public class ThingyListActivity extends ListActivity {
@@ -18,7 +18,7 @@ public class ThingyListActivity extends ListActivity {
   private Repository _repository;
   private final int SCAN_FOR_THINGY_REQUEST_CODE = 1;
   private CustomArrayAdapter<Thingy> _listAdapter;
-  private Repository.UpdateListener _updateListener;
+  private Repository.Listener _repositoryListener;
   private boolean _selectionMode;
 
   @Override
@@ -38,13 +38,13 @@ public class ThingyListActivity extends ListActivity {
   @Override
   protected void onDestroy() {
     super.onDestroy();
-    removeUpdateListener();
+    removeRepositoryListener();
   }
 
   private void addRepositoryListener() {
-    _updateListener = new UpdateListener() {
+    _repositoryListener = new Listener() {
       @Override
-      public void repositoryUpdated() {
+      public void structureChanged() {
         runOnUiThread(new Runnable() {
           @Override
           public void run() {
@@ -52,12 +52,22 @@ public class ThingyListActivity extends ListActivity {
           }
         });
       }
+
+      @Override
+      public void statusChanged() {
+        runOnUiThread(new Runnable() {
+          @Override
+          public void run() {
+            _listAdapter.notifyDataSetChanged();
+          }
+        });
+      }
     };
-    _repository.addUpdateListener(_updateListener);
+    _repository.addUpdateListener(_repositoryListener);
   }
 
-  private void removeUpdateListener() {
-    _repository.removeUpdateListener(_updateListener);
+  private void removeRepositoryListener() {
+    _repository.removeUpdateListener(_repositoryListener);
   }
 
   private void addListSelectionListener() {

### 2012-04-23 prototype/src/dk/itu/spcl/dex/model/Repository.java

@@ -6,15 +6,16 @@ import java.util.HashMap;
 
 public class Repository {
 
-  public interface UpdateListener {
-    public void repositoryUpdated();
+  public interface Listener {
+    public void structureChanged();
+    public void statusChanged();
   }
 
   HashMap<String, Thingy> _thingies = new HashMap<String, Thingy>();
   HashMap<String, Preset> _presets = new HashMap<String, Preset>();
 
   private static Repository _instance;
-  private ArrayList<UpdateListener> _updateListeners = new ArrayList<Repository.UpdateListener>();
+  private ArrayList<Listener> _updateListeners = new ArrayList<Repository.Listener>();
 
   private Repository() {
     //addTestData();
@@ -32,11 +33,11 @@ public class Repository {
     addPreset(samplePreset);
   }
 
-  public void addUpdateListener(UpdateListener listener) {
+  public void addUpdateListener(Listener listener) {
     _updateListeners.add(listener);
   }
 
-  public void removeUpdateListener(UpdateListener listener) {
+  public void removeUpdateListener(Listener listener) {
     _updateListeners.remove(listener);
   }
 
@@ -48,17 +49,23 @@ public class Repository {
 
   public void addThingy(Thingy t) {
     _thingies.put(t.getName(), t);
-    onUpdate();
+    onStructureChanged();
   }
 
   public void addPreset(Preset p) {
     _presets.put(p.getName(), p);
-    onUpdate();
+    onStructureChanged();
   }
 
-  private void onUpdate() {
-    for (UpdateListener listener : _updateListeners) {
-      listener.repositoryUpdated();
+  private void onStructureChanged() {
+    for (Listener listener : _updateListeners) {
+      listener.structureChanged();
+    }
+  }
+  
+  public void onStatusChanged() {
+    for (Listener listener : _updateListeners) {
+     listener.statusChanged(); 
     }
   }
 

### 2012-04-23 prototype/src/dk/itu/spcl/dex/model/Thingy.java

@@ -3,18 +3,44 @@ package dk.itu.spcl.dex.model;
 public class Thingy implements Comparable<Thingy> {
 
   private String _name;
+  private String _url;
+  private boolean _status;
 
   public Thingy() {
   }
+  
+  // properties
 
   public String getName() {
     return _name;
   }
-
+  
   public Thingy setName(String name) {
     _name = name;
     return this;
   }
+  
+  public String getUrl() {
+    return _url;
+  }
+  
+  public Thingy setUrl(String url) {
+    _url = url;
+    return this;
+  }
+  
+  // status (to be expanded)
+  
+  public boolean getStatus() {
+    return _status;
+  }
+  
+  public Thingy setStatus(boolean status) {
+    _status = status;
+    return this;
+  }
+  
+  // standard overrides
 
   @Override
   public String toString() {

### 2012-04-23 prototype/src/dk/itu/spcl/dex/model/ThingyUpdateService.java

@@ -1,0 +1,98 @@
+package dk.itu.spcl.dex.model;
+
+import java.io.IOException;
+
+import org.apache.http.client.ClientProtocolException;
+import org.apache.http.client.HttpClient;
+import org.apache.http.client.ResponseHandler;
+import org.apache.http.client.methods.HttpGet;
+import org.apache.http.impl.client.BasicResponseHandler;
+import org.apache.http.impl.client.DefaultHttpClient;
+
+import android.app.Service;
+import android.content.Intent;
+import android.os.IBinder;
+
+public class ThingyUpdateService extends Service implements Runnable {
+
+  private Thread _thread;
+  private boolean _running;
+  private final static int UPDATE_INTERVAL = 2000;
+  private Repository _repository;
+
+  @Override
+  public void onCreate() {
+    super.onCreate();
+    _repository = Repository.getInstance();
+  }
+
+  @Override
+  public int onStartCommand(Intent intent, int flags, int startId) {
+    startBackgroundUpdates();
+    return START_STICKY;
+  }
+
+  private void startBackgroundUpdates() {
+    _thread = new Thread(this);
+    _running = true;
+    _thread.start();
+  }
+
+  @Override
+  public IBinder onBind(Intent intent) {
+    return null;
+  }
+
+  @Override
+  public void run() {
+    while (_running) {
+      update();
+      pause();
+    }
+  }
+
+  private void update() {
+    for (Thingy thingy : _repository.getThingies())
+      updateThingy(thingy);
+
+    _repository.onStatusChanged();
+  }
+
+  private void updateThingy(Thingy thingy) {
+    try {
+      boolean thingyStatus = getStatusFromUrl(thingy.getUrl());
+      thingy.setStatus(thingyStatus);
+    } catch (ClientProtocolException e) {
+      e.printStackTrace();
+    } catch (IOException e) {
+      e.printStackTrace();
+    }
+  }
+
+  private boolean getStatusFromUrl(String url) throws ClientProtocolException,
+      IOException {
+    HttpClient httpClient = new DefaultHttpClient();
+    HttpGet get = new HttpGet(url);
+    ResponseHandler<String> resp = new BasicResponseHandler();
+    String responseText = httpClient.execute(get, resp);
+    return responseText.equals("true");
+  }
+
+  private void pause() {
+    try {
+      Thread.sleep(UPDATE_INTERVAL);
+    } catch (InterruptedException e) {
[…]

### 2012-04-23 prototype/src/dk/itu/spcl/dex/CustomArrayAdapter.java
showing thingy status from urls

@@ -29,25 +29,44 @@ public class CustomArrayAdapter<T> extends ArrayAdapter<T> {
   public View getView(int position, View convertView, ViewGroup parent) {
     View itemView = super.getView(position, convertView, parent);
     TextView textView = (TextView) itemView.findViewById(_textViewResourceId);
-    Drawable icon = getDrawableForListItem(getItem(position));
-    if (icon != null)
-      icon.setBounds(new Rect(0, 0, 20, 24));
-    textView.setCompoundDrawables(icon, null, null, null);
+    T item = getItem(position);
+    Drawable typeIcon = getTypeIconForListItem(item);
+    if (typeIcon != null)
+      typeIcon.setBounds(new Rect(0, 0, 20, 24));
+    Drawable statusIcon = getStatusIconForListItem(item);
+    if (statusIcon != null)
+      statusIcon.setBounds(new Rect(0, 0, 20, 24));
+    textView.setCompoundDrawables(typeIcon, null, statusIcon, null);
     return itemView;
   }
 
-  private Drawable getDrawableForListItem(T listItem) {
+  private Drawable getStatusIconForListItem(T item) {
+    if (!(item instanceof Thingy) || item == _repository.getDummyThingy())
+      return null;
+
+    Thingy thingy = (Thingy) item;
+    int iconId;
+    if (thingy.getStatus())
+      iconId = android.R.drawable.button_onoff_indicator_on;
+    else
+      iconId = android.R.drawable.button_onoff_indicator_off;
+    return getDrawableFromId(iconId);
+  }
+
+  private Drawable getDrawableFromId(int iconId) {
+    return getContext().getResources().getDrawable(iconId);
+  }
+
+  private Drawable getTypeIconForListItem(T listItem) {
     if (listItem == _repository.getDummyPreset()
         || listItem == _repository.getDummyThingy())
-      return getContext().getResources().getDrawable(
-          android.R.drawable.ic_input_add);
+      return getDrawableFromId(android.R.drawable.ic_input_add);
     else if (listItem instanceof Preset)
       return null;
     else if (listItem instanceof Thingy)
       return null;
     else
       return null;
-
   }
 
 }

### 2012-04-23 prototype/src/dk/itu/spcl/dex/HomeActivity.java

@@ -4,6 +4,7 @@ import android.app.TabActivity;
 import android.content.Intent;
 import android.content.res.Resources;
 import android.os.Bundle;
+import android.util.Log;
 import android.widget.TabHost;
 
 public class HomeActivity extends TabActivity {
@@ -11,8 +12,12 @@ public class HomeActivity extends TabActivity {
   public void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
     setContentView(R.layout.home);
-
     addTabs();
+    startUpdateService();
+  }
+
+  private void startUpdateService() {
+    startService(new Intent(this, ThingyUpdateService.class));
   }
 
   private void addTabs() {

### 2012-04-23 prototype/src/dk/itu/spcl/dex/ScanActivity.java

@@ -8,13 +8,13 @@ import dk.itu.spcl.dex.model.Repository;
 import dk.itu.spcl.dex.model.Thingy;
 
 public class ScanActivity extends Activity {
-  
+
   private Repository _repository;
 
   @Override
   protected void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
-    
+
     _repository = Repository.getInstance();
 
     TextView textview = new TextView(this);
@@ -23,6 +23,8 @@ public class ScanActivity extends Activity {
 
     performDummyScan();
   }
+
+  private static int _thingiesReturned = 0;
 
   private void performDummyScan() {
     Thread scanThread = new Thread(new Runnable() {
@@ -33,16 +35,35 @@ public class ScanActivity extends Activity {
           Thread.sleep(1500);
         } catch (InterruptedException e) {
         }
-        
-        Thingy thingy = new Thingy().setName("scanned thingy whoo!");
+
+        Thingy thingy = getMockThingy();
+
         _repository.addThingy(thingy);
-        
+
         returnScannedThingy(thingy);
       }
 
+      private Thingy getMockThingy() {
+        _thingiesReturned++;
+        if (_thingiesReturned == 1) {
+          return new Thingy().setName("Thingy one!").setUrl(
+              "http://anti.zno.dk/wizard/one");
+        } else if (_thingiesReturned == 2) {
+          return new Thingy().setName("Thingy two!").setUrl(
+              "http://anti.zno.dk/wizard/two");
+        } else {
+          return null;
+        }
+      }
+
       private void returnScannedThingy(Thingy thingy) {
-        Intent data = new Intent(ScanActivity.this, getClass()).putExtra("thingy", thingy.getName());
-        setResult(RESULT_OK, data);
+        if (thingy == null) {
+          setResult(RESULT_CANCELED);
+        } else {
+          Intent data = new Intent(ScanActivity.this, getClass()).putExtra(
+              "thingy", thingy.getName());
+          setResult(RESULT_OK, data);
+        }
         finish();
       }
     });

### 2012-04-23 prototype/src/dk/itu/spcl/dex/ThingyUpdateService.java

@@ -1,4 +1,4 @@
-package dk.itu.spcl.dex.model;
+package dk.itu.spcl.dex;
 
 import java.io.IOException;
 
@@ -9,9 +9,13 @@ import org.apache.http.client.methods.HttpGet;
 import org.apache.http.impl.client.BasicResponseHandler;
 import org.apache.http.impl.client.DefaultHttpClient;
 
+import dk.itu.spcl.dex.model.Repository;
+import dk.itu.spcl.dex.model.Thingy;
+
 import android.app.Service;
 import android.content.Intent;
 import android.os.IBinder;
+import android.util.Log;
 
 public class ThingyUpdateService extends Service implements Runnable {
 
@@ -23,11 +27,13 @@ public class ThingyUpdateService extends Service implements Runnable {
   @Override
   public void onCreate() {
     super.onCreate();
+    Log.i("dex", "Service created");
     _repository = Repository.getInstance();
   }
 
   @Override
   public int onStartCommand(Intent intent, int flags, int startId) {
+    System.out.println("* Service started!");
     startBackgroundUpdates();
     return START_STICKY;
   }
@@ -45,6 +51,7 @@ public class ThingyUpdateService extends Service implements Runnable {
 
   @Override
   public void run() {
+    Log.i("dex", "Run called");
     while (_running) {
       update();
       pause();
@@ -52,6 +59,7 @@ public class ThingyUpdateService extends Service implements Runnable {
   }
 
   private void update() {
+    Log.i("dex", "Updating");
     for (Thingy thingy : _repository.getThingies())
       updateThingy(thingy);
 
@@ -63,9 +71,9 @@ public class ThingyUpdateService extends Service implements Runnable {
       boolean thingyStatus = getStatusFromUrl(thingy.getUrl());
       thingy.setStatus(thingyStatus);
     } catch (ClientProtocolException e) {
-      e.printStackTrace();
+      Log.e("dex", e.toString());
     } catch (IOException e) {
-      e.printStackTrace();
+      Log.e("dex", e.toString());
     }
   }
 
@@ -75,7 +83,7 @@ public class ThingyUpdateService extends Service implements Runnable {
     HttpGet get = new HttpGet(url);
     ResponseHandler<String> resp = new BasicResponseHandler();
     String responseText = httpClient.execute(get, resp);
-    return responseText.equals("true");
+    return responseText.equals("1");
   }
 
   private void pause() {

### 2012-05-05 arduino/library/WiFly/WiFlyDevice.cpp
slightly modified WiFly library. examples/WebServer works.

@@ -1,0 +1,538 @@
+
+#include "WiFly.h"
+
+#define DEBUG_LEVEL 0
+
+#include "Debug.h"
+
+
+boolean WiFlyDevice::findInResponse(const char *toMatch,
+                                    unsigned int timeOut = 0) {
+  /*
+
+   */
+
+  // TODO: Change 'sendCommand' to use 'findInResponse' and have timeouts,
+  //       and then use 'sendCommand' in routines that call 'findInResponse'?
+
+  // TODO: Don't reset timer after successful character read? Or have two
+  //       types of timeout?
+
+  int byteRead;
+
+  unsigned int timeOutTarget; // in milliseconds
+
+
+  DEBUG_LOG(1, "Entered findInResponse");
+  DEBUG_LOG(2, "Want to match:");
+  DEBUG_LOG(2, toMatch);
+  DEBUG_LOG(3, "Found:");
+
+  for (unsigned int offset = 0; offset < strlen(toMatch); offset++) {
+
+    // Reset after successful character read
+    timeOutTarget = millis() + timeOut; // Doesn't handle timer wrapping
+
+    while (!uart.available()) {
+      // Wait, with optional time out.
+      if (timeOut > 0) {
+        if (millis() > timeOutTarget) {
+          return false;
+        }
+      }
+      delay(1); // This seems to improve reliability slightly
+    }
+
+    // We read this separately from the conditional statement so we can
+    // log the character read when debugging.
+    byteRead = uart.read();
+
+    delay(1); // Removing logging may affect timing slightly
+
+    DEBUG_LOG(5, "Offset:");
+    DEBUG_LOG(5, offset);
+    DEBUG_LOG(3, (char) byteRead);
+    DEBUG_LOG(4, byteRead);
+
+    if (byteRead != toMatch[offset]) {
+      offset = 0;
+      // Ignore character read if it's not a match for the start of the string
+      if (byteRead != toMatch[offset]) {
+        offset = -1;
+      }
+      continue;
+    }
+  }
+
+  return true;
+}
+
+
+
+boolean WiFlyDevice::responseMatched(const char *toMatch) {
+  /*
+   */
+  boolean matchFound = true;
+
+  DEBUG_LOG(3, "Entered responseMatched");
+
+  for (unsigned int offset = 0; offset < strlen(toMatch); offset++) {
+    while (!uart.available()) {
+      // Wait -- no timeout
+    }
[…]

### 2012-05-05 arduino/library/WiFly/examples/WiFly_WebServer/Credentials.h

@@ -1,0 +1,8 @@
+#ifndef __CREDENTIALS_H__
+#define __CREDENTIALS_H__
+
+// Wifi parameters
+char passphrase[] = "*snip*";
+char ssid[] = "lol$internets";
+
+#endif

### 2012-05-07 arduino/WindowThingy/Credentials.h
added Arduino code for window thingy. changes status on each request for now.

@@ -1,0 +1,8 @@
+#ifndef __CREDENTIALS_H__
+#define __CREDENTIALS_H__
+
+// Wifi parameters
+char passphrase[] = "*snip*";
+char ssid[] = "lol$internets$on$tour";
+
+#endif

### 2012-05-07 JUIDLParser.java/src/dk/itu/spcl/dex/juidl/UIGenerator.java
Updates to JUIDLParser

@@ -1,5 +1,6 @@
 package dk.itu.spcl.dex.juidl;
 
+import java.lang.reflect.Array;
 import java.util.ArrayList;
 import java.util.Arrays;
 import java.util.Collections;
@@ -14,11 +15,11 @@ import org.json.JSONObject;
 public abstract class UIGenerator {
 	public static final double[] SUPPORTED_SCHEMA_VERSIONS = { 1.0 };
 	private static Comparator<JSONObject> priorityComparator = new JSONWidgetPriorityComparator();
-	private HashSet<String> idCol; 
+	private HashSet<String> idCol;
 
 	/**
-	 * Use this method to generate the UI based on the schema.
-	 * This method calls the validate method before generating.
+	 * Use this method to generate the UI based on the schema. This method calls
+	 * the validate method before generating.
 	 * 
 	 * @param schema
 	 * @throws JUIDLException
@@ -26,25 +27,22 @@ public abstract class UIGenerator {
 	public void generate(JSONObject schema) throws JUIDLException {
 		// validate schema
 		validate(schema);
-		
+
 		// generate the main canvas
-		generateCanvas(schema.optString("title"), 
-					   schema.optString("description"),
-					   schema.optDouble("version"));
-		
+		generateCanvas(schema.optString("title"),
+				schema.optString("description"), schema.optDouble("version"));
+
 		// generate the rest of the widgets
 		JSONArray widgets = schema.optJSONArray("widgets");
 		generateWidgets(widgets, null);
-	}	
+	}
 
 	/**
 	 * Validate the schema base, based on version and rules.
 	 * 
-	 * Rules (version 1.0): 
-	 * - title attribute required, is type string 
-	 * - description attribute is optional, is type string 
-	 * - version attribute is required, is type double 
-	 * - widgets array is required, is type array
+	 * Rules (version 1.0): - title attribute required, is type string -
+	 * description attribute is optional, is type string - version attribute is
+	 * required, is type double - widgets array is required, is type array
 	 * 
 	 * @param schema
 	 * @throws JUIDLException
@@ -68,7 +66,7 @@ public abstract class UIGenerator {
 			throw new JUIDLException(
 					"The widgets attribute is missing or not a valid array.");
 		}
-		
+
 		idCol = new HashSet<String>();
 		JSONArray widgets = schema.optJSONArray("widgets");
 		validateWidgets(widgets);
[…]

### 2012-05-07 JUIDLParser.java/tests/dk/itu/spcl/dex/juidl/tests/MockUIGenerator.java

@@ -8,12 +8,20 @@ import junit.framework.Assert;
 import org.json.JSONObject;
 
 import dk.itu.spcl.dex.juidl.UIGenerator;
+import dk.itu.spcl.dex.juidl.Widget;
 
 public class MockUIGenerator extends UIGenerator {
 	public String canvasTitle;
 	public String canvasDesription;
 	public double canvasVersion;
-	public ArrayList<JSONObject> canvasItems = new ArrayList<JSONObject>();
+	
+	public Widget widget;
+	public String stringContent;
+	public String[] stringContentArray;
+	public boolean boolContent;
+	public boolean[] boolContentArray;
+	public int intContent;
+	public int[] intContentArray;
 
 	@Override
 	protected void generateCanvas(String title, String description,
@@ -22,4 +30,41 @@ public class MockUIGenerator extends UIGenerator {
 		canvasDesription = description;
 		canvasVersion = version;
 	}
+
+	@Override
+	protected void generateWidget(Widget w, String content) {
+		widget = w;
+		stringContent = content;
+	}
+
+	@Override
+	protected void generateWidget(Widget w, String[] contentArray) {
+		widget = w;
+		this.stringContentArray = contentArray;
+	}
+
+	@Override
+	protected void generateWidget(Widget w, boolean content) {
+		widget = w;
+		this.boolContent = content;
+	}
+
+	@Override
+	protected void generateWidget(Widget w, boolean[] contentArray) {
+		widget = w;
+		this.boolContentArray = contentArray;
+	}
+
+	@Override
+	protected void generateWidget(Widget w, int content) {
+		widget = w;
+		this.intContent = content;		
+	}
+
+	@Override
+	protected void generateWidget(Widget w, int[] contentArray) {
+		widget = w;
+		this.intContentArray = contentArray;
+	}
+
 }

### 2012-05-07 JUIDLParser.java/tests/dk/itu/spcl/dex/juidl/tests/UIGeneratorTest.java

@@ -10,6 +10,7 @@ import org.junit.Test;
 
 import dk.itu.spcl.dex.juidl.JUIDLException;
 import dk.itu.spcl.dex.juidl.UIGenerator;
+import dk.itu.spcl.dex.juidl.WidgetType;
 
 public class UIGeneratorTest {
 
@@ -32,13 +33,28 @@ public class UIGeneratorTest {
 		assertEquals(1.0, p.canvasVersion, 0);
 	}
 	
-	// @Test
-	// public void sortingTest() {
-	// String test_schema = "{'title':'The Title', 'version':1.0, " +
-	// "'widgets':[{'id':'2'}," +
-	// "{'id':'3'}," +
-	// "]}";
-	// JSONObject schema_json = new JSONObject(test_schema);
-	// p.validate(schema_json);
-	// }
+	@Test
+	public void widgetGenTest() throws JSONException, JUIDLException {
+		String test_schema = "{'title':'The Title', " +
+							  "'version':1.0, 'widgets':[" +
+							  "{'id':'one', " +
+							  " 'title':'a title', " +
+							  " 'description':'a description', " +
+							  " 'priority':3, " +
+							  " 'type':'editable', " +
+							  " 'content-type':'integer', " +
+							  " 'content':42 }" +
+							  "]}";
+		JSONObject schema_json = new JSONObject(test_schema);
+		p.generate(schema_json);
+		
+		assertEquals("one", p.widget.getId());
+		assertEquals("a title", p.widget.getTitle());
+		assertEquals("a description", p.widget.getDescription());
+		assertEquals(WidgetType.EDITABLE, p.widget.getType());
+		assertEquals("integer", p.widget.getContentType());
+		assertEquals(42, p.intContent);
+	}
+	
+	
 }

### 2012-05-07 JUIDLParser.java/tests/dk/itu/spcl/dex/juidl/tests/WidgetTest.java

@@ -28,13 +28,12 @@ public class WidgetTest {
 		json.put("content", expectedContent);
 		String expParentId = "42";
 		
-		Widget<int[]> widget = Widget.genericFillFromJSONObject(json, expParentId);
+		Widget widget = Widget.fromJSONObject(json, expParentId);
 
 		assertEquals(expId, widget.getId());
 		assertEquals(expTitle, widget.getTitle());
 		assertEquals(expDesc, widget.getDescription());
 		assertEquals(expType, widget.getType());
-		assertEquals(expectedContent, widget.getContent());
 		assertEquals(expParentId, widget.getParentId());
 	}
 

### 2012-05-07 JUIDLParser.java/src/dk/itu/spcl/dex/juidl/UIGenerator.java
thingy code, starting UI generation

@@ -1,12 +1,8 @@
 package dk.itu.spcl.dex.juidl;
 
-import java.util.ArrayList;
 import java.util.Arrays;
-import java.util.Collections;
 import java.util.Comparator;
 import java.util.HashSet;
-import java.util.LinkedList;
-import java.util.List;
 
 import org.json.JSONArray;
 import org.json.JSONObject;
@@ -90,7 +86,7 @@ public abstract class UIGenerator {
 		} 
 		String id = widget.optString("id");
 		if (idCol.contains(id)) {
-			throw new JUIDLException(String.format("The widget ID '{0}' is doublicated.", id));	
+			throw new JUIDLException(String.format("The widget ID '{0}' is duplicated.", id));	
 		}
 		// add id to collection for duplication checking purposes
 		idCol.add(id);

### 2012-05-07 arduino/WindowThingy/Credentials.h

@@ -3,6 +3,6 @@
 
 // Wifi parameters
 char passphrase[] = "*snip*";
-char ssid[] = "lol$internets$on$tour";
+char ssid[] = "lol";
 
 #endif

### 2012-05-07 arduino/library/WiFly/WiFlyDevice.cpp

@@ -215,8 +215,6 @@ void WiFlyDevice::begin() {
 
 // TODO: Create a `begin()` that allows IP etc to be supplied.
 
-
-
 #define SOFTWARE_REBOOT_RETRY_ATTEMPTS 5
 
 boolean WiFlyDevice::softwareReboot(boolean isAfterBoot = true) {
@@ -367,6 +365,7 @@ void WiFlyDevice::setConfiguration() {
   // TODO: Handle configuration better
   // Turn off auto-connect
   sendCommand("set wlan join 0");
+  sendCommand("set ip dhcp 1");
 
   // TODO: Turn off server functionality until needed
   //       with "set ip protocol <something>"
@@ -379,7 +378,7 @@ void WiFlyDevice::setConfiguration() {
 
   // Turn off remote connect message
   sendCommand("set comm remote 0");
-
+  
   // Turn off status messages
   // sendCommand("set sys printlvl 0");
 
@@ -529,6 +528,45 @@ boolean WiFlyDevice::configure(byte option, unsigned long value) {
       break;
   }
   return true;
+}
+
+void WiFlyDevice::beginAdhoc() {
+  /*
+    Create and AdHoc network with the WiFly Shield.
+   */
+
+  DEBUG_LOG(1, "Entered WiFlyDevice::beginAdhoc()");
+
+  uart.begin();
+  reboot(); // Reboot to get device into known state
+  requireFlowControl();
+  enterCommandMode();
+
+  // Turn on Adhoc Mode
+  sendCommand("set wlan join 4");
+  // Set SSID of Adhoc Network
+  sendCommand("set wlan ssid WindowThingySSID");
+  // Set Channel for Adhoc Network
+  sendCommand("set wlan chan 1");
+  // Set IP for Adhoc Network
+  sendCommand("set ip address 169.254.1.1");
+  sendCommand("set ip netmask 255.255.0.0");
+  // Turn off DHCP
+  sendCommand("set ip dhcp 0");
+  // Set server port
+  sendCommand("set ip localport ", true);
+  uart.print(serverPort);
+  sendCommand("");
+
+  // Turn off remote connect message
+  sendCommand("set comm remote 0");
+
+  sendCommand("save", false, "Storing in config");
+  //Ensures sucessful reboot. See requireFlowControl for more info.
+  sendCommand("get uart", false, "Flow=0x1");
+  reboot();
+
+  //After rebooting, your AdHoc network will be available.
 }
 
 

### 2012-05-07 arduino/library/WiFly/WiFlyDevice.h

@@ -9,6 +9,7 @@ class WiFlyDevice {
   public:
     WiFlyDevice(SpiUartDevice& theUart);
     void begin();
+    void beginAdhoc();
 
     boolean join(const char *ssid);
     boolean join(const char *ssid, const char *passphrase, 

### 2012-05-07 prototype/src/dk/itu/spcl/dex/AndroidUIGenerator.java

@@ -1,0 +1,13 @@
+package dk.itu.spcl.dex;
+
+import dk.itu.spcl.dex.juidl.UIGenerator;
+
+public class AndroidUIGenerator extends UIGenerator {
+
+  @Override
+  protected void generateCanvas(String title, String description, double version) {
+    // TODO Auto-generated method stub
+
+  }
+
+}

### 2012-05-07 prototype/src/dk/itu/spcl/dex/PresetActivity.java

@@ -92,8 +92,8 @@ public class PresetActivity extends Activity implements Repository.Listener {
 
   public void onActivatePreset(View view) {
     for (PresetEntry entry : _preset.getEntries()) {
-      _thingyWriter.setStatus(entry.getThingy(), entry.getStatus());
-      _thingyWriter.flushWizard();
+//      _thingyWriter.setStatus(entry.getThingy(), entry.getStatus());
+//      _thingyWriter.flushWizard();
     }
   }
 

### 2012-05-07 prototype/src/dk/itu/spcl/dex/ScanActivity.java

@@ -34,14 +34,9 @@ public class ScanActivity extends Activity {
     performDummyScan();
   }
 
-  private void addMockThingy(String name) {
-    Thingy thingy = new Thingy().setName(name).setUrl(
-        "status_" + _thingiesReturned);
-    if (_thingiesReturned > 0)
-      thingy.setReadOnly(true);
-
+  private void addThingy(String name) {
+    Thingy thingy = new Thingy().setName(name).setUrl(Settings.THINGY_URL);
     _repository.addThingy(thingy);
-    _thingiesReturned++;
     returnScannedThingy(thingy);
   }
 
@@ -78,7 +73,7 @@ public class ScanActivity extends Activity {
 
     @Override
     protected String doInBackground(Integer... params) {
-      waitForMockScan();
+      waitForScan();
       return null;
     }
 
@@ -89,31 +84,15 @@ public class ScanActivity extends Activity {
             @Override
             public void closed(boolean accepted, String value) {
               if (accepted && value.length() > 0) {
-                addMockThingy(value);
+                addThingy(value);
               }
             }
           });
     }
 
-    private void waitForMockScan() {
+    private void waitForScan() {
       while (!isCancelled()) {
-        String scanned = null;
-        try {
-          scanned = HttpTools.readStringFromUrl(Settings.WIZARD_URL + "scan_"
-              + _thingiesReturned);
-        } catch (ClientProtocolException e1) {
-          e1.printStackTrace();
-        } catch (IOException e1) {
-          e1.printStackTrace();
-        }
-        if (scanned.equals("1"))
-          return;
-        else
-          try {
-            Thread.sleep(500);
-          } catch (InterruptedException e) {
-            e.printStackTrace();
-          }
+        return; // todo QR/whatever
       }
     }
   }

### 2012-05-07 prototype/src/dk/itu/spcl/dex/Settings.java

@@ -2,6 +2,6 @@ package dk.itu.spcl.dex;
 
 public class Settings {
 
-  public static final String WIZARD_URL = "http://anti.zno.dk/wizard/";
+  public static final String THINGY_URL = "http://192.168.43.193/";
   
 }

### 2012-05-07 prototype/src/dk/itu/spcl/dex/ThingyActivity.java

@@ -28,17 +28,7 @@ public class ThingyActivity extends Activity implements Repository.Listener {
 
     setTitle("Thingy: " + _thingy.getName());
 
-    setContentView(R.layout.simple_thingy);
-    _toggleButton = (ToggleButton) findViewById(R.id.thingyToggleButton);
     _repository.addListener(this);
-    _toggleButton.setChecked(_thingy.getStatus());
-  }
-
-  public void thingyToggleButtonClicked(View v) {
-    ToggleButton button = (ToggleButton) v;
-    boolean on = button.isChecked();
-    _thingyWriter.setStatus(_thingy, on);
-    _thingyWriter.flushWizard();
   }
   
   @Override 

### 2012-05-07 prototype/src/dk/itu/spcl/dex/ThingyStatusWriter.java

@@ -9,30 +9,7 @@ import dk.itu.spcl.dex.tools.HttpTools;
 
 public class ThingyStatusWriter {
 
-  public void setStatus(Thingy thingy, boolean status) {
-    if (thingy.isReadOnly())
-      return;
-    
-    String url = Settings.WIZARD_URL + "write.php?thingy=" + thingy.getUrl()
-        + "&status=" + (status ? 1 : 0);
-    try {
-      HttpTools.readStringFromUrl(url);
-    } catch (ClientProtocolException e) {
-      e.printStackTrace();
-    } catch (IOException e) {
-      e.printStackTrace();
-    }
-  }
-
-  public void flushWizard() {
-    String url = Settings.WIZARD_URL + "write.php?setLast=1";
-    try {
-      HttpTools.readStringFromUrl(url);
-    } catch (ClientProtocolException e) {
-      e.printStackTrace();
-    } catch (IOException e) {
-      e.printStackTrace();
-    }
-  }
+//  public void setStatus(Thingy thingy, ...) {
+//  }
 
 }

### 2012-05-07 prototype/src/dk/itu/spcl/dex/ThingyUpdater.java

@@ -78,14 +78,14 @@ public class ThingyUpdater implements Runnable {
   }
 
   private void updateThingy(Thingy thingy) {
-    try {
-      boolean thingyStatus = getStatusFromUrl(Settings.WIZARD_URL + thingy.getUrl());
-      thingy.setStatus(thingyStatus);
-    } catch (ClientProtocolException e) {
-      Log.e("dex", e.toString());
-    } catch (IOException e) {
-      Log.e("dex", e.toString());
-    }
+//    try {
+//      boolean thingyStatus = getStatusFromUrl(Settings.WIZARD_URL + thingy.getUrl());
+//      thingy.setStatus(thingyStatus);
+//    } catch (ClientProtocolException e) {
+//      Log.e("dex", e.toString());
+//    } catch (IOException e) {
+//      Log.e("dex", e.toString());
+//    }
   }
 
   private boolean getStatusFromUrl(String url) throws ClientProtocolException,

### 2012-05-07 report/paper.tex
report, etc

--- 2012-02-29 proposal/proposal.tex
@@
-\documentclass{ubicomp2011}
-\usepackage{times}
-\usepackage{url}
-\usepackage{graphics}
-\usepackage{color}
-\usepackage[pdftex]{hyperref}
-\hypersetup{%
-pdftitle={Your Title}, pdfauthor={Your Authors}, pdfkeywords={your
-keywords}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
-citecolor=black, filecolor=black, linkcolor=black, urlcolor=black,
-breaklinks=true, }
-\newcommand{\comment}[1]{}
-\definecolor{Orange}{rgb}{1,0.5,0}
-\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[[#1]]}}}}
-
-\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy
+\documentclass{article}
 
 \begin{document}
-% to make various LaTeX processors do the right thing with page size
-\special{papersize=8.5in,11in}
-\setlength{\paperheight}{11in}
-\setlength{\paperwidth}{8.5in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
 
-% use this command to override the default ACM copyright statement
-% (e.g. for preprints). Remove for camera ready copy.
+\begin{abstract}
+  TODOlish
+\end{abstract}
 
-%\toappear{Paper submitted for evaluation in the Pervasive Computing Course, Spring 2012. The IT University of Copenhagen. Copyright remains with the authors.}
+\section{Introduction}
 
-\toappear{Project proposal for the Pervasive Computing Course, Spring 2012. The IT University of Copenhagen. Copyright remains with the authors.}
+More than 20 years after Weiser first defined ubiquitous computing \cite{Weiser1991} we have yet to see smart homes become commonplace.
+We believe this is largely due to smart home technology being inaccessible and too complicated for everyday users, and both price, perceived lack of advantages, and challenges in learning new technology scare users away.
 
-\title{UbiComp 2011 Conference Proceedings Format}
-\numberofauthors{2}
-\author{
-  \alignauthor Egil Hansen\\
-    \affaddr{IT University of Copenhagen}\\
-%    \affaddr{Address  (Blank for Blind Review)}\\
-    \email{ekri@itu.dk}
- \alignauthor David Thomas\\
-    \affaddr{IT University of Copenhagen}\\
-%    \affaddr{Address  (Blank for Blind Review)}\\
-    \email{dtho@itu.dk}  }
-\maketitle
+We propose a smart home infrastructure which bases itself on hardware that exist in most homes today -- Wifi and smart phones -- and use simple, open, interoperable technologies such as HTTP and HTML5's web sockets to provide the communication backbone of the architecture.
+Each individual device, or ``thingy'', as we have dubbed them, is supposed to be simple to comprehend, install, and use, but provide value nonetheless.
+We call this concept \textit{Thingies for Dummies}\footnote{This is a reference to the \textit{For Dummies} book series that tries to present non-intimidating guides to various topics and that always contains the subtitle ``A Reference for the Rest of Us!''.}.
 
-%\begin{abstract}
-%  In this paper we describe the formatting requirements for the UbiComp 2011
-%  Conference Proceedings, and offer recommendations on writing for the
-%  worldwide Ubiquitous Computing readership.  Please review this document even if
-%  you have submitted to Ubiquitous Computing conferences before, for some format
-%  details have changed relative to previous years. These include the
-%  formatting of table captions, the formatting of references, a
-%  requirement to include ACM DL indexing information, and guidelines for how to handle relevant references to your own work while preparing your submission for blind review.
-%\end{abstract}
+Edwards and Grinter describe in their 2001 paper \cite{Edwards01athome} seven challenges facing the adoption of smart home technology\footnote{Challenge One: \textit{The `Accidentally' Smart Home}.
+Challenge Two: \textit{Impromptu Interoperability (islands of functionality)}.
+Challenge Three: \textit{No Systems Administrator}.
+Challenge Four: \textit{Designing for Domestic Use}.
+Challenge Five: \textit{Social Implications of Aware Home Technologies}.
+Challenge Six: \textit{Reliability}.
+Challenge Seven: \textit{Inference in the Presence of Ambiguity}.}, and we believe that through the overarching theme of `simple’ in our proposal -- simple architechure and simple thingies -- we are able to answer the first six challenges, at least partly.
+Simplifying things does imply giving up on the dream of a fully automated intelligence home for the time being, but our proposed infrastructure does not prevent a home from becoming gradually more automated or intelligent.
 
-%\keywords{Guides, instructions, authors' kit, conference publications.}
+\paragraph{TODO in this section:}
+\begin{itemize}
+\item Overview of the coming sections
+\item Discussion of smart homes vs smart office (or discussion)
+\item Scenario (lock down)
+\item Should we include a more detailed description of why we solve six challenges, or is that for the discussion section?
+\end{itemize}
 
-%\category{H.5.2}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}.
+\section{Thinges for Dummies Infrastructure}
 
-%\generalterms{This section is limited to the following 16 terms and
-%MUST be included on the first page of all submissions after the ACM
-%Categories section, then as well chosen properly on the Proceedings
-%or Publication's submission page: Algorithms, Design,
-%Documentation, Economics, Experimentation, Human Factors, Languages,
-%Legal Aspects, Management, Measurement, Performance, Reliability,
-%Security, Standardization, Theory, Verification.}
+The key design decision for \textit{Thingies for Dummies} was the it should be simple and  inexpensive to get started retrofitting an existing house with thingies and that it should be independent of specific hardware and software platforms.
+This ment not requiring a dedicated controller, and relying on the existing infrastructure in the home for handling communication and control, i.e.
+a Wifi network.
+Using the home’s Wifi, assuming it is protected with a passphrase, adds a virtual boundary to the smart home, a boundary that users understand because they understand that you cannot access the Wifi without the passphrase.
+[NOTE: Does this require a ref?]
 
-\section{Background}
-hep
+For communication protocol, we decided to use HTTP and web sockets .
+This opens up for a huge list of possible controllers, basically any type of computer that understands HTTP.
+Using HTTP also enables remote management scenarios much easier, since HTTP traffic very unlikely to be blocked in firewalls.
+TODO MORE HERE ABOUT CLOUD
 
-\section{Idea}
-hep
+You cannot have a smart home without controllers, and to us the obvious choice for controllers are smart phones.
+It is a device which users carries around with them all the time and are comfortable using.
+It does limit the
 
-\section{Scenario}
-hep
+TODO in this section:
+- diagram of the architecture
+- mention cloud computing
+- intro to section
+- key design goals
+- overall infrastructure -- reasoning
+- something
 
-\section{Plan}
-hep
+\subsection{Thingies}
 
-\subsection{Equipment}
-hep
+A Thingy can be either a sensor, a actuator, or a proxy for other Thingies.
+How simple can a thingy be and still be useful?
+That is a question raised in \cite{Edwards01athome} and it turns out, at least from our informal questioning of friends, family, and colleagues that even a simple Thingy that enables remote toggle of a light switch is useful.
 
-% Referencer:
-% ~\cite{ref}
+Keeping thingies simple.
+- no UI
+- only operational configuration on the device
+- no transactions
 
-% til sidst
-%\nocite{example-journal,example-abstracts,example-conference2}
+Bootstrapping devices
+
+Security - wifi in the home determines that
+\subsection{Bootstrapping}
+
+mDNS, Apple Bonjour
+\subsection{Configuration}
+
+\subsection{Configuration synchronization}
+
+\subsection{Networking}
+
+\subsection{Security}
 
 \bibliographystyle{abbrv}
-\bibliography{proposal}
+\bibliography{bibliography}
 

### 2012-05-09 JUIDLParser.java/src/dk/itu/spcl/dex/juidl/UIGenerator.java
work on final prototype so far

@@ -1,7 +1,5 @@
 package dk.itu.spcl.dex.juidl;
 
-import java.lang.reflect.Array;
-import java.util.ArrayList;
 import java.util.Arrays;
 import java.util.Comparator;
 import java.util.HashSet;

### 2012-05-09 JUIDLParser.java/tests/dk/itu/spcl/dex/juidl/tests/UIGeneratorTest.java

@@ -1,7 +1,6 @@
 package dk.itu.spcl.dex.juidl.tests;
 
-import static org.junit.Assert.*;
-import junit.framework.Assert;
+import static org.junit.Assert.assertEquals;
 
 import org.json.JSONException;
 import org.json.JSONObject;
@@ -9,7 +8,6 @@ import org.junit.Before;
 import org.junit.Test;
 
 import dk.itu.spcl.dex.juidl.JUIDLException;
-import dk.itu.spcl.dex.juidl.UIGenerator;
 import dk.itu.spcl.dex.juidl.WidgetType;
 
 public class UIGeneratorTest {

### 2012-05-09 JUIDLParser.java/tests/dk/itu/spcl/dex/juidl/tests/UIGeneratorValidateTest.java

@@ -1,12 +1,8 @@
 package dk.itu.spcl.dex.juidl.tests;
 
-import static org.junit.Assert.*;
-import junit.framework.Assert;
-
 import org.json.JSONException;
 import org.json.JSONObject;
 import org.junit.Before;
-import org.junit.BeforeClass;
 import org.junit.Test;
 
 import dk.itu.spcl.dex.juidl.JUIDLException;

### 2012-05-09 prototype/src/dk/itu/spcl/dex/AndroidUIGenerator.java

@@ -1,13 +1,60 @@
 package dk.itu.spcl.dex;
 
+import android.app.Activity;
+import android.widget.LinearLayout;
+import android.widget.ToggleButton;
 import dk.itu.spcl.dex.juidl.UIGenerator;
+import dk.itu.spcl.dex.juidl.Widget;
+import dk.itu.spcl.dex.juidl.WidgetType;
+import dk.itu.spcl.dex.model.Thingy;
 
 public class AndroidUIGenerator extends UIGenerator {
+  
+  private Thingy _thingy;
+  private Activity _activty;
+  private LinearLayout _layout;
+  
+  public AndroidUIGenerator(Thingy thingy, Activity activity) {
+    _thingy = thingy;
+    _activty = activity;
+  }
 
   @Override
   protected void generateCanvas(String title, String description, double version) {
-    // TODO Auto-generated method stub
+    _layout = new LinearLayout(_activty);
+    _activty.setContentView(_layout);
+  }
 
+  @Override
+  protected void generateWidget(Widget w, String content) {
+    // not implemented    
+  }
+
+  @Override
+  protected void generateWidget(Widget w, String[] contentArray) {
+    // not implemented    
+  }
+
+  @Override
+  protected void generateWidget(Widget w, boolean content) {
+    ToggleButton button = new ToggleButton(_activty);
+    button.setEnabled(w.getType() != WidgetType.READ_ONLY);
+    _layout.addView(button);
+  }
+
+  @Override
+  protected void generateWidget(Widget w, boolean[] contentArray) {
+    // not implemented    
+  }
+
+  @Override
+  protected void generateWidget(Widget w, int content) {
+    // not implemented
+  }
+
+  @Override
+  protected void generateWidget(Widget w, int[] contentArray) {
+    // not implemented
   }
 
 }

### 2012-05-09 prototype/src/dk/itu/spcl/dex/ThingyActivity.java

@@ -2,8 +2,6 @@ package dk.itu.spcl.dex;
 
 import android.app.Activity;
 import android.os.Bundle;
-import android.view.View;
-import android.widget.ToggleButton;
 import dk.itu.spcl.dex.model.Repository;
 import dk.itu.spcl.dex.model.Thingy;
 
@@ -13,7 +11,6 @@ public class ThingyActivity extends Activity implements Repository.Listener {
   private ThingyUpdater _thingyUpdater;
   private Repository _repository;
   private ThingyStatusWriter _thingyWriter;
-  private ToggleButton _toggleButton;
 
   @Override
   protected void onCreate(Bundle savedInstanceState) {
@@ -59,7 +56,7 @@ public class ThingyActivity extends Activity implements Repository.Listener {
     runOnUiThread(new Runnable() {
       @Override
       public void run() {
-        _toggleButton.setChecked(_thingy.getStatus());  
+  
       }
     });
   }

### 2012-05-09 prototype/src/dk/itu/spcl/dex/ThingyListActivity.java

@@ -103,9 +103,6 @@ public class ThingyListActivity extends ListActivity implements
   }
 
   private void startThingyActivity(Thingy thingy) {
-    if (thingy.isReadOnly())
-      return;
-    
     Intent intent = new Intent(this, ThingyActivity.class).putExtra("thingy",
         thingy.getName());
     startActivity(intent);

### 2012-05-09 prototype/src/dk/itu/spcl/dex/ThingyStatusWriter.java

@@ -1,11 +1,5 @@
 package dk.itu.spcl.dex;
 
-import java.io.IOException;
-
-import org.apache.http.client.ClientProtocolException;
-
-import dk.itu.spcl.dex.model.Thingy;
-import dk.itu.spcl.dex.tools.HttpTools;
 
 public class ThingyStatusWriter {
 

### 2012-05-09 prototype/src/dk/itu/spcl/dex/model/Thingy.java

@@ -1,11 +1,14 @@
 package dk.itu.spcl.dex.model;
 
+import java.util.HashMap;
+
+import dk.itu.spcl.dex.juidl.Widget;
+
 public class Thingy implements Comparable<Thingy> {
 
   private String _name;
   private String _url;
-  private boolean _status;
-  private boolean _isReadOnly;
+  private HashMap<String, Widget> _widgets = new HashMap<String, Widget>();
 
   public Thingy() {
   }
@@ -29,25 +32,13 @@ public class Thingy implements Comparable<Thingy> {
     _url = url;
     return this;
   }
-  
-  // status (to be expanded)
+    
+  public void addWidget(Widget widget) {
+    _widgets.put(widget.getId(), widget);
+  }
   
   public boolean getStatus() {
-    return _status;
-  }
-  
-  public Thingy setStatus(boolean status) {
-    _status = status;
-    return this;
-  }
-  
-  public boolean isReadOnly() {
-    return _isReadOnly;
-  }
-  
-  public Thingy setReadOnly(boolean readOnly) {
-    _isReadOnly = readOnly;
-    return this;
+    return false;
   }
   
   // standard overrides

### 2012-05-12 JUIDLParser.java/tests/dk/itu/spcl/dex/juidl/tests/MockUIGenerator.java
bootstrap proof of concept. just add polish!

@@ -1,12 +1,5 @@
 package dk.itu.spcl.dex.juidl.tests;
 
-import java.util.ArrayList;
-import java.util.List;
-
-import junit.framework.Assert;
-
-import org.json.JSONObject;
-
 import dk.itu.spcl.dex.juidl.UIGenerator;
 import dk.itu.spcl.dex.juidl.Widget;
 

### 2012-05-12 arduino/WindowThingy/Credentials.h

@@ -1,8 +1,0 @@
-#ifndef __CREDENTIALS_H__
-#define __CREDENTIALS_H__
-
-// Wifi parameters
-char passphrase[] = "*snip*";
-char ssid[] = "lol";
-
-#endif

### 2012-05-12 arduino/library/WiFly/WiFlyDevice.cpp

@@ -393,7 +393,8 @@ void WiFlyDevice::setConfiguration() {
 boolean WiFlyDevice::join(const char *ssid) {
     // Ron Guest -- begin change to support space in SSID
       // First we set the SSID (putting the SSID on the join command doesn't work
-      Serial.println("Setting SSID using Ron method");
+      Serial.print("Connecting to ");
+      Serial.println(ssid);
       sendCommand("set wlan ssid ",true);
       sendCommand(ssid);
       if (sendCommand("join", false, "Associated!")) {
@@ -529,46 +530,6 @@ boolean WiFlyDevice::configure(byte option, unsigned long value) {
   }
   return true;
 }
-
-void WiFlyDevice::beginAdhoc() {
-  /*
-    Create and AdHoc network with the WiFly Shield.
-   */
-
-  DEBUG_LOG(1, "Entered WiFlyDevice::beginAdhoc()");
-
-  uart.begin();
-  reboot(); // Reboot to get device into known state
-  requireFlowControl();
-  enterCommandMode();
-
-  // Turn on Adhoc Mode
-  sendCommand("set wlan join 4");
-  // Set SSID of Adhoc Network
-  sendCommand("set wlan ssid WindowThingySSID");
-  // Set Channel for Adhoc Network
-  sendCommand("set wlan chan 1");
-  // Set IP for Adhoc Network
-  sendCommand("set ip address 169.254.1.1");
-  sendCommand("set ip netmask 255.255.0.0");
-  // Turn off DHCP
-  sendCommand("set ip dhcp 0");
-  // Set server port
-  sendCommand("set ip localport ", true);
-  uart.print(serverPort);
-  sendCommand("");
-
-  // Turn off remote connect message
-  sendCommand("set comm remote 0");
-
-  sendCommand("save", false, "Storing in config");
-  //Ensures sucessful reboot. See requireFlowControl for more info.
-  sendCommand("get uart", false, "Flow=0x1");
-  reboot();
-
-  //After rebooting, your AdHoc network will be available.
-}
-
 
 // Preinstantiate required objects
 SpiUartDevice SpiSerial;

### 2012-05-12 prototype/src/dk/itu/spcl/dex/Bootstrapper.java

@@ -1,0 +1,81 @@
+package dk.itu.spcl.dex;
+
+import java.io.BufferedWriter;
+import java.io.IOException;
+import java.io.OutputStreamWriter;
+import java.lang.reflect.InvocationTargetException;
+import java.lang.reflect.Method;
+import java.net.ServerSocket;
+import java.net.Socket;
+import java.nio.charset.Charset;
+
+import android.content.Context;
+import android.net.wifi.WifiConfiguration;
+import android.net.wifi.WifiManager;
+import android.util.Log;
+
+public class Bootstrapper {
+
+  private WifiManager _wifiManager;
+  private String _ssid;
+  private String _key;
+
+  public Bootstrapper(Context context, String ssid, String key) {
+    _wifiManager = (WifiManager) context.getSystemService(Context.WIFI_SERVICE);
+    _ssid = ssid;
+    _key = key;
+  }
+
+  public void runBootstrapping() {
+    try {
+      toggleWifi(false);
+      toggleHotspot(true);
+      waitForConnection();
+      pause(); // give the thingy a chance to disconnect
+      toggleHotspot(false);
+      toggleWifi(true);
+    } catch (Exception e) {
+      Log.e("dex", e.toString());
+    }
+  }
+
+  private void pause() {
+    try {
+      Thread.sleep(1000);
+    } catch (InterruptedException e) {
+    }
+  }
+
+  private void waitForConnection() throws IOException {
+    Log.i("dex", "Listening");
+    ServerSocket server = new ServerSocket(44444);
+    Socket connection = server.accept();
+    BufferedWriter writer = new BufferedWriter(new OutputStreamWriter(
+        connection.getOutputStream(), Charset.forName("US-ASCII")));
+    String response = "HTTP/1.1 200 OK\n" + "Content-Type: text/html\n" + "\n"
+        + Settings.HOME_SSID + "/" + Settings.HOME_PSK + "\n";
+    writer.write(response);
+    writer.flush();
+    writer.close();
+    server.close();
+    Log.i("dex", "Sent response");
+  }
+
+  private void toggleHotspot(boolean enable) throws IllegalArgumentException,
+      IllegalAccessException, InvocationTargetException, SecurityException,
+      NoSuchMethodException {
+    Log.i("dex", "Setting up AP");
+    WifiConfiguration wifiConfig = new WifiConfiguration();
[…]

### 2012-05-12 prototype/src/dk/itu/spcl/dex/HomeActivity.java

@@ -48,9 +48,15 @@ public class HomeActivity extends TabActivity {
     case R.id.resetMenu:
       _repository.reset();
       return true;
+    case R.id.bootstrapMenu:
+      testBootstrap();
     default:
       return super.onOptionsItemSelected(item);
     }
+  }
+
+  private void testBootstrap() {
+    new Bootstrapper(this, "ThingyBootstrapAP", "1234567890").runBootstrapping();
   }
 
   private void addTabs() {

### 2012-05-12 prototype/src/dk/itu/spcl/dex/ScanActivity.java

@@ -1,17 +1,15 @@
 package dk.itu.spcl.dex;
 
-import java.io.IOException;
-
-import org.apache.http.client.ClientProtocolException;
-
 import android.app.Activity;
 import android.content.Intent;
 import android.os.AsyncTask;
 import android.os.Bundle;
-import android.widget.TextView;
+
+import com.google.zxing.integration.android.IntentIntegrator;
+import com.google.zxing.integration.android.IntentResult;
+
 import dk.itu.spcl.dex.model.Repository;
 import dk.itu.spcl.dex.model.Thingy;
-import dk.itu.spcl.dex.tools.HttpTools;
 import dk.itu.spcl.dex.tools.UITools;
 
 public class ScanActivity extends Activity {
@@ -26,16 +24,31 @@ public class ScanActivity extends Activity {
     _repository = Repository.getInstance();
 
     setTitle("Install new thingy");
-    TextView textview = new TextView(this);
-    textview.setText("Hold your phone close to the device you want to add.");
-    textview.setTextSize(18);
-    setContentView(textview);
 
-    performDummyScan();
+    IntentIntegrator integrator = new IntentIntegrator(this);
+    integrator.initiateScan();
   }
 
-  private void addThingy(String name) {
-    Thingy thingy = new Thingy().setName(name).setUrl(Settings.THINGY_URL);
+  public void onActivityResult(int requestCode, int resultCode, Intent intent) {
+    IntentResult scanResult = IntentIntegrator.parseActivityResult(requestCode,
+        resultCode, intent);
+    if (scanResult != null) {
+      String scannedText = scanResult.getContents();
+      if (scannedText.startsWith("thingy://")) {
+        String[] wifiInfo = scannedText.substring("thingy://".length()).split(
+            "\\/");
+        startBootstrap(wifiInfo[0], wifiInfo[1]);
+      }
+    }
+  }
+
+  private void startBootstrap(String ssid, String key) {
+    _scanTask = new ScanTask();
+    _scanTask.execute(ssid, key);
+  }
+
+  private void addThingy(String name, String url) {
+    Thingy thingy = new Thingy().setName(name).setUrl(url);
     _repository.addThingy(thingy);
     returnScannedThingy(thingy);
   }
@@ -59,42 +72,27 @@ public class ScanActivity extends Activity {
     super.onDestroy();
   }
 
-  public static int _thingiesReturned = 0;
-
[…]

### 2012-05-12 prototype/src/dk/itu/spcl/dex/Settings.java

@@ -3,5 +3,7 @@ package dk.itu.spcl.dex;
 public class Settings {
 
   public static final String THINGY_URL = "http://192.168.43.193/";
+  public static final String HOME_SSID = "HomeAP";
+  public static final String HOME_PSK = "abcdefgh";
   
-}
+} 

### 2012-05-12 prototype/src/dk/itu/spcl/dex/ThingyUpdater.java

@@ -5,7 +5,6 @@ import java.util.ArrayList;
 
 import org.apache.http.client.ClientProtocolException;
 
-
 import android.util.Log;
 import dk.itu.spcl.dex.model.Repository;
 import dk.itu.spcl.dex.model.Thingy;
@@ -70,7 +69,6 @@ public class ThingyUpdater implements Runnable {
   }
 
   private void update() {
-    Log.i("dex", "Updating");
     for (Thingy thingy : _repository.getThingies())
       updateThingy(thingy);
 

### 2012-05-13 prototype/src/dk/itu/spcl/dex/Bootstrapper.java
bootstrapping - now with one less hardcoded ip!

@@ -1,7 +1,9 @@
 package dk.itu.spcl.dex;
 
+import java.io.BufferedReader;
 import java.io.BufferedWriter;
 import java.io.IOException;
+import java.io.InputStreamReader;
 import java.io.OutputStreamWriter;
 import java.lang.reflect.InvocationTargetException;
 import java.lang.reflect.Method;
@@ -26,17 +28,19 @@ public class Bootstrapper {
     _key = key;
   }
 
-  public void runBootstrapping() {
+  public String runBootstrapping() {
     try {
       toggleWifi(false);
       toggleHotspot(true);
-      waitForConnection();
+      String thingyUrl = listenForBootstrapRequests();
       pause(); // give the thingy a chance to disconnect
       toggleHotspot(false);
       toggleWifi(true);
+      return thingyUrl;
     } catch (Exception e) {
       Log.e("dex", e.toString());
     }
+    return null;
   }
 
   private void pause() {
@@ -46,19 +50,32 @@ public class Bootstrapper {
     }
   }
 
-  private void waitForConnection() throws IOException {
+  private String listenForBootstrapRequests() throws IOException {
     Log.i("dex", "Listening");
     ServerSocket server = new ServerSocket(44444);
-    Socket connection = server.accept();
-    BufferedWriter writer = new BufferedWriter(new OutputStreamWriter(
-        connection.getOutputStream(), Charset.forName("US-ASCII")));
-    String response = "HTTP/1.1 200 OK\n" + "Content-Type: text/html\n" + "\n"
-        + Settings.HOME_SSID + "/" + Settings.HOME_PSK + "\n";
-    writer.write(response);
-    writer.flush();
-    writer.close();
+    String thingyUrl = null;
+    while (thingyUrl == null) {
+      Socket connection = server.accept();
+      // request format:
+      // /getssid
+      // /saveip/x.x.x.x
+      BufferedReader reader = new BufferedReader(new InputStreamReader(
+          connection.getInputStream()));
+      String request = reader.readLine();
+      if (request.contains("/saveip/")) {
+        thingyUrl = "http://"
+            + request.split("\\ ")[1].substring("/saveip/".length()) + "/";
+      }
+      BufferedWriter writer = new BufferedWriter(new OutputStreamWriter(
+          connection.getOutputStream(), Charset.forName("US-ASCII")));
+      String response = "HTTP/1.1 200 OK\n" + "Content-Type: text/html\n"
[…]

### 2012-05-13 prototype/src/dk/itu/spcl/dex/ScanActivity.java

@@ -4,6 +4,7 @@ import android.app.Activity;
 import android.content.Intent;
 import android.os.AsyncTask;
 import android.os.Bundle;
+import android.util.Log;
 
 import com.google.zxing.integration.android.IntentIntegrator;
 import com.google.zxing.integration.android.IntentResult;
@@ -49,6 +50,7 @@ public class ScanActivity extends Activity {
 
   private void addThingy(String name, String url) {
     Thingy thingy = new Thingy().setName(name).setUrl(url);
+    Log.i("dex", "Adding thingy with url " + url);
     _repository.addThingy(thingy);
     returnScannedThingy(thingy);
   }
@@ -78,8 +80,7 @@ public class ScanActivity extends Activity {
     protected String doInBackground(String... params) {
       Bootstrapper bootstrapper = new Bootstrapper(ScanActivity.this,
           params[0], params[1]);
-      bootstrapper.runBootstrapping();
-      return "http://10.0.0.101/"; // todo
+      return bootstrapper.runBootstrapping();
     }
 
     @Override

### 2012-05-13 prototype/src/dk/itu/spcl/dex/HomeActivity.java
tweaked bootstrap a bit

@@ -48,15 +48,9 @@ public class HomeActivity extends TabActivity {
     case R.id.resetMenu:
       _repository.reset();
       return true;
-    case R.id.bootstrapMenu:
-      testBootstrap();
     default:
       return super.onOptionsItemSelected(item);
     }
-  }
-
-  private void testBootstrap() {
-    new Bootstrapper(this, "ThingyBootstrapAP", "1234567890").runBootstrapping();
   }
 
   private void addTabs() {

### 2012-05-13 prototype/src/dk/itu/spcl/dex/ScanActivity.java

@@ -5,6 +5,7 @@ import android.content.Intent;
 import android.os.AsyncTask;
 import android.os.Bundle;
 import android.util.Log;
+import android.widget.TextView;
 
 import com.google.zxing.integration.android.IntentIntegrator;
 import com.google.zxing.integration.android.IntentResult;
@@ -16,7 +17,8 @@ import dk.itu.spcl.dex.tools.UITools;
 public class ScanActivity extends Activity {
 
   private Repository _repository;
-  private ScanTask _scanTask;
+  private BootstrapTask _bootstrapTask;
+  private TextView _textView;
 
   @Override
   protected void onCreate(Bundle savedInstanceState) {
@@ -25,6 +27,10 @@ public class ScanActivity extends Activity {
     _repository = Repository.getInstance();
 
     setTitle("Install new thingy");
+
+    _textView = new TextView(this);
+    _textView.setTextSize(18);
+    setContentView(_textView);
 
     IntentIntegrator integrator = new IntentIntegrator(this);
     integrator.initiateScan();
@@ -36,6 +42,7 @@ public class ScanActivity extends Activity {
     if (scanResult != null) {
       String scannedText = scanResult.getContents();
       if (scannedText.startsWith("thingy://")) {
+        showText("Great! Now press the button on the thingy. Connecting will take a little while.");
         String[] wifiInfo = scannedText.substring("thingy://".length()).split(
             "\\/");
         startBootstrap(wifiInfo[0], wifiInfo[1]);
@@ -44,8 +51,8 @@ public class ScanActivity extends Activity {
   }
 
   private void startBootstrap(String ssid, String key) {
-    _scanTask = new ScanTask();
-    _scanTask.execute(ssid, key);
+    _bootstrapTask = new BootstrapTask();
+    _bootstrapTask.execute(ssid, key);
   }
 
   private void addThingy(String name, String url) {
@@ -68,13 +75,21 @@ public class ScanActivity extends Activity {
 
   @Override
   protected void onDestroy() {
-    if (_scanTask != null)
-      _scanTask.cancel(true);
+    if (_bootstrapTask != null)
+      _bootstrapTask.cancel(true);
 
     super.onDestroy();
   }
 
-  private class ScanTask extends AsyncTask<String, Integer, String> {
+  private void showText(final String text) {
+    runOnUiThread(new Runnable() {
+      public void run() {
+        _textView.setText(text);
+      }
+    });
+  }
+
+  private class BootstrapTask extends AsyncTask<String, Integer, String> {
 
     @Override
[…]

### 2012-05-13 prototype/gen/dk/itu/spcl/dex/R.java
added settings for home wifi

@@ -22,14 +22,14 @@ public final class R {
         public static final int on_nocheck=0x7f020008;
     }
     public static final class id {
-        public static final int addThingyMenu=0x7f060006;
-        public static final int bootstrapMenu=0x7f060004;
-        public static final int listTextView=0x7f060000;
-        public static final int newPresetMenu=0x7f060005;
-        public static final int newThingyMenu=0x7f060007;
-        public static final int presetThingyList=0x7f060001;
-        public static final int resetMenu=0x7f060003;
-        public static final int thingyToggleButton=0x7f060002;
+        public static final int addThingyMenu=0x7f070006;
+        public static final int listTextView=0x7f070000;
+        public static final int newPresetMenu=0x7f070005;
+        public static final int newThingyMenu=0x7f070007;
+        public static final int presetThingyList=0x7f070001;
+        public static final int resetMenu=0x7f070004;
+        public static final int settingsMenu=0x7f070003;
+        public static final int thingyToggleButton=0x7f070002;
     }
     public static final class layout {
         public static final int default_list_item=0x7f030000;
@@ -38,19 +38,22 @@ public final class R {
         public static final int simple_thingy=0x7f030003;
     }
     public static final class menu {
-        public static final int homemenu=0x7f050000;
-        public static final int presetlistmenu=0x7f050001;
-        public static final int presetmenu=0x7f050002;
-        public static final int thingylistmenu=0x7f050003;
+        public static final int homemenu=0x7f060000;
+        public static final int presetlistmenu=0x7f060001;
+        public static final int presetmenu=0x7f060002;
+        public static final int thingylistmenu=0x7f060003;
     }
     public static final class string {
-        public static final int addThingyMenu=0x7f040004;
-        public static final int app_name=0x7f040000;
-        public static final int newPresetMenu=0x7f040003;
-        public static final int newThingyMenu=0x7f040001;
-        public static final int presetActivate=0x7f040002;
-        public static final int presetIntroText=0x7f040006;
-        public static final int renamePresetMenu=0x7f040005;
-        public static final int resetMenu=0x7f040007;
+        public static final int addThingyMenu=0x7f050004;
+        public static final int app_name=0x7f050000;
+        public static final int newPresetMenu=0x7f050003;
+        public static final int newThingyMenu=0x7f050001;
+        public static final int presetActivate=0x7f050002;
+        public static final int presetIntroText=0x7f050006;
[…]

### 2012-05-13 prototype/src/dk/itu/spcl/dex/Bootstrapper.java

@@ -21,8 +21,10 @@ public class Bootstrapper {
   private WifiManager _wifiManager;
   private String _ssid;
   private String _key;
+  private Context _context;
 
   public Bootstrapper(Context context, String ssid, String key) {
+    _context = context;
     _wifiManager = (WifiManager) context.getSystemService(Context.WIFI_SERVICE);
     _ssid = ssid;
     _key = key;
@@ -69,7 +71,7 @@ public class Bootstrapper {
       BufferedWriter writer = new BufferedWriter(new OutputStreamWriter(
           connection.getOutputStream(), Charset.forName("US-ASCII")));
       String response = "HTTP/1.1 200 OK\n" + "Content-Type: text/html\n"
-          + "\n" + Settings.HOME_SSID + "/" + Settings.HOME_PSK + "\n";
+          + "\n" + Settings.getHomeSsid(_context) + "/" + Settings.getHomePsk(_context) + "\n";
       writer.write(response);
       writer.flush();
       writer.close();

### 2012-05-13 prototype/src/dk/itu/spcl/dex/HomeActivity.java

@@ -1,14 +1,15 @@
 package dk.itu.spcl.dex;
 
-import dk.itu.spcl.dex.model.Repository;
 import android.app.TabActivity;
 import android.content.Intent;
 import android.content.res.Resources;
 import android.os.Bundle;
+import android.preference.PreferenceManager;
 import android.view.Menu;
 import android.view.MenuInflater;
 import android.view.MenuItem;
 import android.widget.TabHost;
+import dk.itu.spcl.dex.model.Repository;
 
 public class HomeActivity extends TabActivity {
 
@@ -21,6 +22,7 @@ public class HomeActivity extends TabActivity {
     _repository = Repository.getInstance();
     setContentView(R.layout.home);
     addTabs();
+    PreferenceManager.setDefaultValues(this, R.xml.settings, false); 
   }
 
   @Override
@@ -48,9 +50,16 @@ public class HomeActivity extends TabActivity {
     case R.id.resetMenu:
       _repository.reset();
       return true;
+    case R.id.settingsMenu:
+      showSettings();
+      return true;
     default:
       return super.onOptionsItemSelected(item);
     }
+  }
+
+  private void showSettings() {
+    startActivity(new Intent(this, SettingsActivity.class));
   }
 
   private void addTabs() {

### 2012-05-13 prototype/src/dk/itu/spcl/dex/Settings.java

@@ -1,9 +1,23 @@
 package dk.itu.spcl.dex;
 
+import android.content.Context;
+import android.content.SharedPreferences;
+import android.preference.PreferenceManager;
+
 public class Settings {
 
   public static final String THINGY_URL = "http://192.168.43.193/";
-  public static final String HOME_SSID = "HomeAP";
-  public static final String HOME_PSK = "abcdefgh";
+
+  public static String getHomeSsid(Context context) {
+    SharedPreferences sp = PreferenceManager
+        .getDefaultSharedPreferences(context);
+    return sp.getString("ssid", null);
+  }
   
-} 
+  public static String getHomePsk(Context context) {
+    SharedPreferences sp = PreferenceManager
+        .getDefaultSharedPreferences(context);
+    return sp.getString("key", null);
+  }
+
+}

### 2012-05-13 prototype/src/dk/itu/spcl/dex/SettingsActivity.java

@@ -1,0 +1,16 @@
+package dk.itu.spcl.dex;
+
+import android.os.Bundle;
+import android.preference.PreferenceActivity;
+
+public class SettingsActivity extends PreferenceActivity {
+
+  @Override
+  protected void onCreate(Bundle savedInstanceState) {
+    super.onCreate(savedInstanceState);
+    addPreferencesFromResource(R.xml.settings);
+  }
+  
+  
+
+}

### 2012-05-13 prototype/src/dk/itu/spcl/dex/ThingyActivity.java
getting status from thingy

@@ -2,6 +2,8 @@ package dk.itu.spcl.dex;
 
 import android.app.Activity;
 import android.os.Bundle;
+import android.view.View;
+import android.widget.ToggleButton;
 import dk.itu.spcl.dex.model.Repository;
 import dk.itu.spcl.dex.model.Thingy;
 
@@ -11,6 +13,7 @@ public class ThingyActivity extends Activity implements Repository.Listener {
   private ThingyUpdater _thingyUpdater;
   private Repository _repository;
   private ThingyStatusWriter _thingyWriter;
+  private ToggleButton _toggleButton;
 
   @Override
   protected void onCreate(Bundle savedInstanceState) {
@@ -25,7 +28,16 @@ public class ThingyActivity extends Activity implements Repository.Listener {
 
     setTitle("Thingy: " + _thingy.getName());
 
+    setContentView(R.layout.simple_thingy);
+    _toggleButton = (ToggleButton) findViewById(R.id.thingyToggleButton);
     _repository.addListener(this);
+    _toggleButton.setChecked(_thingy.getStatus());
+  }
+
+  public void thingyToggleButtonClicked(View v) {
+    ToggleButton button = (ToggleButton) v;
+    boolean on = button.isChecked();
+    //_thingyWriter.setStatus(_thingy, on);
   }
   
   @Override 
@@ -56,7 +68,7 @@ public class ThingyActivity extends Activity implements Repository.Listener {
     runOnUiThread(new Runnable() {
       @Override
       public void run() {
-  
+        _toggleButton.setChecked(_thingy.getStatus());  
       }
     });
   }

### 2012-05-13 prototype/src/dk/itu/spcl/dex/ThingyUpdater.java

@@ -13,7 +13,7 @@ import dk.itu.spcl.dex.tools.HttpTools;
 public class ThingyUpdater implements Runnable {
 
   private Thread _runningThread;
-  private final static int UPDATE_INTERVAL = 500;
+  private final static int UPDATE_INTERVAL = 2000;
   private Repository _repository;
   private ArrayList<Object> _listeners = new ArrayList<Object>();
   private static ThingyUpdater _instance;
@@ -76,20 +76,20 @@ public class ThingyUpdater implements Runnable {
   }
 
   private void updateThingy(Thingy thingy) {
-//    try {
-//      boolean thingyStatus = getStatusFromUrl(Settings.WIZARD_URL + thingy.getUrl());
-//      thingy.setStatus(thingyStatus);
-//    } catch (ClientProtocolException e) {
-//      Log.e("dex", e.toString());
-//    } catch (IOException e) {
-//      Log.e("dex", e.toString());
-//    }
+    try {
+      boolean thingyStatus = getStatusFromUrl(thingy.getUrl() + "values");
+      thingy.setStatus(thingyStatus);
+    } catch (ClientProtocolException e) {
+      Log.e("dex", e.toString());
+    } catch (IOException e) {
+      Log.e("dex", e.toString());
+    }
   }
 
   private boolean getStatusFromUrl(String url) throws ClientProtocolException,
       IOException {
     String responseText = HttpTools.readStringFromUrl(url);
-    return responseText.equals("1");
+    return responseText.contains("true");
   }
 
   private void pause() {

### 2012-05-13 prototype/src/dk/itu/spcl/dex/model/Thingy.java

@@ -8,7 +8,7 @@ public class Thingy implements Comparable<Thingy> {
 
   private String _name;
   private String _url;
-  private HashMap<String, Widget> _widgets = new HashMap<String, Widget>();
+  private boolean _status;
 
   public Thingy() {
   }
@@ -32,13 +32,14 @@ public class Thingy implements Comparable<Thingy> {
     _url = url;
     return this;
   }
-    
-  public void addWidget(Widget widget) {
-    _widgets.put(widget.getId(), widget);
-  }
   
   public boolean getStatus() {
-    return false;
+    return _status;
+  }
+  
+  public Thingy setStatus(boolean status) {
+    _status = status;
+    return this;
   }
   
   // standard overrides

### 2012-05-15 report/paper.tex
report template

--- 2012-02-29 proposal/proposal.tex
@@
-\documentclass{ubicomp2011}
+\documentclass{ubicomp2012}
 \usepackage{times}
@@
 \hypersetup{%
-pdftitle={Your Title}, pdfauthor={Your Authors}, pdfkeywords={your
+pdftitle={Thinges for Dummies}, pdfauthor={David Thomas, Egil Hansen}, pdfkeywords={your
 keywords}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
@@
 % (e.g. for preprints). Remove for camera ready copy.
+\toappear{Submitted for evaluation in the Pervasive Computing Lab class at IT University of Copenhagen, Spring 2012.}
 
-%\toappear{Paper submitted for evaluation in the Pervasive Computing Course, Spring 2012. The IT University of Copenhagen. Copyright remains with the authors.}
-
-\toappear{Project proposal for the Pervasive Computing Course, Spring 2012. The IT University of Copenhagen. Copyright remains with the authors.}
-
-\title{UbiComp 2011 Conference Proceedings Format}
+\title{Thingies for Dummies}
 \numberofauthors{2}
 \author{
+  \alignauthor David Thomas\\
+    Author\\
+    \email{dtho@itu.dk}
  \alignauthor Egil Hansen\\
-    \affaddr{IT University of Copenhagen}\\
-%    \affaddr{Address  (Blank for Blind Review)}\\
-    \email{ekri@itu.dk}
- \alignauthor David Thomas\\
-    \affaddr{IT University of Copenhagen}\\
-%    \affaddr{Address  (Blank for Blind Review)}\\
-    \email{dtho@itu.dk}  }
+    Author\\
+    \email{ekri@itu.dk}  }
 \maketitle
 
-%\begin{abstract}
-%  In this paper we describe the formatting requirements for the UbiComp 2011
-%  Conference Proceedings, and offer recommendations on writing for the
-%  worldwide Ubiquitous Computing readership.  Please review this document even if
-%  you have submitted to Ubiquitous Computing conferences before, for some format
-%  details have changed relative to previous years. These include the
-%  formatting of table captions, the formatting of references, a
-%  requirement to include ACM DL indexing information, and guidelines for how to handle relevant references to your own work while preparing your submission for blind review.
-%\end{abstract}
+\begin{abstract}
 
-%\keywords{Guides, instructions, authors' kit, conference publications.}
+\end{abstract}
 
-%\category{H.5.2}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}.
+\keywords{Guides, instructions, authors' kit, conference publications.}
 
-%\generalterms{This section is limited to the following 16 terms and
-%MUST be included on the first page of all submissions after the ACM
-%Categories section, then as well chosen properly on the Proceedings
-%or Publication's submission page: Algorithms, Design,
-%Documentation, Economics, Experimentation, Human Factors, Languages,
-%Legal Aspects, Management, Measurement, Performance, Reliability,
-%Security, Standardization, Theory, Verification.}
+\category{H.5.2}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}.
 
-\section{Background}
-hep
+\generalterms{Design,
+Documentation, Economics, Experimentation, Human Factors, Languages, Management, Measurement, Performance, Reliability,
+Security, Standardization, Theory, Verification.}
 
-\section{Idea}
-hep
+\section{Introduction}
 
-\section{Scenario}
-hep
+More than 20 years after Weiser first defined ubiquitous computing \cite{Weiser1991} we have yet to see smart homes become commonplace.
+We believe this is largely due to smart home technology being inaccessible and too complicated for everyday users, and both price, perceived lack of advantages, and challenges in learning new technology scare users away.
 
-\section{Plan}
-hep
+In this paper we propose a smart home infrastructure that allow homeowners to cheaply bring new smart home technology into their existing homes in small batches, technology that homeowners will realistically be able to install and manage themselves.
+Our proposed infrastructure bases itself on hardware that exists in most homes today -- Wifi and smart phones -- and uses simple and open protocols like HTTP and the WebSocket protocol to provide the communication backbone of the infrastructure.
+Each individual device, or ``Thingy'', as we have dubbed them, is supposed to be simple to install and use, but provide value nonetheless.
+We call this concept \textit{Thingies for Dummies}\footnote{This is a reference to the \textit{For Dummies} book series that tries to present non-intimidating guides to various topics and that always contains the subtitle ``A Reference for the Rest of Us!''.}.
 
-\subsection{Equipment}
-hep
+Edwards and Grinter describe, in their 2001 paper\cite{Edwards01athome}, seven challenges facing the adoption of smart home technology\footnote{Challenge One: \textit{The `Accidentally' Smart Home}.
+Challenge Two: \textit{Impromptu Interoperability (islands of functionality)}.
+Challenge Three: \textit{No Systems Administrator}.
+Challenge Four: \textit{Designing for Domestic Use}.
+Challenge Five: \textit{Social Implications of Aware Home Technologies}.
+Challenge Six: \textit{Reliability}.
+Challenge Seven: \textit{Inference in the Presence of Ambiguity}.}, and we believe that through the overarching theme of `simple' in our proposal -- simple infrastructure and simple Thingies -- we are able to answer the first six challenges, at least partly.
+Simplifying does imply giving up on the dream of a fully automated intelligent home for the time being, but our proposed infrastructure does not prevent a home from becoming gradually more automated or intelligent as developers become better at utilizing the platform.
 
-% Referencer:
-% ~\cite{ref}
+When we started doing research for this project we first wanted to see if we could come up with a few use cases where some smart home technology would add so much value, that a normal homeowner would go out and invest time and money to retrofit the home.
+Through our informal questioning of friends, colleagues, and family, it quickly became clear that promise of the classic intelligent appliances we see in many office buildings that automatically adjusts their operations through context awareness\footnote{Appliances such as HVAC, lights fixtures, window curtains, and automatic doors.} did not have a strong enough appeal.
+The only thing that really resonated was various remote control scenarios.
+Examples included double checking if all the lights are turned off at home, remotely starting the washer when leaving from work so clean cloth is ready to be hung up to dry when the user gets home, and remotely unlocking the front door to the home if a friend is waiting and the owner is running late.
+With that in mind,  we created the following scenario to guide our design process:
 
-% til sidst
-%\nocite{example-journal,example-abstracts,example-conference2}
+\textit{After putting his children to bed, Peter is ready to go to sleep as well.
+He sits on his bed and picks up his phone and navigates to his Home Remote app, where he selects the ``Lock down'' preset.
+Once selected, the app sets all the homes  actuators into their specified lock down mode, i.e.
+all doors are locked, lights are turned] off, curtains are drawn, and the array of sensors in the house reports back what they see.
+Peter scrolls through the list and sees a warning indicating an open window in the kitchen.
+Peter stands up and walks out of the bedroom towards the kitchen.
+As he walks with his phone in his hand, the management software turns on the light around him and unlocks the doors he is near, while keeping everything else in lock down mode.
+Once the window in the kitchen is closed, the sensor indicator on his phones turns green Peter returns to his bedroom for a good night’s sleep.}
+
+Even if this scenario does not describe a remote control scenario where the user is many kilometers away, it is still remote by our definition.
+We consider anything remote if the user is able to control a Thingy without being able to observe how it affects its surroundings.
+For example,  if user A is sitting in room A, and remotely controlling a lamp in room B, and user A is unable to see what is going on in room B, i.e.
+see the physical lamp turn on and off or see if there are people or other appliances in room B that react to the lamps state change, then it does not matter if room A and room B are right next to each other or on opposite sites of the word, it is remote controlling scenario because user A has the same information available in both cases.
+
+In the next section we will describe our proposed infrastructure in details and discuss the design.
+Following that, we will present related work and end with our implementation, evaluation and discussion of the prototype we built.
+
+\section{Thinges for Dummies Infrastructure}
+
+The key design decision for \textit{Thingies for Dummies} is that it should be simple and  inexpensive to get started retrofitting an existing house with thingies and that it should be independent of specific hardware and software platforms.
+This means not requiring a dedicated, centralized controller, and instead to rely on the existing infrastructure in the home for handling communication and control, i.e.
+a Wifi network and smart phones.
+By doing so, we limit the amount of new hardware required to get started, since most homes will already have a Wifi network and at least one smartphone.
+This lowers the price and reduces the environmental impact.
+
+In the rest of this section we will describe each of the critical elements in our proposed infrastructure that enable this and discuss our design decisions.
+
+\subsection{Networking, protocols, and Security}
+
+With so many networking technologies care must be taken before choosing one above another, however, we arrived at our choice, Wifi, pretty fast.
+One of our primary requirements was that the network should exist in most homes already.
+This eliminates quite a few choices right away, leaving us with power lines, which the X10 protocol uses, cellular networks such as 3G, phone line wiring and Wifi.
+Using power lines, which usually reaches all rooms in a home, has problems with the boundary of the network where since data signals can travel out of the home.
+It is also inherently a wired network, which means an extra bridge device is needed between the power lines and mobile devices if those are to interact with devices connected to it.
+The phone lines inside the home has similar problems, and is also far less ubiquitous in the home, with most homes only having a few phone plugs.
+This leaves cellular networks, which are indeed wireless, but also owned and maintained by carrier companies, that charges fees for the data that travels on their network.
+This makes cellular networks less ideal choices, landing us squarely on Wifi as the preferred option.
+
+There are many advantages to choosing the Wifi as the basis for our infrastructure and a few drawbacks.
+Users get to reuse their existing Wifi in their home, thus saving money and time setting up a new device.
+Wifi also adds, assuming it is protected with a passphrase, a virtual boundary to the smart home, a boundary that users understand because they understand that you cannot access the Wifi without the passphrase.
+Wifi also have the advantage of being a high bandwidth network which enables thingies such as high resolution CCTV cameras.
+
+The biggest drawback related to Wifi is that it is power hungry compared to other technologies such as ZigBee.
+However, there is a general focus from the Wifi radio chip makers to lower power consumption due to the massive surge of mobile devices the last few years, so the drawback will matter less as Wifi radios become more power friendly.
+In addition, for many of the scenarios we have found users to be interested in, Thingies will have a permanent power source.
+In the case where low powered sensor thingies are required, we expect these to use a protocol like ZigBee\cite{zigbeeWebsite} and be bundled with a special purpose Thingy which act as a bridge between the individual ZigBee enabled Thingies the Wifi network.
+The bridge Thingy could also perform other tasks so the extra cost would be negligible.
+
+We also discussed the problems with oversaturation and general instabilities of the average home Wifi network.
+This is of course very dependent on the model of the wireless access point used.
+Better models with good Wifi radios, antennas, faster CPUs, and enough memory, can handle around 25 concurrent connected clients, while lesser models choke at at half as many connections.
+However, since one of our design goals was that it should be as inexpensive as possible to get started with smart home technology, we do not expect a average home Wifi to get saturated right away.
+The scenario where a homeowner invests in over 20 new thingies at the same time might not be unlikely, but in that case we feel that investment in an extra access point to handle traffic from Thingies is probably also within the budget.
+It is common knowledge among Wifi experts that Wifi clients also have a tendency to drop their connection from access points more often if using the higher bandwidth 802.11n and 802.11g protocols compared to the slower 802.11b.
+The solution here is to make Thingies use 802.11b where possible, and since only a very small subset of Thingies will require a 100\% stable connection, homeowners should experience no problems since Thingies can simply reconnect if their connection drops.
+
+\subsubsection{Communication protocols}
+
+For communication, we use standard HTTP \cite{Fielding:1999:HTP:RFC2616}.
+This opens up for a huge list of possible controllers, basically any type of computing device or library that supports HTTP.
+This is especially important to us since we do not want to be limited to a certain framework, language, or platform, e.g.
+Java\footnote{\url{http://java.com}} or Android\footnote{\url{http://android.com}}.
+Other great properties of HTTP is that it is fairly lightweight and stateless protocol, which simplifies things considerably on the Thingies.
+HTTP also supports our goal of an open infrastructure; it might very well be the best supported protocol among developers, and this enables the average app developer to build new functionality on top of the infrastructure on their platform of choice.
+Another benefit is that HTTP communication is very unlikely to be blocked in firewalls compared to other less used protocols, so there is a much bigger chance that things will just work.
+
+However, HTTP's statelessness \cite{Fielding:1999:HTP:RFC2616} is also a weakness in common smart home scenarios, where a context change in one Thingy should trigger an event in another Thingy.
+With basic HTTP, a Thingy (client) waiting for a state change has to continuously poll the other Thingy it is monitoring to discover the state change in a timely manner.
+This is an waste of resources and could potentially deplete the resources of a Thingy entirely, especially if more clients are waiting for changes.
+Clearly, relying only on HTTP alone does not scale.
+Several solutions to this problem were considered, the biggest contender to be considered being multicast.
+The advantages of using multicast is that Thingies can simply announce state changes on the network and it would not matter if zero, one, or hundreds of clients were interested, the amount of resources required to do so would be the same.
+Ignoring the problems associated multicast on Wifi, i.e.
+lost multicast packets are not retransmitted at the MAC layer \cite{conf/icnp/ChandraKMNPRR09}, the reason we did not choose multicast was that the protocol works on a lower level compared to HTTP, and that would limit the number of supported development platforms.
+We wanted to stay in the Web-stack of technologies so we chose the WebSocket protocol.
+In the recent years, the WebSocket protocol has been standardized by the Internet Engineering Task Force (IETF)\cite{IETFWebsockets} and is in the process of being standardized by the World Wide Web Consortium (W3C)\cite{w3cWebsockets}.
+The WebSocket protocol supports multiplexing bi-directional, full-duplex communications channels over a single TCP connection and is already supported by the latests versions of most major browsers\footnote{The WebSocket protocol is supported from Chrome 16, Firefox 11 and Internet Explorer 10.}, with numerous frameworks and libraries also on the way.
+The WebSocket Protocol was essentially designed to be a solution for the scenario where a server needs to push information to a client\cite{IETFWebsockets} which web developers have been struggling with for many years, so while it might not scale as well as multicast, we feel this is the best overall approach.
+
+\subsubsection{Service Discovery}
+Most home networks do not have traditional unicast DNS server set up, so we need a different way to discover Thingies connect to the network, both during installation and also if and when their IP address changes.
+We have decided to use mDNS/Bonjour\footnote{Bonjour is available on \url{https://developer.apple.com/opensource/}} since it offers wide support across platforms and is relatively lightweight.
+
+\subsubsection{Security considerations}
+
+The basic trust model for Thingies for Dummies is based on the security of the home's Wifi.
+Assuming the Wifi is probably configured using WPA2 with AES encryption and a reasonable passphrase, there is a clear boundary for the smart home, and an adversary would not be able to pick up data sent to and from Thingies without being connected to the network.
+This also means, that anyone on the network have full control over the Thingies attached to it, which can be a problem in some cases.
+We have discussed the possibility of adding an extra layer of security that would handle such a case.
+If the concern is only that unauthorised users cannot perform certain actions on a Thingy, i.e.
+only change state, not update configuration, then we need a way to authenticate each user.
+This could be done using certificates that clients use to authenticate with.
+The certificate would be generated during the initial configuration of a Thingy, and depending on the number of authorisation levels needed for a Thingy, e.g.
+read only, update state, and update configuration, one or more unique certificates would be generated.
+Then it would be up to the controller devices used during the initial configuration to distribute the generated certificates to authorized users.
+However, it is not enough only to authenticate users, since the communication between users and Thingies are still being transmitted over an open channel which can allow an adversary to perform replay attacks.
+The solution to this is to secure the communication channel between users and Thinges, i.e.
+using HTTPS.
+Adding the extra level of security does raise the hardware requirements on Thingies which increases cost and power consumption, so an environment that supports both ``open'', low risk Thingies and ``secure'' Thingies should provide the best of both worlds.
 
 \bibliographystyle{abbrv}
-\bibliography{proposal}
+\bibliography{bibliography}
 

### 2012-05-15 report/paper.tex
almost final draft of paper

--- 2012-05-07 report/paper.tex
@@
-\documentclass{article}
+\documentclass{ubicomp2012}
+\usepackage{times}
+\usepackage{url}
+\usepackage{graphics}
+\usepackage{color}
+\usepackage{mathtools}
+\usepackage{float}
+\usepackage[pdftex]{hyperref}
+\usepackage{listings}
+\lstset{ %
+  % language=C,             % the language of the code
+  basicstyle=\ttfamily,         % the size of the fonts that are used for the code
+  showspaces=false,             % show spaces adding particular underscores
+  showstringspaces=false,       % underline spaces within strings
+  showtabs=false,              % show tabs within strings adding particular underscores
+  tabsize=2,                    % sets default tabsize to 2 spaces
+  captionpos=b,                 % sets the caption-position to bottom
+  breaklines=true,              % sets automatic line breaking
+  breakatwhitespace=false     % sets if automatic breaks should only happen at witespace
+}
+\hypersetup{%
+pdftitle={Thinges for Dummies - A Smart}, pdfauthor={David Thomas, Egil Hansen}, pdfkeywords={your
+keywords}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
+citecolor=black, filecolor=black, linkcolor=black, urlcolor=black,
+breaklinks=true, }
+\newcommand{\comment}[1]{}
+\definecolor{Orange}{rgb}{1,0.5,0}
+\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[[#1]]}}}}
+
+\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy
 
 \begin{document}
+% to make various LaTeX processors do the right thing with page size
+\special{papersize=8.5in,11in}
+\setlength{\paperheight}{11in}
+\setlength{\paperwidth}{8.5in}
+\setlength{\pdfpageheight}{\paperheight}
+\setlength{\pdfpagewidth}{\paperwidth}
+
+% use this command to override the default ACM copyright statement
+% (e.g. for preprints). Remove for camera ready copy.
+\toappear{Submitted for evaluation in the Pervasive Computing Lab class at IT University of Copenhagen, Spring 2012.}
+
+\title{Thingies for Dummies\\A smart home infrastructure for the rest of us}
+\numberofauthors{2}
+\author{
+  \alignauthor David Thomas\\
+    \email{dtho@itu.dk}
+ \alignauthor Egil Hansen\\
+    \email{ekri@itu.dk}  }
+\maketitle
 
 \begin{abstract}
-  TODOlish
+
 \end{abstract}
+
+\keywords{TODO.}
+
+\category{H.5.2}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}.
+
+\generalterms{Design,
+Documentation, Economics, Experimentation, Human Factors, Languages, Management, Measurement, Performance, Reliability,
+Security, Standardization, Theory, Verification.}
 
@@
 
-We propose a smart home infrastructure which bases itself on hardware that exist in most homes today -- Wifi and smart phones -- and use simple, open, interoperable technologies such as HTTP and HTML5's web sockets to provide the communication backbone of the architecture.
-Each individual device, or ``thingy'', as we have dubbed them, is supposed to be simple to comprehend, install, and use, but provide value nonetheless.
+In this paper we propose a smart home infrastructure that allow homeowners to cheaply bring new smart home technology into their existing homes in small batches, technology that homeowners will realistically be able to install and manage themselves.
+Our proposed infrastructure bases itself on hardware that exists in most homes today -- Wi-Fi and smart phones -- and uses simple and open protocols like HTTP and the WebSocket protocol to provide the communication backbone of the infrastructure.
+Each individual device, or ``Thingy'', as we have dubbed them, is supposed to be simple to install and use, but provide value nonetheless.
 We call this concept \textit{Thingies for Dummies}\footnote{This is a reference to the \textit{For Dummies} book series that tries to present non-intimidating guides to various topics and that always contains the subtitle ``A Reference for the Rest of Us!''.}.
 
-Edwards and Grinter describe in their 2001 paper \cite{Edwards01athome} seven challenges facing the adoption of smart home technology\footnote{Challenge One: \textit{The `Accidentally' Smart Home}.
-Challenge Two: \textit{Impromptu Interoperability (islands of functionality)}.
-Challenge Three: \textit{No Systems Administrator}.
-Challenge Four: \textit{Designing for Domestic Use}.
-Challenge Five: \textit{Social Implications of Aware Home Technologies}.
-Challenge Six: \textit{Reliability}.
-Challenge Seven: \textit{Inference in the Presence of Ambiguity}.}, and we believe that through the overarching theme of `simple’ in our proposal -- simple architechure and simple thingies -- we are able to answer the first six challenges, at least partly.
-Simplifying things does imply giving up on the dream of a fully automated intelligence home for the time being, but our proposed infrastructure does not prevent a home from becoming gradually more automated or intelligent.
+Edwards and Grinter describe, in their 2001 paper \cite{Edwards01athome}, seven challenges facing the adoption of smart home technology\footnote{1: \textit{The `Accidentally' Smart Home}.
+2: \textit{Impromptu Interoperability (islands of functionality)}.
+3: \textit{No Systems Administrator}.
+4: \textit{Designing for Domestic Use}.
+5: \textit{Social Implications of Aware Home Technologies}.
+6: \textit{Reliability}.
+7: \textit{Inference in the Presence of Ambiguity}.}, and we believe that through the overarching theme of `simple' in our proposal -- simple infrastructure and simple thingies -- we are able to answer the first six challenges, at least partly.
+Simplifying does imply giving up on the dream of a fully automated intelligent home for the time being, but our proposed infrastructure does not prevent a home from becoming gradually more automated or intelligent as developers become better at leveraging the platform.
 
-\paragraph{TODO in this section:}
+When we started doing research for this project we first wanted to see if we could come up with a few use cases where some smart home technology would add so much value, that a normal homeowner would go out and invest time and money to retrofit the home.
+Through our informal questioning of friends, colleagues, and family, it quickly became clear that the promise of the classic intelligent appliances we see in many office buildings that automatically adjusts their operations through context awareness\footnote{Appliances such as HVAC, light fixtures, window curtains, and automatic doors.} did not have a strong enough appeal.
+The only thing that really resonated was various remote control scenarios.
+Examples included double checking if all the lights are turned off at home, controlling radiators, remotely starting the washer when leaving from work so clean clothes are ready to be hung up to dry when the user gets home, and remotely unlocking the front door to the home if a friend is waiting and the owner is running late.
+With that in mind,  we created the following scenario to guide our design process:
+
+\textit{After putting his children to bed, Peter is ready to go to sleep as well.
+He sits on his bed and picks up his smartphone and navigates to his Home Remote app, where he selects the ``Lock down'' preset.
+Once selected, the app sets all the homes  actuators into their specified lock down mode, i.e.
+all doors are locked, lights are turned off, curtains are drawn, and the array of sensors in the house reports back what they see.
+Peter looks at the status screen and sees a warning indicating an open window in the kitchen.
+Peter stands up and walks out of the bedroom towards the kitchen.
+As he walks with his phone in his hand, the management software turns on the light around him and unlocks the doors he is near, while keeping everything else in lock down mode.
+Once the window in the kitchen is closed, the sensor indicator on his phones turns green Peter returns to his bedroom for a good night's sleep.}
+
+Even if this scenario does not describe a remote control scenario where the user is many kilometers away, it is still remote by our definition.
+We consider anything remote to be if the user is able to control a thingy without being able to observe how it affects its surroundings.
+For example,  if user A is sitting in room A, and remotely controlling a lamp in room B, and user A is unable to see what is going on in room B, i.e.
+see the physical lamp turn on and off or see if there are people or other appliances in room B that react to the lamps state change, then it does not matter if room A and room B are right next to each other or on opposite sites of the word, it is a remote controlling scenario because user A has the same information available in both cases.
+
+\section{Thinges for Dummies Infrastructure}
+The key design decision for \textit{thingies for Dummies} is that it should be simple and  inexpensive to get started retrofitting an existing house with thingies and that it should be independent of specific hardware and software platforms.
+This means not requiring a dedicated, centralized controller, and instead to rely on the existing infrastructure in the home for handling communication and control, i.e.
+a Wi-Fi network and smart phones.
+By doing so, we limit the amount of new hardware required to get started, since most homes will already have a Wi-Fi network and at least one smartphone.
+This lowers the price and reduces the environmental impact.
+Figure \ref{fig:infrastructureOverview} shows an overview of the infrastructure:
+
+\begin{figure}[th]
+\begin{center}
+\includegraphics[width=0.90\columnwidth]{figures/systemoverviewdrawing.png}
+\end{center}
+\caption{Overview of the infrastructure}
+\label{fig:infrastructureOverview}
+\end{figure}
+
+An existing Wi-Fi network in the home provides the communications channel.
+The user's smartphone is connected to this network.
+A number of thingies -- exemplified in the figure as a light switch and a window sensor -- are brought into the home and connected to the Wi-Fi network as well.
+An app on the smartphone then enables the user control and check on the thingies.
+
+In the rest of this section we will describe each of the critical elements in our proposed infrastructure and discuss our design decisions.
+
+\subsection{Networking, protocols, and Security}
+
+With so many networking technologies available care must be taken before picking one above another, however, we arrived at our choice, Wi-Fi, pretty fast.
+One of our primary requirements was that the network should exist in most homes already.
+This eliminates quite a few choices right away, leaving us with power lines, which the X10 protocol uses, cellular networks such as 3G, phone line wiring, Bluetooth, and Wi-Fi.
+Power lines, which has the advantage of reaches all rooms in a home, has problems with the an uncertain network boundaries, since there is usually no special gateway or firewall preventing data from traveling on the power lines to the neighbours power lines, unless extra hardware is added.
+Power lines are also inherently a wired network, which means an extra bridge device is needed between the power lines and wireless mobile devices if those are to interact with devices connected to it.
+The phone lines inside the home has similar problems, and is also far less ubiquitous in the home, with most homes only having a few phone plugs.
+Then there is Bluetooth, which most laptops and phones, even feature phones, come equipped with.
+Bluetooth is however limited in range.
+This leaves cellular networks, which are indeed wireless, but also owned and maintained by carrier companies, that charges fees for the data that travels on their network and not all areas are covered equally well.
+This makes cellular networks the less ideal choice, landing us squarely on Wi-Fi as the preferred option.
+
+There are many advantages to choosing the Wi-Fi as the basis for our infrastructure and a few drawbacks.
+Users get to reuse their existing Wi-Fi in their home, thus saving money and time setting up a new device.
+Wi-Fi also adds, assuming it is protected with a passphrase, a virtual boundary to the smart home, a boundary that users understand because they understand that you cannot access the Wi-Fi without the passphrase.
+Wi-Fi also have the advantage of being a high bandwidth network which enables thingies such as high resolution CCTV cameras.
+
+The biggest drawback related to Wi-Fi is that it is power hungry compared to other technologies such as ZigBee \cite{zigbeeWebsite}.
+However, there is a general focus from the Wi-Fi radio chip makers to lower power consumption due to the massive surge of battery driven mobile devices the last few years, so the drawback will matter less as Wi-Fi radios become more power friendly.
+In addition, for many of the scenarios we have found users to be interested in, thingies will have a permanent power source and in the case where low powered sensor thingies are required, we expect these to use a protocol like ZigBee\cite{zigbeeWebsite} and be bundled with a special purpose thingy which act as a bridge between the individual ZigBee enabled thingies the Wi-Fi network.
+The bridge thingy could also perform other tasks so the extra cost would be negligible.
+
+We also discussed the problems with oversaturation and general instabilities of the average home Wi-Fi network.
+This is of course very dependent on the model of the wireless access point used.
+Better models with good Wi-Fi radios, antennas, faster CPUs, and enough memory, can handle around 25 concurrent connected clients, while lesser models choke at at half as many connections.
+However, since one of our design goals was that it should be as inexpensive as possible to get started with smart home technology, we do not expect a average home Wi-Fi to get saturated right away.
+The scenario where a homeowner invests in over 20 new thingies at the same time might not be unlikely, but in that case we feel that investment in an extra access point to handle traffic from thingies is probably also within the budget.
+It is common knowledge among Some Wi-Fi experts claim that Wi-Fi clients also have a tendency to drop their connection from access points more often if using the higher bandwidth 802.11n and 802.11g protocols compared to the slower 802.11b.
+The solution here is to make thingies use 802.11b where possible, and since only a very small subset of thingies will require a 100\% stable connection, homeowners should experience no problems since thingies can simply reconnect if their connection drops.
+\subsubsection{Communication protocols}
+
+For communication, we use standard HTTP \cite{Fielding:1999:HTP:RFC2616}.
+This opens up for a huge list of possible controllers, basically any type of computing device or library that supports HTTP.
+This is especially important to us since we do not want to be limited to a certain framework, language, or platform, e.g.
+Java\footnote{\url{http://java.com}} or Android\footnote{\url{http://android.com}}.
+Other great properties of HTTP is that it is fairly lightweight and stateless protocol \cite{Fielding:1999:HTP:RFC2616}, which simplifies things considerably on the thingies.
+HTTP also supports our goal of an open infrastructure; it might very well be the best supported protocol among developers, and this enables the average app developer to build new functionality on top of the infrastructure on their platform of choice.
+Another benefit is that HTTP communication is very unlikely to be blocked in firewalls compared to other less used protocols, so there is a much bigger chance that things will just work.
+
+However, HTTP's statelessness is also a weakness in common smart home scenarios, where a context change in one thingy should trigger an event in another thingy.
+With basic HTTP, a thingy (client) waiting for a state change has to continuously poll the other thingy it is monitoring to discover the state change in a timely manner.
+This is an waste of resources and could potentially deplete the resources of a thingy entirely, especially if more clients are waiting for changes.
+Clearly, relying only on HTTP alone does not scale.
+Several solutions to this problem were considered, the biggest contender to be considered being multicast.
+The advantages of using multicast is that thingies can simply announce state changes on the network and it would not matter if zero, one, or hundreds of clients were interested, the amount of resources required to do so would be the same.
+Ignoring the problems associated multicast on Wi-Fi, i.e.
+lost multicast packets are not retransmitted at the MAC layer \cite{conf/icnp/ChandraKMNPRR09}, the reason we did not choose multicast was that the protocol works on a lower level compared to HTTP, and that would limit the number of supported development platforms.
+We wanted to stay in the Web-stack of technologies so we chose the WebSocket protocol.
+In the recent years, the WebSocket protocol has been standardized by the Internet Engineering Task Force (IETF) \cite{IETFWebsockets} and is in the process of being standardized by the World Wide Web Consortium (W3C) \cite{w3cWebsockets}.
+The WebSocket protocol supports multiplexing bi-directional, full-duplex communications channels over a single TCP connection and is already supported by the latests versions of most major browsers\footnote{The WebSocket protocol is supported from Chrome 16, Firefox 11 and Internet Explorer 10.}, with numerous frameworks and libraries already built and more on the way.
+The WebSocket Protocol was essentially designed to be a solution for the scenario where a server needs to push information to a client\cite{IETFWebsockets} which web developers have been struggling with for many years, so while it might not scale as well as multicast, we feel this is the best overall approach.
+
+\subsubsection{Service Discovery}
+Most home networks do not have traditional unicast DNS server set up, so we need a different way to discover thingies connect to the network, both during installation and also if and when their IP address changes.
+We have decided to use mDNS/Bonjour\footnote{Bonjour is available on \url{https://developer.apple.com/opensource/}} since it offers wide support across platforms and is relatively lightweight and open source.
+.
+\subsubsection{Security considerations}
+
+The basic trust model for thingies for Dummies is based on the security of the home's Wi-Fi.
+Assuming the Wi-Fi is probably configured using WPA2 with AES encryption and a reasonable passphrase, there is a clear boundary for the smart home, and an adversary would not be able to pick up data sent to and from thingies without being connected to the network.
+This also means, that anyone on the network have full control over the thingies attached to it, which can be a problem in some cases.
+We have discussed the possibility of adding an extra layer of security that would handle such a case.
+If the concern is only that unauthorised users cannot perform certain actions on a thingy, i.e.
+only change state, not update configuration, then we need a way to authenticate each user.
+This could be done using certificates that clients use to authenticate with.
+The certificate would be generated during the initial configuration of a thingy, and depending on the number of authorisation levels needed for a thingy, e.g.
+read only, update state, and update configuration, one or more unique certificates would be generated.
+Then it would be up to the controller devices used during the initial configuration to distribute the generated certificates to authorized users.
+However, it is not enough only to authenticate users, since the communication between users and thingies are still being transmitted over an open channel which can allow an adversary to perform replay attacks.
+The solution to this is to secure the communication channel between users and Thinges, i.e.
+using HTTPS.
+Adding the extra level of security does raise the hardware requirements on thingies which increases cost and power consumption, so an environment that supports both ``open'', low risk thingies and ``secure'' thingies should provide the best of both worlds.
+
+\subsection{thingies - actuators and sensors}
+
+To help us narrow down the responsibilities, requirements, and goals for thingies we looked closely at both the scenario described in the introduction of this paper and Edwards et al's \cite{Edwards01athome} work.
+In summary, thingies should be:
+
 \begin{itemize}
-\item Overview of the coming sections
-\item Discussion of smart homes vs smart office (or discussion)
-\item Scenario (lock down)
-\item Should we include a more detailed description of why we solve six challenges, or is that for the discussion section?
+\item Easy to install, maintain, and understand
+\item Independent
+\item Have a consistent and predictable software interface
 \end{itemize}
 
-\section{Thinges for Dummies Infrastructure}
+The first two points are important because thingies must be installable and manageable by non-technical users.
+It is also reasonable to assume that a simple thingy with one or two functions is going to be more reliable than a device with several functions.
+Not allowing thingies to be dependent on other thingies or services simplifies everything, which again helps makes things easier for the non-technical user.
+Making things simple also means being less dependent on constant firmware updates, which will limit the amount of maintenance required after the initial installation.
+This is highly important, as Kindberg et al writes, \textit{ ``You can't reboot the world, let alone rewrite it, to introduce new functionality.
+Users shouldn't be led into a disposable physical world just because they can't keep up with software upgrades.''} \cite{kindbergSystem}.
 
-The key design decision for \textit{Thingies for Dummies} was the it should be simple and  inexpensive to get started retrofitting an existing house with thingies and that it should be independent of specific hardware and software platforms.
-This ment not requiring a dedicated controller, and relying on the existing infrastructure in the home for handling communication and control, i.e.
-a Wifi network.
-Using the home’s Wifi, assuming it is protected with a passphrase, adds a virtual boundary to the smart home, a boundary that users understand because they understand that you cannot access the Wifi without the passphrase.
-[NOTE: Does this require a ref?]
+thingies can have running logic inside them, depending on their functionality, e.g.
+a power plug could be configured to turn on and off at specific times during the day, or turn on a secondary output if a specified amount of power is being drawn from a primary output, but it cannot depend on context outside of its domain, i.e.
+other thingies.
+Such logic should exist on controllers.
 
-For communication protocol, we decided to use HTTP and web sockets .
-This opens up for a huge list of possible controllers, basically any type of computer that understands HTTP.
-Using HTTP also enables remote management scenarios much easier, since HTTP traffic very unlikely to be blocked in firewalls.
-TODO MORE HERE ABOUT CLOUD
+The last point, have a consistent and predictable software interface, is important since controllers and thingies are loosely coupled to each other.
+A controller must be able to build the visual interface to a thingy without any prior knowledge of it, no matter if the thingy is just a ``read only'' sensor, an actuator or a thingy acting as a bridge for other thingies.
+To do so, a predictable software interface, in our case, an HTTP-based web service interface is required.
 
-You cannot have a smart home without controllers, and to us the obvious choice for controllers are smart phones.
-It is a device which users carries around with them all the time and are comfortable using.
-It does limit the
+How simple can a thingy be and still be useful?
+That is a question raised in \cite{Edwards01athome} and it turns out, at least from our informal questioning of friends, family, and colleagues, that even a simple thingy that enables remote toggle of a light switch is useful, and that it is better to have many simple things that end-users are able to comprehend individually instead of one big complex thingy.
 
-TODO in this section:
-- diagram of the architecture
-- mention cloud computing
-- intro to section
-- key design goals
-- overall infrastructure -- reasoning
-- something
+\subsubsection{Requirements}
 
-\subsection{Thingies}
+In keeping with the simple theme, we also have very few explicit physical requirements to thingies. They should:
 
-A Thingy can be either a sensor, a actuator, or a proxy for other Thingies.
-How simple can a thingy be and still be useful?
-That is a question raised in \cite{Edwards01athome} and it turns out, at least from our informal questioning of friends, family, and colleagues that even a simple Thingy that enables remote toggle of a light switch is useful.
+\begin{itemize}
+\item Have a unique identifier
+\item Have a passive NFC tag and/or QR code with its ID
+\item Have a physical reset/install mode button
+\item Be able to connect to an IP based network
+\end{itemize}
 
-Keeping thingies simple.
-- no UI
-- only operational configuration on the device
-- no transactions
+The unique identifier could easily be the MAC address of the Wi-Fi radio or a generic UUID \cite{Leach2005}.
+A unique ID is required since controllers need a way to identify individual thingies independent of how they are named.
 
-Bootstrapping devices
+The passive NFC tag or QR code and the physical button are all related to the bootstrapping phase, which we will describe later in this section.
 
-Security - wifi in the home determines that
-\subsection{Bootstrapping}
+Why not require a Wi-Fi radio in thingies?
+This is covered by the last requirement, but is more generalized, since we want to allow for thingies that connect directly through the LAN interface on the home Wi-Fi router, and also enable the scenario where a ZigBee enabled sensor thingies connect through a specialized ZigBee to Wi-Fi bridge thingy.
+We do however still require that all thingies can be reached on their own unique URI through the network.
+This is trivial for thingies connecting directly through Wi-Fi or LAN to the home network -- they simply have a standard URI \cite{uri-rfc} based on their IP address, e.g.
+\lstinline{http://192.168.0.42}.
+In the bridge scenario, the bridged thingies, e.g.
+ZigBee sensors, may have to share the IP of the bridge.
+Luckily, the URI schema allows for ports to be defined, so each bridged thingy will be identified by the bridges IP and their own port, e.g.
+\lstinline{http://192.168.0.42:1337}, \lstinline{http://192.168.0.42:1338}, etc.
 
-mDNS, Apple Bonjour
-\subsection{Configuration}
+\subsubsection{Web service interface}
 
-\subsection{Configuration synchronization}
+Each thingy will have a very basic web service interface consisting of a getter and a setter method, and a method to subscribe to be notified of state changes using the WebSockets protocol.
+Since controllers have no prior knowledge of thingies, thingies also have a dedicated method which returns a structured description of the their abilities.
+This makes it possible for the controller to render a UI that lets the user see and manage the state of the thingy.
 
-\subsection{Networking}
+The structured description associates each state variable in the thingy with an internally unique ID.
+This is what makes it possible to keep the service interface simple, as these IDs are used when querying and setting state.
+The following list summarizes the web service interface:
 
-\subsection{Security}
+\begin{itemize}
+\item \lstinline{/get?id=[list of ids]}\\
+Returns the current internal values in the thingy, possibly filtered by ids.
+\item \lstinline{/set?id=<id>&value=<value>}\\
+Sets the state of a specified internal value in the thingy.
+\item \lstinline{/ui}\\
+Returns the UI description for the thingy.
+\item \lstinline{/subscribe=[list of ids]}\\
+Subscribe to live updates of state changes, possibly filtered by ids.
+\end{itemize}
+
+The data sent to and from thingies are represented as JSON\footnote{\url{http://json.org/}}.
+We chose JSON since it is more lightweight than XML, but still structured.
+It is also easy to parse with libraries available for practically all platforms and languages, and it is aligned with our choice to stick with common web technologies when possible.
+
+\subsubsection{JSON UI Definition Language (JUIDL)}
+
+Inspired by similar work done in the LockIt paper \cite{lockit}, we also defined a JSON based UI definition language, tailored to our needs.
+The goal for our definition language was that it should convey to controllers \emph{what} type of state is available to controllers, but not \emph{how} that state should be represented visually.
+This is a similar to XML based Web Service Definition Language (WSDL) \cite{Christensen2001}, however, our JUIDL is much more lightweight, especially since we do not support complex objects.
+
+\subsection{Bootstrapping and installation}
+
+Installing new hardware on a home network is far from trivial, especially when that hardware has little or no UI, and few physical buttons to handle configuration.
+It is a topic being actively researched in the industry, including the Wi-Fi Alliance\footnote{\url{https://www.wi-fi.org}}.
+Their 2007 attempt, Wi-Fi Protected Setup (WPS)\footnote{WPS specifications available for purchase at \url{http://www.wi-fi.org/knowledge-center/articles/wi-fi-protected-setup}\texttrademark} was very promising and would have been our choice for easy bootstrapping, but considering the security problems discovered in 2011 \cite{StefanWPS}, we do not feel comfortable depending on a technology that makes Wi-Fi networks insecure if enabled.
+Instead, we have devised our own bootstrapping protocol.
+
+\subsubsection{Bootstrapping protocol}
+
+Thingies have two modes of operations -- installation mode and normal mode.
+A thingy can be put in installation mode by pressing a button, and should also arrive in installation mode from the manufacturer.
+In installation mode, the Wi-Fi radio of the thingy is put in access point mode, allowing another device to connect directly to it to configure it.
+
+The general bootstrapping process from a user's point of view is very simple.
+First, the user plugs in and turns on the thingy.
+Then, the user starts the Home Remote app on his smartphone and, after entering credentials for the Wi-Fi network, clicks ``Install new Thingy''.
+The onscreen instructions will prompt the user to scan the QR code or hold the phone close to the thingy (if the phone is NFC enabled).
+From this point, the phone and the thingy are connected to each other, and the user is asked to give it a name so it is identifiable by humans.
+The phone also sends the Wi-Fi credentials to the thingy.
+The diagram in figure \ref{fig:installworkflow} illustrates the workflow of the bootstrapping protocol from a technical point of view.
+
+\begin{figure}[th]
+\begin{center}
+\includegraphics[width=0.90\columnwidth]{figures/installation-workflow.pdf}
+\end{center}
+\caption{Workflow of the bootstrapping protocol.}
+\label{fig:installworkflow}
+\end{figure}
+
+Once the thingy is bootstrapped on to the home network, the thingy can be configured regularly through its configuration screen in the Home Remote app.
+
+As for security during bootstrapping, we do not think there is a likely attack vector.
+When a thingy is in installation mode and has its Wi-Fi radio in access point mode, it will have a passphrase set.
+With the passphrase randomized, it is very hard for an attacker to get access to a thingy and bootstrap it before the user is able to.
+Even if this unlikely scenario should occur, the user still retains full physical control over the device, and is able to turn it off or restart the installation process again.
+
+\subsection{Controllers}
+
+You cannot have a smart home without controllers, and to us, the obvious first choice for controllers are smart phones.
+It is a device which users carry all the time and are comfortable using.
+As the previous sections show, we are by no means limited to smart phones -- any computing device supporting the HTTP protocol can act as a controller.
+This is also our only requirements for simple controllers, although we do require a full controller to be able to perform bootstrapping of new thingies, which is where smartphones really shine.
+To enable the simplest form of user programming and automation on the controller level, and to make the scenario described in the introduction possible, we need a way to execute a batch of commands to different thingies.
+Our solution to this is something we have dubbed ``Presets''.
+A Preset consists of a name and a set of thingies, along with a desired state for each thingy.
+When the user defines a new Preset, he gives it a name and then adds one thingy at a time to the preset, specifying which state it should be in.When a Preset is triggered by the user, all thingies in the preset are put in the required state in sequential order, and the expected state of each thingies is checked.
+If any thingies in the Preset did not end up in the expected state, the user is notified.
+This also applies to thingies that are only sensors, where the Preset is simply used to verify their states.
+This enables relatively advanced scenarios such as our ``Lock Down'' scenario described earlier.
+
+This is clearly just the tip of the iceberg in terms of automation.
+It is easy to imaging additional functionality and in some cases it is simply a matter of enhancing the Preset concept, e.g.
+having Presets triggered at certain times.
+When designing more complex automation, there are other issues to consider; e.g.
+active monitoring of sensors might drain the battery of the phone too fast.
+
+\section{Related Work}
+
+The Internet of Things, implemented in e.g.
+HP's Cooltown project\cite{cooltown} is a concept related to ours in that it connects the physical and virtual worlds by creating an online presence for physical objects.
+The Cooltown project also mentions the use of local wireless networks as a means of access restriction.
+
+\subsection{Smart home technologies}
+
+X10\footnote{\url{http://x10.com}} is a low-level protocol from the 70s running through the power lines in a home.
+It allows one to control a number of devices using a pre-defined set of commands \footnote{url{http://software.x10.com/pub/manuals/xtdcode.pdf}}.
+Thus, it requires a controller device which is connected to the power lines.
+The power line medium also introduces potential issues with X10 commands leaving or entering a home.
+
+The Open Services Gateway Initiative, OSGi\cite{osgiIntroduction}, is an infrastructure designed by an alliance of over 80 companies.
+\cite{osgiDiscovery} describes how the technology can be used in the context of a smart home, including integration with devices through other technologies such as UPnP and Jini.
+The approach makes use of a gateway device within the home network.
+The infrastructure is marketed towards vendors and used in various products and solutions\cite{osgiMarkets}.
+
+Table \ref{smartHomeTable} compares some properties of our approach versus the ones we have mentioned:
+\begin{table}[H]
+\centering
+\begin{tabular}{| p{1cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{0.8cm} |}
+\hline
+& Installation by end-users & Security & Wireless control & Com-plex-ity \\ \hline
+X10 & Yes, with limitations & Relies on signals not leaving or entering the home & Requires extra equipment & Low \\ \hline
+OSGi & Yes, for some products & Varies with products & Varies with products & High \\ \hline
+Thingies for Dummies & Yes & Provided by Wi-Fi network & Yes & Low \\ \hline
+\end{tabular}
+\caption{Comparison of smart home approaches}
+\label{smartHomeTable}
+\end{table}
+
+Sources for X10: \footnote{\url{http://www.smarthome.com/about_x10.html}}, \footnote{\url{http://kbase.x10.com/wiki/MyHouse_Online_Remote_Connection_Setup}}.
+Sources for OSGi: \cite{osgiMarkets}, \cite{osgiDiscovery}.
+
+OSGi is a complex beast with many existing solutions.
+We have not been able to find one that matches ours in terms of simplicity.
+When it comes to simplicity and end-user installation, X10 is the approach most similar to ours.
+However, there is the caveat that X10 signals can enter and leave a home through the power lines, so for a secure installation, an electrician is required to install a filtering device.
+Additionally, X10 does not have the convenience of wireless control built in; this requires the addition of a controller device that supports this.
+\subsection{User interface generation}
+
+\cite{kindbergSystem} defines four levels of intelligence when moving user interfaces across devices, ranging from e.g.
+VNC\cite{vnc} where raw pixels and input events are transferred, to e.g.
+Jini\cite{jini} where the Java code that generates the UI is transferred.
+In-between, there are approaches where individual widgets are transferred, either by specifying precise widgets (i.e.
+``this is a drop down''), or on a purely semantic level (i.e.
+``this control must allow selection among these values'').
+We position ourselves in line with the latter, semantic approach.
+
+\cite{mobileServiceUsage} describes an approach for defining defining mobile user interfaces for web services, by adding two layers on top of the web service definition: one containing a semantic description of the service, and one containing a semantic description of the UI.
+While this approach may be more generally applicable than ours, it also introduces a considerable complexities.
+\section{Implementation}
+
+We have implemented a subset of our designed infrastructure.
+The implementation includes a sample thingy in the form of a light switch, and a controller in the form of an Android app.
+We have implemented bootstrapping of the thingy onto one's home Wi-Fi network as well as communication between the controller and the thingy.
+
+We have not implemented secure thingies with user authentication, or synchronization of configuration across users; nor is the Android-side of the UI generation implemented beyond what is needed for the sample thingy.
+The sample thingy requires no configuration, so this has been left out.
+Also, remote access from outside the Wi-Fi network is not implemented, and we opted to use HTTP polling rather than web sockets for communication with the thingy.
+Finally, the bootstrapping process was implemented differently; more on that later.
+
+Our implementation is described in the following.
+
+\subsection{Controller: Home Remote for Android}
+
+We implemented a controller Android app, dubbed Home Remote.
+Its initial view (see figure\ref{fig:homeRemoteHomeView} ) shows a list of installed thingies along with an option to install new ones.
+Selecting a thingy shows the user interface for that thingy (same figure).
+
+\begin{figure}[th]
+\begin{center}
+\includegraphics[width=0.90\columnwidth]{figures/home-remote-thingies+1.png}
+\end{center}
+\caption{Left: The initial view in our controller app. The status of each thingy is shown in a square. Right: The interface for one thingy.}
+\label{fig:homeRemoteHomeView}
+\end{figure}
+
+\subsubsection{Presets}
+
+Presets have been implemented as designed -- a preset consists of a list of thingies along with a desired status for each thingy (figure \ref{fig:homeRemotePresets}).
+Activating a preset causes thingies with actuators to change state, while thingies with sensors are listed to let the preset function as a check list.
+Check marks are overlaid on the status icons of thingies to indicate whether each thingy is in the desired state.
+
+\begin{figure}[th]
+\begin{center}
+\includegraphics[width=0.45\columnwidth]{figures/home-remote-preset.png}
+\end{center}
+\caption{A preset in our controller app. The light is off as desired, but the window is still open.}
+\label{fig:homeRemotePresets}
+\end{figure}
+
+\subsection{Thingy: Light switch}
+
+Our sample thingy, a light switch, was implemented on an Arduino board, with a WiFly shield\footnote{\url{http://www.sparkfun.com/products/9954}} for Wi-Fi connectivity.
+A relay was used in a circuit based on this one\footnote{\url{http://www.arduino.cc/playground/uploads/Learning/relays.pdf}}, except with a 480$\Omega$ resistor and two transistors mounted as a Darlington pair\footnote{\url{http://en.wikipedia.org/wiki/Darlington_transistor}}.
+Once installed, this thingy allows one to control a power outlet and thus, for instance, a lamp.
+\subsection{The bootstrap process}
+
+Recall that the purpose of our bootstrap process is to get a new thingy connected to the home Wi-Fi.
+In the design, we had envisioned a bootstrap process where the thingy would provide a temporary access point that the Android app could connect to for initial communication.
+However, it turned out that while the WiFly board supports ad hoc mode, it cannot work as a regular access point\footnote{\url{http://www.sparkfun.com/datasheets/Wireless/WiFi/WiFlyGSX-um2.pdf}}.
+Ad hoc mode is, in turn, not supported by Android phones out of the box\footnote{\url{http://szym.net/2010/12/adhoc-wifi-in-android/}}.
+However, since Android phones \emph{are} able to work as regular access points, we decided to turn the process around:
+
+\begin{figure}[th]
+\begin{center}
+\includegraphics[width=0.70\columnwidth]{figures/bootstrap-drawing.png}
+\end{center}
+\caption{Devices and access points involved in the bootstrap process}
+\label{fig:bootstrapDraw}
+\end{figure}
+
+When the user starts the process by selecting ``Install new thingy'' in the Android app, he is first prompted to scan the QR code that came with the thingy.
+This code contains the SSID and passphrase of the bootstrap access point that the app then sets up on the phone.
+Second, the app instructs the user to press the button on the thingy; this causes the thingy to make a request to the Android phone via the bootstrap access point.
+The response to this request contains the SSID and passphrase of the home Wi-Fi access point, which the thingy then connects to, obtaining an IP address.
+Next, the thingy briefly reconnects to the bootstrap access point to send this IP address to the Android app.
+Finally, the thingy reconnects to the home Wi-Fi, and the Android app closes the bootstrap access point and reconnects to the home Wi-Fi as well.
+Thus, the thingy is connected to the home Wi-Fi and the Android app is able to make requests to the thingy.
+
+One disadvantage of this implementation is the use of an undocumented API call\footnote{\url{http://stackoverflow.com/questions/3023226/android-2-2-wifi-hotspot-api}}, another is the fact that older Android phones cannot work as access points, and third it relies on the home access point issuing the same IP address when the thingy reconnects.
+That being said, it works, and the user experience is the same as we had envisioned.
+\section{Evaluation}
+
+The evaluation in our prototype was performed at three points: first, an initial evaluation of the overall idea, second, an evaluation of an early prototype using the ``Wizard of Oz'' technique, and third, an evaluation of the final prototype.
+Each is described in the following.
+\subsection{Initial evaluation of the idea}
+
+Before setting out to develop a prototype, we wanted to be sure that our idea was useful.
+Therefore, we checked with a number of friends and colleagues.
+We used short, semi-structured interviews, asking ``Would you be interested in controlling something in your home from your phone, and if so, what would it be?''.
+We also told them that controlling objects while away from home was a possibility.
+Five participants were asked.
+
+We generally received a moderate amount of interest -- it was not the case that everyone was instantly thrilled by the possibility, but all participants did think of something that they would actually like to remote control, either from inside or outside the home.
+The ideas are listed in the introduction.
+
+This assured us that it was worthwhile to proceed.
+\subsection{Evaluation of the first prototype}
+
+In order to evaluate a prototype as early as possible, we decided to use a ``Wizard of Oz'' -- approach where we faked the parts of the system that were the least perceptible for the participants.
+We thus implemented the interface for the Home Remote Android app that the participants would interact with directly.
+A fake thingy was built in the form of a light switch -- in reality, a physical switch at the end of an extension cord allowed the test conductor to turn the light on or off according to the participant's interaction with the app.
+Similarly, the association of the fake thingy with the home Wi-Fi was simulated.
+A simple web interface, shown in figure \ref{fig:wizardInterface} let the test conductor see and change the status of thingies that was shown in the app.
+
+\begin{figure}[th]
+\begin{center}
+\includegraphics[width=0.4\columnwidth]{figures/prototype-wizard-interface.png}
+\end{center}
+\caption{Web interface for the wizard. The ``scanned'' boxes indicate whether the thingies are connected to Wi-Fi while the ``on'' boxes indicate their status.}
+\label{fig:wizardInterface}
+\end{figure}
+
+The evaluation focused on the installation process, the concept of remote control, the concept of presets, and the overall usefulness of our idea.
+An installation guide\footnote{\url{https://github.com/egil/DEX1/blob/master/report/extras/installation-guide.pdf}} was handed out.
+In order to evaluate the ease of installation, we selected two less technical, middle-aged participants, one of which already owned a smart phone.
+While the number of participants for this evaluation was indeed limited due to time constraints, we still believe that the results are useful -- especially where there are similarities in the reactions.
+For details on how this evaluation was performed, see the evaluation plan.
+It is available online\footnote{\url{https://github.com/egil/DEX1/blob/master/report/extras/evaluation-plan.pdf}}.
+
+The ``Wizard of Oz''-approach worked surprisingly well as participants forgot about the extension cord and were surprised to see the the light control working.
+This system introduced a new causal relationship\cite{causalReasoning}, i.e.
+interacting with the app caused lights to go on and off, and participants quickly picked up on this.
+
+Neither participant found it immediately obvious how to control a thingy from the app after having installed the thingy, so the interface needs some tweaks in this regard.
+The concept of presets required some explaining, and with only one physical thingy it proved difficult to provide the illusion of controlling several thingies at once.
+
+Both participants were mostly interested in remote scenarios -- e.g.
+checking that everything was in order after having left the home.
+This shows us that we do indeed need to cross the boundary of the home Wi-Fi, perhaps through a cloud service or a gateway device in the home.
+
+\subsection{Evaluation of the final prototype}
+
+For the final prototype, we set out to implement a light switch.
+With the bootstrapping implemented, we were able to to evaluate the installation process.
+As we were, despite an enthusiastic attempt, unable to build the circuitry to control an actual switch in time for the evaluation, we opted not to evaluate regular use at this point.
+
+We selected two participants in their early twenties.
+Both had experience with smart phones but were not overwhelmingly tech savvy.
+Neither participant had been part of the previous evaluation.
+We used the same questions as previously, skipping the ones that did not apply.
+
+\begin{figure}[th]
+\begin{center}
+\includegraphics[width=0.90\columnwidth]{figures/evaluation-picture.jpg}
+\end{center}
+\caption{Evaluation of the bootstrapping process.}
+\label{fig:evalPic}
+\end{figure}
+
+Both participants found that the process was simple and easy to follow overall, one stating that the process was well-guided by the app.
+One participant pointed out that there was a lack of feedback during the process -- the bootstrapping took around 20 seconds with a static text indicating that it would take ``a little while''.
+This was especially apparent when the thingy failed connecting in the first attempt and required an extra button push.
+The other participant had not previously scanned a QR code and thus found this a little less intuitive than we had anticipated.
+
+\section{Discussion}
+
+OUR DREAMS NOTES: It is on the controller that we envision the platform to take shape in a similar way to e.g.
+the Android platform.
+We imagine that the technologies that developers already understand will enable new innovative ways to control the home.
+[More about cloud here.]
+
+- Comparing home smart thingies to office thingies, i.e. usage patterns.
+
+\section{Future Work}
+
+Cloud backed solution
+- adds real remote control support
+- would require a local ``bridge'' between inhouse thingies and cloud provider
+
+\section{Conclusion}
+
+TODO
+
+\section{Acknowledgements}
+
+We would like to thank Jakob Bardram, Sebastian B\"{u}ttrich, and especially Thomas Pederson for excellent supervision.
+A thank-you is also due for the guys at Brinck's Elektronik\footnote{\url{http://elextra.dk}}, and to those who participated in our evaluation.
 

### 2012-05-17 report/paper.tex
pdf figures
report finished

@@
 \usepackage{url}
+\mdseries\itshape\urlstyle{same}
 \usepackage{graphics}
@@
 \hypersetup{%
-pdftitle={Thinges for Dummies - A Smart}, pdfauthor={David Thomas, Egil Hansen}, pdfkeywords={your
-keywords}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
+pdftitle={Thinges for Dummies},
+pdfauthor={David Thomas, Egil Hansen},
+pdfkeywords={UI-less devices, smart homes, remote control, infrastructure.},
+bookmarksnumbered,
+pdfstartview={FitH},
+colorlinks,
 citecolor=black, filecolor=black, linkcolor=black, urlcolor=black,
@@
 
-\title{Thingies for Dummies\\A smart home infrastructure for the rest of us}
+\title{Thingies for Dummies:\\A smart home infrastructure for the rest of us}
 \numberofauthors{2}
@@
   \alignauthor David Thomas\\
+    \affaddr{IT University of Copenhagen}\\
     \email{dtho@itu.dk}
  \alignauthor Egil Hansen\\
+    \affaddr{IT University of Copenhagen}\\
     \email{ekri@itu.dk}  }
@@
 \begin{abstract}
-
+A number of smart home infrastructures and technologies exist.
+However, these are not commonly adopted by homeowners as they are often too expensive, complex and difficult to retrofit in existing homes.
+We introduce an infrastructure that enables end-users to bring simple smart home devices into their homes and install them.
+Our infrastructure makes use of equipment already present in many homes -- Wi-Fi networks and smartphones -- and is based on common web technologies.
+We include a bootstrapping process to connect UI-less devices to Wi-Fi networks, and an approach to generate user interfaces for these devices.
+We have evaluated our designed infrastructure via a user test of an implemented prototype, and our evaluation participants found the prototype easy to install and use overall.
 \end{abstract}
 
-\keywords{TODO.}
+\keywords{UI-less devices, smart homes, remote control, infrastructure.}
 
-\category{H.5.2}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}.
+%\category{H.5.2}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}.
 
-\generalterms{Design,
-Documentation, Economics, Experimentation, Human Factors, Languages, Management, Measurement, Performance, Reliability,
-Security, Standardization, Theory, Verification.}
+\generalterms{Design, Human Factors, Security.}
 
@@
 
-More than 20 years after Weiser first defined ubiquitous computing \cite{Weiser1991} we have yet to see smart homes become commonplace.
+More than 20 years after Weiser first defined ubiquitous computing \cite{Weiser1991}, we have yet to see smart homes become commonplace.
 We believe this is largely due to smart home technology being inaccessible and too complicated for everyday users, and both price, perceived lack of advantages, and challenges in learning new technology scare users away.
@@
 In this paper we propose a smart home infrastructure that allow homeowners to cheaply bring new smart home technology into their existing homes in small batches, technology that homeowners will realistically be able to install and manage themselves.
-Our proposed infrastructure bases itself on hardware that exists in most homes today -- Wi-Fi and smart phones -- and uses simple and open protocols like HTTP and the WebSocket protocol to provide the communication backbone of the infrastructure.
-Each individual device, or ``Thingy'', as we have dubbed them, is supposed to be simple to install and use, but provide value nonetheless.
+Our proposed infrastructure bases itself on hardware that exists in many homes today -- Wi-Fi and smartphones -- and uses simple and open protocols like HTTP and the WebSocket protocol to provide the communication backbone of the infrastructure.
+Each individual device, or ``thingy'', as we have dubbed them, is supposed to be simple to install and use, but provide value nonetheless.
 We call this concept \textit{Thingies for Dummies}\footnote{This is a reference to the \textit{For Dummies} book series that tries to present non-intimidating guides to various topics and that always contains the subtitle ``A Reference for the Rest of Us!''.}.
 
-Edwards and Grinter describe, in their 2001 paper \cite{Edwards01athome}, seven challenges facing the adoption of smart home technology\footnote{1: \textit{The `Accidentally' Smart Home}.
-2: \textit{Impromptu Interoperability (islands of functionality)}.
-3: \textit{No Systems Administrator}.
-4: \textit{Designing for Domestic Use}.
-5: \textit{Social Implications of Aware Home Technologies}.
-6: \textit{Reliability}.
-7: \textit{Inference in the Presence of Ambiguity}.}, and we believe that through the overarching theme of `simple' in our proposal -- simple infrastructure and simple thingies -- we are able to answer the first six challenges, at least partly.
-Simplifying does imply giving up on the dream of a fully automated intelligent home for the time being, but our proposed infrastructure does not prevent a home from becoming gradually more automated or intelligent as developers become better at leveraging the platform.
+Edwards and Grinter describe, in their 2001 paper \cite{Edwards01athome}, seven challenges facing the adoption of smart home technology:
+\begin{enumerate}
+\item The `Accidentally' Smart Home
+\item Impromptu Interoperability (islands of functionality)
+\item No Systems Administrator
+\item Designing for Domestic Use
+\item Social Implications of Aware Home Technologies
+\item Reliability
+\item Inference in the Presence of Ambiguity
+\end{enumerate}
 
-When we started doing research for this project we first wanted to see if we could come up with a few use cases where some smart home technology would add so much value, that a normal homeowner would go out and invest time and money to retrofit the home.
+We believe that through the overarching theme of `simple' in our proposal -- simple infrastructure and simple thingies -- we are able to answer the first six challenges, at least in part.
+Simplifying does imply giving up on the idea of a fully automated intelligent home for the time being, but our proposed infrastructure does not prevent a home from becoming gradually more automated or intelligent as developers become better at leveraging the platform.
+
+\subsection{Do people want smart homes?}
+When we started doing research for this project, we first wanted to see if we could come up with a few use cases where some smart home technology would add so much value, that a normal homeowner would go out and invest time and money to retrofit the home.
 Through our informal questioning of friends, colleagues, and family, it quickly became clear that the promise of the classic intelligent appliances we see in many office buildings that automatically adjusts their operations through context awareness\footnote{Appliances such as HVAC, light fixtures, window curtains, and automatic doors.} did not have a strong enough appeal.
@@
 \section{Thinges for Dummies Infrastructure}
-The key design decision for \textit{thingies for Dummies} is that it should be simple and  inexpensive to get started retrofitting an existing house with thingies and that it should be independent of specific hardware and software platforms.
+The key design decision for \textit{Thingies for Dummies} is that it should be simple and  inexpensive to get started retrofitting an existing house with thingies and that it should be independent of specific hardware and software platforms.
 This means not requiring a dedicated, centralized controller, and instead to rely on the existing infrastructure in the home for handling communication and control, i.e.
-a Wi-Fi network and smart phones.
+a Wi-Fi network and smartphones.
 By doing so, we limit the amount of new hardware required to get started, since most homes will already have a Wi-Fi network and at least one smartphone.
 This lowers the price and reduces the environmental impact.
-Figure \ref{fig:infrastructureOverview} shows an overview of the infrastructure:
+Figure \ref{fig:infrastructureOverview} shows an overview of the infrastructure.
 
@@
 \begin{center}
-\includegraphics[width=0.90\columnwidth]{figures/systemoverviewdrawing.png}
+\includegraphics[width=0.90\columnwidth]{figures/systemoverviewdrawing.pdf}
 \end{center}
@@
 A number of thingies -- exemplified in the figure as a light switch and a window sensor -- are brought into the home and connected to the Wi-Fi network as well.
-An app on the smartphone then enables the user control and check on the thingies.
+An app on the smartphone then enables the user to control and check on the thingies.
 
@@
 
-With so many networking technologies available care must be taken before picking one above another, however, we arrived at our choice, Wi-Fi, pretty fast.
+With so many networking technologies available, care must be taken before picking one above another, however, we arrived at our choice, Wi-Fi, pretty fast.
 One of our primary requirements was that the network should exist in most homes already.
-This eliminates quite a few choices right away, leaving us with power lines, which the X10 protocol uses, cellular networks such as 3G, phone line wiring, Bluetooth, and Wi-Fi.
-Power lines, which has the advantage of reaches all rooms in a home, has problems with the an uncertain network boundaries, since there is usually no special gateway or firewall preventing data from traveling on the power lines to the neighbours power lines, unless extra hardware is added.
+This eliminates quite a few choices right away, leaving us with power lines, cellular networks such as 3G, phone line wiring, Bluetooth, and Wi-Fi.
+Power lines, which have the advantage of reaches all rooms in a home, have problems with the an uncertain network boundaries, since there is usually no special gateway or firewall preventing data from traveling to the neighbours power lines, unless extra hardware is added.
 Power lines are also inherently a wired network, which means an extra bridge device is needed between the power lines and wireless mobile devices if those are to interact with devices connected to it.
-The phone lines inside the home has similar problems, and is also far less ubiquitous in the home, with most homes only having a few phone plugs.
+The phone lines inside the home have similar problems, and are also far less ubiquitous in the home, with most homes only having a few phone plugs.
 Then there is Bluetooth, which most laptops and phones, even feature phones, come equipped with.
 Bluetooth is however limited in range.
-This leaves cellular networks, which are indeed wireless, but also owned and maintained by carrier companies, that charges fees for the data that travels on their network and not all areas are covered equally well.
-This makes cellular networks the less ideal choice, landing us squarely on Wi-Fi as the preferred option.
+This leaves cellular networks, which are indeed wireless, but also owned and maintained by carrier companies, that charge fees for the data that travels on their network and not all areas are covered equally well.
+This makes cellular networks a less ideal choice, landing us squarely on Wi-Fi as the preferred option.
 
@@
 However, there is a general focus from the Wi-Fi radio chip makers to lower power consumption due to the massive surge of battery driven mobile devices the last few years, so the drawback will matter less as Wi-Fi radios become more power friendly.
-In addition, for many of the scenarios we have found users to be interested in, thingies will have a permanent power source and in the case where low powered sensor thingies are required, we expect these to use a protocol like ZigBee\cite{zigbeeWebsite} and be bundled with a special purpose thingy which act as a bridge between the individual ZigBee enabled thingies the Wi-Fi network.
+In addition, for many of the scenarios we have found users to be interested in, thingies will have a permanent power source and in the case where low powered sensor thingies are required, we expect these to use a protocol like ZigBee \cite{zigbeeWebsite} and be bundled with a special purpose thingy which act as a bridge between the individual ZigBee enabled thingies the Wi-Fi network.
 The bridge thingy could also perform other tasks so the extra cost would be negligible.
@@
 This is of course very dependent on the model of the wireless access point used.
-Better models with good Wi-Fi radios, antennas, faster CPUs, and enough memory, can handle around 25 concurrent connected clients, while lesser models choke at at half as many connections.
+Better models with good Wi-Fi radios and antennas, faster CPUs, and enough memory, can handle around 25 concurrent connected clients, while lesser models choke at at half as many connections.
 However, since one of our design goals was that it should be as inexpensive as possible to get started with smart home technology, we do not expect a average home Wi-Fi to get saturated right away.
 The scenario where a homeowner invests in over 20 new thingies at the same time might not be unlikely, but in that case we feel that investment in an extra access point to handle traffic from thingies is probably also within the budget.
-It is common knowledge among Some Wi-Fi experts claim that Wi-Fi clients also have a tendency to drop their connection from access points more often if using the higher bandwidth 802.11n and 802.11g protocols compared to the slower 802.11b.
+Some Wi-Fi experts claim that Wi-Fi clients also have a tendency to drop their connection from access points more often if using the higher bandwidth 802.11n and 802.11g protocols compared to the slower 802.11b.
 The solution here is to make thingies use 802.11b where possible, and since only a very small subset of thingies will require a 100\% stable connection, homeowners should experience no problems since thingies can simply reconnect if their connection drops.
@@
 HTTP also supports our goal of an open infrastructure; it might very well be the best supported protocol among developers, and this enables the average app developer to build new functionality on top of the infrastructure on their platform of choice.
-Another benefit is that HTTP communication is very unlikely to be blocked in firewalls compared to other less used protocols, so there is a much bigger chance that things will just work.
+Another benefit is that HTTP communication is very unlikely to be blocked by firewalls compared to other less used protocols, so there is a much bigger chance that things will just work.
 
-However, HTTP's statelessness is also a weakness in common smart home scenarios, where a context change in one thingy should trigger an event in another thingy.
-With basic HTTP, a thingy (client) waiting for a state change has to continuously poll the other thingy it is monitoring to discover the state change in a timely manner.
-This is an waste of resources and could potentially deplete the resources of a thingy entirely, especially if more clients are waiting for changes.
+However, HTTP's statelessness is also a weakness in common smart home scenarios, where a context change in a thingy should trigger an event on a controller.
+With basic HTTP, a controller waiting for a state change has to continuously poll the thingy it is monitoring to discover the state change in a timely manner.
+This is an waste of resources and could potentially deplete the resources of a thingy entirely, especially if more controllers are waiting for changes.
 Clearly, relying only on HTTP alone does not scale.
 Several solutions to this problem were considered, the biggest contender to be considered being multicast.
-The advantages of using multicast is that thingies can simply announce state changes on the network and it would not matter if zero, one, or hundreds of clients were interested, the amount of resources required to do so would be the same.
+The advantages of using multicast is that thingies can simply announce state changes on the network and it would not matter how many controllers were interested, the amount of resources required to do so would be the same.
 Ignoring the problems associated multicast on Wi-Fi, i.e.
@@
 The WebSocket protocol supports multiplexing bi-directional, full-duplex communications channels over a single TCP connection and is already supported by the latests versions of most major browsers\footnote{The WebSocket protocol is supported from Chrome 16, Firefox 11 and Internet Explorer 10.}, with numerous frameworks and libraries already built and more on the way.
-The WebSocket Protocol was essentially designed to be a solution for the scenario where a server needs to push information to a client\cite{IETFWebsockets} which web developers have been struggling with for many years, so while it might not scale as well as multicast, we feel this is the best overall approach.
+The WebSocket protocol was essentially designed to be a solution for the scenario where a server needs to push information to a client\cite{IETFWebsockets} which web developers have been struggling with for many years, so while it might not scale as well as multicast, we feel this is the best overall approach.
 
@@
 We have decided to use mDNS/Bonjour\footnote{Bonjour is available on \url{https://developer.apple.com/opensource/}} since it offers wide support across platforms and is relatively lightweight and open source.
-.
 \subsubsection{Security considerations}
 
-The basic trust model for thingies for Dummies is based on the security of the home's Wi-Fi.
+The basic trust model for Thingies for Dummies is based on the security of the home's Wi-Fi.
 Assuming the Wi-Fi is probably configured using WPA2 with AES encryption and a reasonable passphrase, there is a clear boundary for the smart home, and an adversary would not be able to pick up data sent to and from thingies without being connected to the network.
-This also means, that anyone on the network have full control over the thingies attached to it, which can be a problem in some cases.
+This also means, that anyone on the network has full control of the thingies attached to it, which can be a problem in some cases.
 We have discussed the possibility of adding an extra layer of security that would handle such a case.
@@
 However, it is not enough only to authenticate users, since the communication between users and thingies are still being transmitted over an open channel which can allow an adversary to perform replay attacks.
-The solution to this is to secure the communication channel between users and Thinges, i.e.
+The solution to this is to secure the communication channel between users and thinges, i.e.
 using HTTPS.
@@
 
-\subsection{thingies - actuators and sensors}
+\subsection{Thingies - actuators and sensors}
 
@@
 
-The first two points are important because thingies must be installable and manageable by non-technical users.
+The first two points are important because thingies must be installable and manageable by less tech-savvy users.
 It is also reasonable to assume that a simple thingy with one or two functions is going to be more reliable than a device with several functions.
-Not allowing thingies to be dependent on other thingies or services simplifies everything, which again helps makes things easier for the non-technical user.
-Making things simple also means being less dependent on constant firmware updates, which will limit the amount of maintenance required after the initial installation.
+Not allowing thingies to be dependent on other thingies or services simplifies everything, which again helps makes things easier for the less tech-savvy user.
+Making things simple also means being less dependent on constant firmware updates, which will reduce the amount of maintenance required after the initial installation.
 This is highly important, as Kindberg et al writes, \textit{ ``You can't reboot the world, let alone rewrite it, to introduce new functionality.
@@
 
-thingies can have running logic inside them, depending on their functionality, e.g.
+Thingies can have running logic inside them, depending on their functionality, e.g.
 a power plug could be configured to turn on and off at specific times during the day, or turn on a secondary output if a specified amount of power is being drawn from a primary output, but it cannot depend on context outside of its domain, i.e.
@@
 Such logic should exist on controllers.
+Looking back at figure \ref{fig:infrastructureOverview}, recall that the controller is the users's smartphone.
 
@@
 \item Have a unique identifier
-\item Have a passive NFC tag and/or QR code with its ID
+\item Have a passive NFC tag and/or a QR code with credentials for its bootstrap access point
 \item Have a physical reset/install mode button
-\item Be able to connect to an IP based network
+\item Be able to connect to an IP based network through a Wi-Fi radio
 \end{itemize}
@@
 
-Why not require a Wi-Fi radio in thingies?
-This is covered by the last requirement, but is more generalized, since we want to allow for thingies that connect directly through the LAN interface on the home Wi-Fi router, and also enable the scenario where a ZigBee enabled sensor thingies connect through a specialized ZigBee to Wi-Fi bridge thingy.
+The requirement for a Wi-Fi radio can be weakened to enable the scenario where a ZigBee enabled sensor thingies connect through a specialized ZigBee to Wi-Fi bridge thingy.
 We do however still require that all thingies can be reached on their own unique URI through the network.
-This is trivial for thingies connecting directly through Wi-Fi or LAN to the home network -- they simply have a standard URI \cite{uri-rfc} based on their IP address, e.g.
-\lstinline{http://192.168.0.42}.
+This is trivial for thingies connecting directly through Wi-Fi to the home network -- they simply have a standard URI \cite{uri-rfc} based on their IP address, e.g.
+\texttt{http://192.168.0.42}.
 In the bridge scenario, the bridged thingies, e.g.
@@
 Luckily, the URI schema allows for ports to be defined, so each bridged thingy will be identified by the bridges IP and their own port, e.g.
-\lstinline{http://192.168.0.42:1337}, \lstinline{http://192.168.0.42:1338}, etc.
+\lstinline{http://192.168.0.42:1337},\\\lstinline{http://192.168.0.42:1338}, etc.
 
@@
 
-The structured description associates each state variable in the thingy with an internally unique ID.
-This is what makes it possible to keep the service interface simple, as these IDs are used when querying and setting state.
+The structured description associates each state variable in the thingy with ID that is unique within each thingy.
+This makes it possible update the UI by filling in new state values without reloading the UI description.
+These IDs are also used when setting the state of the thingy.
 The following list summarizes the web service interface:
@@
 
-The general bootstrapping process from a user's point of view is very simple.
+The general bootstrapping process is intended to very simple from a user's point of view.
 First, the user plugs in and turns on the thingy.
-Then, the user starts the Home Remote app on his smartphone and, after entering credentials for the Wi-Fi network, clicks ``Install new Thingy''.
+Then, the user starts the Home Remote app on his smartphone.
+When the app first runs, it will prompt the user for credentials to the home Wi-Fi network.
+We considered picking the current network automatically, but we want to ensure that thingies are connected to the right network, and the passphrase is not programmatically retrievable on Android\footnote{\url{http://developer.android.com/reference/android/net/wifi/WifiConfiguration.html}}.
+Then, the user selects ``Install new thingy''.
 The onscreen instructions will prompt the user to scan the QR code or hold the phone close to the thingy (if the phone is NFC enabled).
-From this point, the phone and the thingy are connected to each other, and the user is asked to give it a name so it is identifiable by humans.
+From this point, the phone and the thingy are connected to each other, and the user is asked to give the new thingy a name so it is identifiable by humans.
 The phone also sends the Wi-Fi credentials to the thingy.
@@
 
-You cannot have a smart home without controllers, and to us, the obvious first choice for controllers are smart phones.
-It is a device which users carry all the time and are comfortable using.
-As the previous sections show, we are by no means limited to smart phones -- any computing device supporting the HTTP protocol can act as a controller.
+You cannot have a smart home without controllers, and to us, the obvious first choice for controllers are smartphones.
+It is a device which many users carry all the time and are comfortable using.
+As the previous sections show, we are by no means limited to smartphones -- any computing device supporting the HTTP protocol can act as a controller.
 This is also our only requirements for simple controllers, although we do require a full controller to be able to perform bootstrapping of new thingies, which is where smartphones really shine.
+
+\subsubsection{End-user programming: Presets}
 To enable the simplest form of user programming and automation on the controller level, and to make the scenario described in the introduction possible, we need a way to execute a batch of commands to different thingies.
@@
 The Internet of Things, implemented in e.g.
-HP's Cooltown project\cite{cooltown} is a concept related to ours in that it connects the physical and virtual worlds by creating an online presence for physical objects.
+HP's Cooltown project \cite{cooltown} is a concept related to ours in that it connects the physical and virtual worlds by creating an online presence for physical objects.
 The Cooltown project also mentions the use of local wireless networks as a means of access restriction.
 
+In the following sections, we will relate our work to other smart home infrastructures as well as other technologies that move user interfaces between devices.
+
 \subsection{Smart home technologies}
+Our investigation of smart home technologies has not been as deep as we would have liked -- in part due to time constraints, but also because we did not have access to the relevant equipment.
+Nevertheless, a comparison follows.
 
-X10\footnote{\url{http://x10.com}} is a low-level protocol from the 70s running through the power lines in a home.
-It allows one to control a number of devices using a pre-defined set of commands \footnote{url{http://software.x10.com/pub/manuals/xtdcode.pdf}}.
+X10\footnote{\url{http://x10.com}, \url{http://www.smarthome.com/about_x10.html}, and \url{http://kbase.x10.com/wiki/MyHouse_Online_Remote_Connection_Setup}} is a low-level protocol from the 70s running through the power lines in a home.
+It allows one to control a number of devices using a pre-defined set of commands\footnote{url{http://software.x10.com/pub/manuals/xtdcode.pdf}}.
 Thus, it requires a controller device which is connected to the power lines.
-The power line medium also introduces potential issues with X10 commands leaving or entering a home.
-
-The Open Services Gateway Initiative, OSGi\cite{osgiIntroduction}, is an infrastructure designed by an alliance of over 80 companies.
-\cite{osgiDiscovery} describes how the technology can be used in the context of a smart home, including integration with devices through other technologies such as UPnP and Jini.
-The approach makes use of a gateway device within the home network.
-The infrastructure is marketed towards vendors and used in various products and solutions\cite{osgiMarkets}.
-
-Table \ref{smartHomeTable} compares some properties of our approach versus the ones we have mentioned:
-\begin{table}[H]
-\centering
-\begin{tabular}{| p{1cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{0.8cm} |}
-\hline
-& Installation by end-users & Security & Wireless control & Com-plex-ity \\ \hline
-X10 & Yes, with limitations & Relies on signals not leaving or entering the home & Requires extra equipment & Low \\ \hline
-OSGi & Yes, for some products & Varies with products & Varies with products & High \\ \hline
-Thingies for Dummies & Yes & Provided by Wi-Fi network & Yes & Low \\ \hline
-\end{tabular}
-\caption{Comparison of smart home approaches}
-\label{smartHomeTable}
-\end{table}
-
-Sources for X10: \footnote{\url{http://www.smarthome.com/about_x10.html}}, \footnote{\url{http://kbase.x10.com/wiki/MyHouse_Online_Remote_Connection_Setup}}.
-Sources for OSGi: \cite{osgiMarkets}, \cite{osgiDiscovery}.
-
-OSGi is a complex beast with many existing solutions.
-We have not been able to find one that matches ours in terms of simplicity.
-When it comes to simplicity and end-user installation, X10 is the approach most similar to ours.
+When it comes to simplicity and end-user installation, X10 is probably the approach most similar to ours.
 However, there is the caveat that X10 signals can enter and leave a home through the power lines, so for a secure installation, an electrician is required to install a filtering device.
 Additionally, X10 does not have the convenience of wireless control built in; this requires the addition of a controller device that supports this.
+
+The Open Services Gateway Initiative, OSGi \cite{osgiIntroduction}, is an infrastructure designed by an alliance of over 80 companies.
+In \cite{osgiDiscovery}, Dobrev et al.
+describes how the technology can be used in the context of a smart home, including integration with devices through other technologies such as UPnP and Jini.
+The approach makes use of a gateway device within the home network.
+The infrastructure is marketed towards vendors and used in a large number of products and solutions \cite{osgiMarkets}.
+OSGi is a complex beast, and we have not been able to find an OSGi solution that matches ours in terms of simplicity -- however, we have not investigated all of them.
+
 \subsection{User interface generation}
 
+Since we are designing interaction with UI-less devices -- the thingies -- we will now position our approach in relation to other techniques to move user interfaces from one device to another.
+
 \cite{kindbergSystem} defines four levels of intelligence when moving user interfaces across devices, ranging from e.g.
-VNC\cite{vnc} where raw pixels and input events are transferred, to e.g.
-Jini\cite{jini} where the Java code that generates the UI is transferred.
+VNC \cite{vnc} where raw pixels and input events are transferred, to e.g.
+Jini \cite{jini} where the Java code that generates the UI is transferred.
 In-between, there are approaches where individual widgets are transferred, either by specifying precise widgets (i.e.
@@
 
-We have implemented a subset of our designed infrastructure.
+Due to time constraints, our implementation is limited to a prioritized subset of our designed infrastructure.
 The implementation includes a sample thingy in the form of a light switch, and a controller in the form of an Android app.
-We have implemented bootstrapping of the thingy onto one's home Wi-Fi network as well as communication between the controller and the thingy.
+We have implemented bootstrapping of the thingy as well as communication between the controller and the thingy.
 
-We have not implemented secure thingies with user authentication, or synchronization of configuration across users; nor is the Android-side of the UI generation implemented beyond what is needed for the sample thingy.
+We have not implemented secure thingies with user authentication, nor is the Android-side of the UI generation implemented beyond what is needed for the sample thingy.
 The sample thingy requires no configuration, so this has been left out.
-Also, remote access from outside the Wi-Fi network is not implemented, and we opted to use HTTP polling rather than web sockets for communication with the thingy.
+Also, we opted to use HTTP polling rather than the WebSockets protocol for communication with the thingy.
 Finally, the bootstrapping process was implemented differently; more on that later.
 
-Our implementation is described in the following.
+Our implementation is described in the following. The source code is available online\footnote{\url{https://github.com/egil/dex1}}.
 
@@
 
-We implemented a controller Android app, dubbed Home Remote.
-Its initial view (see figure\ref{fig:homeRemoteHomeView} ) shows a list of installed thingies along with an option to install new ones.
+We implemented a controller as an Android app, dubbed Home Remote.
+Its initial view (see figure \ref{fig:homeRemoteHomeView}) shows a list of installed thingies along with an option to install new ones.
 Selecting a thingy shows the user interface for that thingy (same figure).
@@
 
-Presets have been implemented as designed -- a preset consists of a list of thingies along with a desired status for each thingy (figure \ref{fig:homeRemotePresets}).
+Presets have been implemented as described under the heading ``End-user programming: Presets''.
+A preset consists of a list of thingies along with a desired status for each thingy (figure \ref{fig:homeRemotePresets}).
 Activating a preset causes thingies with actuators to change state, while thingies with sensors are listed to let the preset function as a check list.
-Check marks are overlaid on the status icons of thingies to indicate whether each thingy is in the desired state.
+Check marks are overlaid on the status icons of thingies to indicate whether each thingy is in the desired state (see figure \ref{fig:homeRemotePresets}).
 
@@
 Our sample thingy, a light switch, was implemented on an Arduino board, with a WiFly shield\footnote{\url{http://www.sparkfun.com/products/9954}} for Wi-Fi connectivity.
-A relay was used in a circuit based on this one\footnote{\url{http://www.arduino.cc/playground/uploads/Learning/relays.pdf}}, except with a 480$\Omega$ resistor and two transistors mounted as a Darlington pair\footnote{\url{http://en.wikipedia.org/wiki/Darlington_transistor}}.
+A relay was used in a circuit based on an example at the Arduino website\footnote{\url{http://www.arduino.cc/playground/uploads/Learning/relays.pdf}}, except with a 480$\Omega$ resistor and two transistors mounted as a Darlington pair\footnote{\url{http://en.wikipedia.org/wiki/Darlington_transistor}}.
 Once installed, this thingy allows one to control a power outlet and thus, for instance, a lamp.
@@
 \begin{center}
-\includegraphics[width=0.70\columnwidth]{figures/bootstrap-drawing.png}
+\includegraphics[width=0.70\columnwidth]{figures/bootstrap-drawing.pdf}
 \end{center}
@@
 
-When the user starts the process by selecting ``Install new thingy'' in the Android app, he is first prompted to scan the QR code that came with the thingy.
+When the user starts the process by selecting ``Install new thingy'' in the Android app, the user is first prompted to scan the QR code that came with the thingy.
 This code contains the SSID and passphrase of the bootstrap access point that the app then sets up on the phone.
@@
 One disadvantage of this implementation is the use of an undocumented API call\footnote{\url{http://stackoverflow.com/questions/3023226/android-2-2-wifi-hotspot-api}}, another is the fact that older Android phones cannot work as access points, and third it relies on the home access point issuing the same IP address when the thingy reconnects.
-That being said, it works, and the user experience is the same as we had envisioned.
+For these reasons, we would still recommend an implementation closer to our design.
+That being said, our implementation works, and the user experience is the same as we had envisioned.
 \section{Evaluation}
 
-The evaluation in our prototype was performed at three points: first, an initial evaluation of the overall idea, second, an evaluation of an early prototype using the ``Wizard of Oz'' technique, and third, an evaluation of the final prototype.
+The evaluation of our concept and prototype was performed in three phases: first, an initial evaluation of the overall idea, second, an evaluation of an early prototype using the ``Wizard of Oz'' technique \cite{wizardOfOz}, and third, an evaluation of the final prototype.
 Each is described in the following.
@@
 We also told them that controlling objects while away from home was a possibility.
-Five participants were asked.
+Nine or ten participants were asked.
 
@@
 
-In order to evaluate a prototype as early as possible, we decided to use a ``Wizard of Oz'' -- approach where we faked the parts of the system that were the least perceptible for the participants.
+In order to evaluate a prototype as early as possible, we decided to use a ``Wizard of Oz''-approach where we faked the parts of the system that were the least perceptible for the participants.
 We thus implemented the interface for the Home Remote Android app that the participants would interact with directly.
-A fake thingy was built in the form of a light switch -- in reality, a physical switch at the end of an extension cord allowed the test conductor to turn the light on or off according to the participant's interaction with the app.
+A fake thingy was built in the form of a light switch -- in reality, a physical switch at the end of an extension cord allowed the ``wizard'' to turn the light on or off according to the participant's interaction with the app.
 Similarly, the association of the fake thingy with the home Wi-Fi was simulated.
-A simple web interface, shown in figure \ref{fig:wizardInterface} let the test conductor see and change the status of thingies that was shown in the app.
+A simple web interface, shown in figure \ref{fig:wizardInterface}, let the test conductor see and change the status of thingies that was shown in the app.
 
@@
 The evaluation focused on the installation process, the concept of remote control, the concept of presets, and the overall usefulness of our idea.
-An installation guide\footnote{\url{https://github.com/egil/DEX1/blob/master/report/extras/installation-guide.pdf}} was handed out.
-In order to evaluate the ease of installation, we selected two less technical, middle-aged participants, one of which already owned a smart phone.
+An installation guide\footnote{\url{https://github.com/egil/DEX1/blob/master/report/extras/installation-guide.pdf}} was handed out, and we asked participants to install the thingy, remotely control it, and then to set up and use a preset.
+This was followed by a semi-structured interview where we asked participants what they liked and didn't like about the system, if there was anything they did not understand, and what they would change.
+For details on the evaluation procedure and the interview questions, see the evaluation document\footnote{\url{https://github.com/egil/DEX1/blob/master/report/extras/evaluation-plan.pdf}}.
+
+ In order to evaluate the ease of installation, we selected two less tech-savvy, middle-aged participants, one of which already owned a smart phone.
 While the number of participants for this evaluation was indeed limited due to time constraints, we still believe that the results are useful -- especially where there are similarities in the reactions.
-For details on how this evaluation was performed, see the evaluation plan.
-It is available online\footnote{\url{https://github.com/egil/DEX1/blob/master/report/extras/evaluation-plan.pdf}}.
 
 The ``Wizard of Oz''-approach worked surprisingly well as participants forgot about the extension cord and were surprised to see the the light control working.
-This system introduced a new causal relationship\cite{causalReasoning}, i.e.
+This system introduced a new causal relationship \cite{causalReasoning}, i.e.
 interacting with the app caused lights to go on and off, and participants quickly picked up on this.
@@
 We selected two participants in their early twenties.
-Both had experience with smart phones but were not overwhelmingly tech savvy.
+Both had experience with smartphones but were not overwhelmingly tech savvy.
 Neither participant had been part of the previous evaluation.
-We used the same questions as previously, skipping the ones that did not apply.
+This time, participants were only asked to install our prototype thingy, i.e.
+to perform the bootstrapping procedure.
+This was followed by a semi-structured interview based on the same questions as previously, skipping the ones that did not apply.
 
@@
 \end{center}
-\caption{Evaluation of the bootstrapping process.}
+\caption{Evaluation of the bootstrapping process. The participant is scanning the QR code.}
 \label{fig:evalPic}
@@
 
-OUR DREAMS NOTES: It is on the controller that we envision the platform to take shape in a similar way to e.g.
+Our evaluation indicates that it is indeed possible to make smart home technology accessible to less tech-savvy users, though a more thorough evaluation is needed.
+There are still questions as to the complexity of physically installing thingies: this cannot be more complicated than it is to assemble furniture from IKEA.
+
+While one might argue that we are missing a complete evaluation of the final prototype, we do feel that we have covered our implementation by evaluating both regular use and the installation process over the course of the project.
+
+It is on the controller that we envision the platform to take shape in a similar way to e.g.
 the Android platform.
-We imagine that the technologies that developers already understand will enable new innovative ways to control the home.
-[More about cloud here.]
+We imagine, that the technologies that developers already understand, will enable new innovative ways to control the home.
+It was clear from our evaluations that users really like the away from home scenarios, and it is probably no coincidence that big companies like AT\&T and IBM are pursuing this through cloud based services.
+Our proposed infrastructure is in no way in conflict with this cloud based approach, quite the opposite, since all thingies are IP based already.
+Enabling a cloud scenario with our infrastructure should only require a gateway device that keeps a connection to the cloud service and a connection to each thingy inside the home network.
 
-- Comparing home smart thingies to office thingies, i.e. usage patterns.
-
-\section{Future Work}
-
-Cloud backed solution
-- adds real remote control support
-- would require a local ``bridge'' between inhouse thingies and cloud provider
-
+Multi-user scenarios add interesting issues that we have not looked into in depth: one is the synchronization of configuration between controllers, another is the privacy issues that might arise when users are suddenly able to remotely monitor and affect physical objects in the home.
+We are more or less used to being actively monitored in some capacity when we leave the home, but will people feel comfortable being monitored while at home?
 \section{Conclusion}
 
-TODO
+In this paper, we have described an infrastructure that allows anyone to retrofit their home with pieces of smart home technology while leveraging existing equipment.
+We have implemented a subset of our design in a prototype, and through our evaluation we have seen that this prototype is indeed easy to install and use, though a few tweaks to the user interface would improve the user experience.
+Our infrastructure includes a secure bootstrapping process where UI-less devices are connected to a user's Wi-Fi network.
 

### 2012-05-21 arduino/library/WiFly/WiFlyDevice.cpp
arduino code should be stable for demo (famous last words)

@@ -2,8 +2,19 @@
 #include "WiFly.h"
 
 #define DEBUG_LEVEL 0
+#define REQUEST_LENGTH 40
+#define LED_PIN 13
 
 #include "Debug.h"
+
+boolean currentStatus = false;
+const char* UI = 
+  "{"
+  "'title': 'Light switch',"
+  "'version': 1.0,"
+  "'widgets': ["
+  "{ 'id': '1', 'title': 'Light on', 'type': 'editable', 'content-type': 'boolean', 'widgets': [] }"
+  "]}";
 
 
 boolean WiFlyDevice::findInResponse(const char *toMatch,
@@ -611,10 +622,12 @@ const char* WiFlyDevice::newConnect(const char* ssid, const char* pass) {
 const char* WiFlyDevice::waitForIP() {
   int timeout = 6000;
   unsigned long startTime = millis();
-  char expected[] = "IP=";
+  static char expected[] = "IP=";
+  static char donotwant[] = "FAILED";
   static char ip[16] = "";
   int index = 0;
   int ipIndex = 0;
+  int badIndex = 0;
   
   while (true) {
     while (!uart.available()) {
@@ -624,6 +637,16 @@ const char* WiFlyDevice::waitForIP() {
     
     char c = uart.read();
     Serial.print(c);
+    
+    if (c == donotwant[badIndex]) {
+      badIndex++;
+      if (badIndex == strlen(donotwant)) {
+        return NULL;
+      }
+    } else {
+      badIndex = 0;
+    }
+    
     if (c == expected[index]) {
       index++;
       if (index == strlen(expected)) {
@@ -642,10 +665,118 @@ const char* WiFlyDevice::waitForIP() {
 }
 
 void WiFlyDevice::runServer() {
-  // wait for *OPEN*
-  // read with timeout
-  // extract request
-  // do stuff & send response
+  while (true) {
+    waitForRequest();
+  }
+}
+
+void WiFlyDevice::waitForRequest() {
+  int timeout = 8000;
+  unsigned long start = millis();
+  static char expected[] = "*OPEN*";
+  int index = 0;
+ 
+  Serial.println("Waiting for open");
+  while (true)
+  {
+    while (!uart.available()) {
+      if (millis() > start + timeout) {
+        enterCommandMode();
+        uart.println("close");
+        uart.println("exit");
+        return;
+      }
+    }
+    char c = uart.read();
+    Serial.print(c);
+    if (c == expected[index]) {
+      index++;
[…]

### 2012-05-21 arduino/library/WiFly/WiFlyDevice.h

@@ -11,6 +11,10 @@ class WiFlyDevice {
     void begin();
     void beginAdhoc();
     void runServer();
+    void handleRequest();
+    void sendResponse(char* request);
+    void sendValues(char* request);
+    void waitForRequest();
         
     const char* newConnect(const char* ssid, const char* pass);
     void newBegin();

### 2012-05-21 prototype/src/dk/itu/spcl/dex/ThingyUpdater.java

@@ -80,12 +80,16 @@ public class ThingyUpdater implements Runnable {
       String url = thingy.getUrl() + "values";
       if (thingy.isStatusChangeQueued()) {
         url += thingy.getStatus() ? "/1" : "/0";
-        thingy.setStatusChangeQueued(false);
       } else {
         url += "/z"; // no change
       }
       boolean thingyStatus = getStatusFromUrl(url);
-      thingy.setStatus(thingyStatus);
+      if (thingy.getStatus() == thingyStatus) {
+        thingy.setStatusChangeQueued(false);
+      }
+      if (!thingy.isStatusChangeQueued()) {
+        thingy.setStatus(thingyStatus);
+      }
     } catch (ClientProtocolException e) {
       Log.e("dex", e.toString());
     } catch (IOException e) {

### 2012-05-21 arduino/library/WiFly/WiFlyDevice.cpp
let there be light

@@ -3,7 +3,8 @@
 
 #define DEBUG_LEVEL 0
 #define REQUEST_LENGTH 40
-#define LED_PIN 13
+// also defined in pde file
+#define LED_PIN 9 
 
 #include "Debug.h"
 
